---
title: "Cause and Burn in Development"
author: "David Rose, Siying Zhang, Shaun Nichols, Ellen Markman & Tobias Gerstenberg"
date: "`r Sys.Date()`"
output: pdf_document
---

# Load packages
```{r eval=TRUE, include=FALSE, message=FALSE, warning=FALSE}

library("janitor")        # for cleaning variable nqmes
library("emmeans")        # for comparing means
library("brms")           # for Bayesian data analysis
library("patchwork")      # for combining figures
library("knitr")          # for knitting 
library("tidyverse")      # for everything else

```

# Settings

```{r message=FALSE, warning=FALSE}

# set theme 
theme_set(theme_classic())

# sum coding
options(contrasts = c("contr.sum","contr.poly"))

```

# EXPERIMENT 1: CHAINS
## CAUSE V LEXICAL (BREAK & CRACK)
### ADULTS
#### DATA
##### Read in data
```{r message=FALSE, warning=FALSE}

df.exp1_cause_adults = read_csv("../../data/experiment1/cause/adults/exp1_cause_adults.csv")

```

##### Wrangle 

```{r message=FALSE, warning=FALSE}

df.exp1_cause_adults = df.exp1_cause_adults %>% 
  mutate(participant = 1:n()) %>% 
  select(participant, break_cause_processed, break_simple_processed, crack_cause_processed, crack_simple_processed, counterbalance) %>% 
  pivot_longer(-c(participant,counterbalance),
               names_to = "tmp_name",
               values_to = "response") %>% 
  separate(.,
           col = tmp_name,
           into = c("verb", "question", "tmp"),
           sep = "_") %>% 
select(-tmp) %>% 
  mutate(distal = ifelse(counterbalance == "order_1" & str_detect(response,
                                                                  "Andy|Sophia"), 1, 0),
         distal = ifelse(counterbalance == "order_2" & str_detect(response,
                                                                  "Suzy|Bobby"), 1, distal),
         proximal = ifelse(counterbalance == "order_1" & str_detect(response,
                                                                    "Suzy|Bobby"), 1, 0),
         proximal = ifelse(counterbalance == "order_2" & str_detect(response,
                                                                    "Andy|Sophia"), 1, proximal), 
         question = str_replace_all(question, "simple", "lexical")) %>% 
  rename(scenario = verb)

```

##### Demographics

```{r message=FALSE, warning=FALSE}

df.exp1_cause_adults_demo = read_csv("../../data/experiment1/cause/adults/exp1_cause_adults_demo.csv")

df.exp1_cause_adults_demo  %>% 
  summarise(age_mean = mean(as.numeric(age), na.rm = TRUE))

df.exp1_cause_adults_demo  %>% 
  summarise(age_sd = sd(as.numeric(age), na.rm = TRUE))

df.exp1_cause_adults_demo  %>% 
  group_by(gender) %>% 
  count() 

df.exp1_cause_adults_demo  %>% 
  group_by(race) %>% 
  count() 

```

#### STATS

##### Bayesian Models
###### Distal

```{r}


df.model = df.exp1_cause_adults %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "cause"))

# Check contrast values
 contrasts(df.model$question)

# removed random intercepts for scenario to avoid divergent transition errors
fit.brm.distal = brm(formula = distal ~ 1 + question + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_adult_distal") 
fit.brm.distal


```

###### Proximal

```{r}

fit.brm.proximal = brm(formula = proximal ~ 1 + question + (1 | participant) + (1 | scenario),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/cause_adult_proximal") 

fit.brm.proximal

```

### CHILDREN
#### DATA
##### Read in data

```{r message=FALSE, warning=FALSE}

df.exp1_cause_children = read_csv("../../data/experiment1/cause/children/exp1_cause_children.csv")

```

##### Wrangle
```{r message=FALSE, warning=FALSE}

#clean data
df.exp1_cause_children = df.exp1_cause_children %>% 
  clean_names() %>% 
  rename(
         question = question_type) %>% 
  mutate(response = str_remove_all(string = response,
                                   pattern = "\""),
         response = str_remove_all(string = response,
                                   pattern = ":"),
         response = str_remove_all(string = response,
                                   pattern = "\\}"),
         response = str_remove_all(string = response,
                                   pattern = "\\."),
         response = str_remove_all(string = response,
                                   pattern = "\\,"),
         response = str_remove_all(string = response,
                                   pattern = "\\\\n"),
         response = str_to_lower(response)) %>% 
  select(-(response_id : age_range), -notes, -full_response, -gender) 


# code responses
df.exp1_cause_children = df.exp1_cause_children %>% 
  mutate(distal = ifelse(counterbalance == "andy" & str_detect(response, "andy"), 1, 0),
         distal = ifelse(counterbalance == "suzy" & str_detect(response, "suzy"), 1, distal),
         distal = ifelse(counterbalance == "bobby" & str_detect(response, "bobby"), 1, distal),
         distal = ifelse(counterbalance == "sophia" & str_detect(response, "sophia"), 1, distal),
         proximal = ifelse(counterbalance == "andy" & str_detect(response, "suzy"), 1, 0),
         proximal = ifelse(counterbalance == "suzy" & str_detect(response, "andy"), 1, proximal),
         proximal = ifelse(counterbalance == "bobby" & str_detect(response, "sophia"), 1, proximal),
         proximal = ifelse(counterbalance == "sophia" & str_detect(response, "bobby"), 1, proximal),
         age = round(rounded_age / 365, digits = 2),
         question = str_replace_all(question, "break|crack", "simple")) %>% 
  na.omit()

# compute age and replace simple with lexical
df.exp1_cause_children = df.exp1_cause_children %>% 
  mutate(age_whole = as.integer(age)) %>%
  mutate(age_character = as.character(age_whole)) %>%
  mutate(age_character = recode(age_character, "7" = "7-9", "8" = "7-9", "9" = "7-9"),
         question = str_replace_all(question, "simple", "lexical")) %>%
  rename(participant = participant_number) 
 
```

##### Demographics

```{r}

```

#### STATS
##### Bayesian Models
###### Distal

```{r}

df.model = df.exp1_cause_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "caused"),
         age = age - mean(age))

# Check contrast values
 contrasts(df.model$question)


fit.brm.distal = brm(formula = distal ~ 1 + question + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_children_distal") 
fit.brm.distal


fit.brm.distal.age = brm(formula = distal ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_children_distal_age") 
fit.brm.distal.age

```

###### Proximal
```{r}

# removed random intercepts for scenario to avoid divergent transition errors
fit.brm.proximal = brm(formula = proximal ~ 1 + question + (1 | participant),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/cause_children_proximal") 

fit.brm.proximal


fit.brm.proximal.age = brm(formula = proximal ~ 1 + question*age + (1 | participant) + (1 | scenario),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/cause_children_proximal_age") 

fit.brm.proximal.age


```

## MADE v LEXICAL (BREAK & CRACK)
### ADULTS
#### DATA
##### Read in data

```{r message=FALSE, warning=FALSE}

df.exp1_made_adults = read_csv("../../data/experiment1/made/adults/exp1_made_adults.csv")

```

##### Wrangle

```{r message=FALSE, warning=FALSE}

df.exp1_made_adults = df.exp1_made_adults %>% 
  mutate(participant = 1:n()) %>% 
  select(participant, break_cause_processed, break_simple_processed, crack_cause_processed, crack_simple_processed, counterbalance) %>% 
  pivot_longer(-c(participant,counterbalance),
               names_to = "tmp_name",
               values_to = "response") %>% 
  separate(.,
           col = tmp_name,
           into = c("verb", "question", "tmp"),
           sep = "_") %>% 
select(-tmp) %>% 
  mutate(distal = ifelse(counterbalance == "order_1" & str_detect(response,
                                    "Andy|Sophia"), 1, 0),
         distal = ifelse(counterbalance == "order_2" & str_detect(response,
                                    "Suzy|Bobby"), 1, distal),
         proximal = ifelse(counterbalance == "order_1" & str_detect(response,
                                    "Suzy|Bobby"), 1, 0),
         proximal = ifelse(counterbalance == "order_2" & str_detect(response,
                                    "Andy|Sophia"), 1, proximal),
         question = str_replace_all(question, "cause", "made"),
         question = str_replace_all(question, "simple", "lexical")) %>% 
  rename(scenario = verb)

```

##### Demographics

```{r message=FALSE, warning=FALSE}

df.exp1_made_adults_demo = read_csv("../../data/experiment1/made/adults/exp1_made_adults_demo.csv")

df.exp1_made_adults_demo %>% 
  summarise(age_mean = mean(as.numeric(age), na.rm = TRUE))

df.exp1_made_adults_demo %>% 
  summarise(age_sd = sd(as.numeric(age), na.rm = TRUE))

df.exp1_made_adults_demo %>% 
  group_by(gender) %>% 
  count() 

df.exp1_made_adults_demo %>% 
  group_by(race) %>% 
  count() 

```

#### STATS
##### Bayesian Models
###### Distal

```{r}

df.model = df.exp1_made_adults %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "made"))

# Check contrast values
 contrasts(df.model$question)


fit.brm.distal = brm(formula = distal ~ 1 + question + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     cores = 8,
                     file = "cache/made_adult_distal") 
fit.brm.distal




```

###### Proximal

```{r}

fit.brm.proximal = brm(formula = proximal ~ 1 + question + (1 | participant) + (1 | scenario),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      cores = 8,
                      file = "cache/made_adult_proximal") 

fit.brm.proximal


```

### CHILDREN
#### DATA
##### Read in data

```{r message=FALSE, warning=FALSE}

df.exp1_made_children = read_csv("../../data/experiment1/made/children/exp1_made_children.csv")

```

##### Wrangle

```{r message=FALSE, warning=FALSE}

#clean data
df.exp1_made_children = df.exp1_made_children %>% 
  clean_names() %>% 
  rename(
         question = question_type) %>% 
  mutate(response = str_to_lower(response),
         counterbalance = str_to_lower(counterbalance)) %>% 
  select(-(response_id : age_range), -notes, -full_response, -gender) 

#code responses
df.exp1_made_children = df.exp1_made_children %>% 
  mutate(distal = ifelse(counterbalance == "andy" & str_detect(response, "andy"), 1, 0),
         distal = ifelse(counterbalance == "suzy" & str_detect(response, "suzy"), 1, distal),
          distal = ifelse(counterbalance == "bobby" & str_detect(response, "bobby"), 1, distal),
          distal = ifelse(counterbalance == "sophia" & str_detect(response, "sophia"), 1, distal),
         proximal = ifelse(counterbalance == "andy" & str_detect(response, "suzy"), 1, 0),
         proximal = ifelse(counterbalance == "suzy" & str_detect(response, "andy"), 1, proximal),
          proximal = ifelse(counterbalance == "bobby" & str_detect(response, "sophia"), 1, proximal),
          proximal = ifelse(counterbalance == "sophia" & str_detect(response, "bobby"), 1, proximal),
         age = round(rounded_age / 365, digits = 2),
         question = str_replace_all(question, "break|crack", "simple")) %>% 
  na.omit()

# compute age and recode question
df.exp1_made_children = df.exp1_made_children %>% 
   mutate(age_whole =as.integer(age)) %>%
  mutate(age_character = as.character(age_whole)) %>%
  mutate(age_character = recode(age_character, "7" = "7-9", "8" = "7-9", "9" = "7-9"),
         question = str_replace_all(question, "simple", "lexical")) %>%
  rename(participant = participant_number) 

```

##### Demographics
```{r}

```

#### STATS

##### Bayesian Models
###### Distal
```{r}

df.model = df.exp1_made_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "made"),
         age = age - mean(age))

# Check contrast values
 contrasts(df.model$question)


fit.brm.distal = brm(formula = distal ~ 1 + question + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     cores = 8,
                     file = "cache/made_children_distal") 
fit.brm.distal


fit.brm.distal.age = brm(formula = distal ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     cores = 8,
                     file = "cache/made_children_distal_age") 
fit.brm.distal.age

```

###### Proximal

```{r}

fit.brm.proximal = brm(formula = proximal ~ 1 + question + (1 | participant) + (1 | scenario),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      cores = 8,
                      file = "cache/made_children_proximal") 

fit.brm.proximal


fit.brm.proximal.age = brm(formula = proximal ~ 1 + question*age + (1 | participant) + (1 | scenario),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      cores = 8,
                      file = "cache/made_children_proximal_age") 

fit.brm.proximal.age



```

##PLOTS
### Data
#### Different Responses

```{r message=FALSE, warning=FALSE}

df.exp1_cause_adults_differnece = df.exp1_cause_adults %>% 
  select(question, distal, proximal) %>% 
  mutate(age = rep("adults"))

df.exp1_made_adults_difference = df.exp1_made_adults %>% 
  select(question, distal, proximal) %>% 
  mutate(age = rep("adults"))

df.exp1_cause_children_difference = df.exp1_cause_children %>% 
  select(question, distal, proximal) %>% 
  mutate(question = str_replace_all(question, "caused", "cause")) %>% 
  mutate(age = rep("children"))

df.exp1_made_children_difference = df.exp1_made_children %>% 
  select(question, distal, proximal) %>% 
  mutate(age = rep("children"))

df.difference_combined = df.exp1_cause_adults_differnece %>% 
  bind_rows(df.exp1_made_adults_difference,
            df.exp1_cause_children_difference,
            df.exp1_made_children_difference) %>% 
   mutate(response_pattern = case_when(
    distal == 1 & proximal == 1 ~ "both",
    distal == 0 & proximal == 0 ~ "neither",
    TRUE ~ "different"
  ))
 
df.difference_combined %>% 
  group_by(age, question, response_pattern) %>% 
  summarize(n = n()) %>% 
  ungroup() %>%
  group_by(age, question) %>% 
  mutate(percentage = n / sum(n) * 100) 

```

### Difference Plots
#### Cause
```{r}

df.cause_children_differnet = df.exp1_cause_children %>% 
  mutate(response_pattern = case_when(
    distal == 1 & proximal == 1 ~ "both",
    distal == 0 & proximal == 0 ~ "neither",
    TRUE ~ "different"
  )) %>% 
  filter(response_pattern == "different")


df.model = df.cause_children_differnet %>% 
  mutate(difference = distal - proximal,
        difference = recode(difference, `-1` = 0),
        question = str_replace_all(question, "caused", "cause"))


fit.brm.chain_cause.difference = brm(formula = difference ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .9999),
                     cores = 8,
                     file = "cache/chain_cause_difference")


df.data = expand_grid(age = seq(4, 9, 0.1),
                      question = c("cause", "lexical"))

df.prediction = fit.brm.chain_cause.difference %>% 
  fitted(newdata = df.data,
         re_formula = NA,
          probs = c(0.1, 0.9)) %>% 
  as_tibble() %>% 
  bind_cols(df.data) %>% 
  clean_names()


df.adults = df.exp1_cause_adults %>% 
    mutate(response_pattern = case_when(
    distal == 1 & proximal == 1 ~ "both",
    distal == 0 & proximal == 0 ~ "neither",
    TRUE ~ "different"
  )) %>% 
  filter(response_pattern == "different") %>% 
  select(-response) %>% 
  mutate(age_whole = rep(10)) %>% 
  mutate(difference = distal - proximal,
        difference = recode(difference, `-1` = 0))



df.means = df.model %>% 
  bind_rows(df.adults) %>% 
  mutate(age_whole = factor(age_whole, 
                            levels = c(4, 5, 6, 7, 8, 9, 10), 
                            labels = c("4", "5", "6", "7", "8", "9", "adults"))) %>% 
  group_by(age_whole, question) %>% 
  summarize(
    response = Hmisc::smean.cl.boot(difference)) %>%
    mutate(index = c("response", "low", "high")) %>%
    ungroup() %>% 
    pivot_wider(names_from = index,
                values_from = response) %>% 
  mutate(age_whole = fct_recode(age_whole, "10" = "adults"),
         age_whole = as.numeric(as.character(age_whole)))



p1 = ggplot(mapping = aes(x = age, 
                     y = difference,
                     color = question)) + 
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  geom_smooth(data = df.prediction,
              mapping = aes(y = estimate,
                            ymin = q10,
                            ymax = q90,
                            color = question,
                            fill = question),
              stat = "identity",
              alpha = 0.2) +
  geom_pointrange(data = df.means,
                  mapping = aes(x = age_whole,
                                y = response,
                                ymin = low,
                                ymax = high,
                                fill = question,
                                shape = question),
                  color = "black",
                  size = 0.5,
                  show.legend = FALSE,
                  alpha = 0.8,
                  position = position_dodge(width = 0.3)) +
  ylab("Probability of selecting \n distal or proximal cause") +
  scale_fill_brewer(palette = "Set1") + 
  scale_color_brewer(palette = "Set1") +
  scale_shape_manual(values = c(21, 23)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = c("100% \n proximal", "75%", "50%", "75%", "100% \n distal"),
                      limits = c(0, 1)) +  
 scale_x_continuous(breaks = 4:10,
                     labels = c("4", "5", "6", "7", "8", "9", "Adults")) +
  theme(plot.title = element_text(hjust = 0.5),
        legend.title = element_blank(),
        text = element_text(size = 18))

```


#### Made
```{r}

df.made_children_differnet = df.exp1_made_children %>%
  mutate(response_pattern = case_when(
    distal == 1 & proximal == 1 ~ "both",
    distal == 0 & proximal == 0 ~ "neither",
    TRUE ~ "different"
  )) %>% 
  filter(response_pattern == "different")

df.model = df.made_children_differnet %>% 
  mutate(difference = distal - proximal,
        difference = recode(difference, `-1` = 0))


fit.brm.chain_made.difference = brm(formula = difference ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .9999),
                     cores = 8,
                     file = "cache/chain_made_difference")


df.data = expand_grid(age = seq(4, 9, 0.1),
                      question = c("made", "lexical"))

df.prediction = fit.brm.chain_made.difference %>% 
  fitted(newdata = df.data,
         re_formula = NA,
          probs = c(0.1, 0.9)) %>% 
  as_tibble() %>% 
  bind_cols(df.data) %>% 
  clean_names()



df.adults = df.exp1_made_adults %>% 
    mutate(response_pattern = case_when(
    distal == 1 & proximal == 1 ~ "both",
    distal == 0 & proximal == 0 ~ "neither",
    TRUE ~ "different"
  )) %>% 
  filter(response_pattern == "different") %>% 
  select(-response) %>% 
  mutate(age_whole = rep(10)) %>% 
  mutate(difference = distal - proximal,
        difference = recode(difference, `-1` = 0))



df.means = df.model %>% 
  bind_rows(df.adults) %>% 
  mutate(age_whole = factor(age_whole, 
                            levels = c(4, 5, 6, 7, 8, 9, 10), 
                            labels = c("4", "5", "6", "7", "8", "9", "adults"))) %>% 
  group_by(age_whole, question) %>% 
  summarize(
    response = Hmisc::smean.cl.boot(difference)) %>%
    mutate(index = c("response", "low", "high")) %>%
    ungroup() %>% 
    pivot_wider(names_from = index,
                values_from = response) %>% 
  mutate(age_whole = fct_recode(age_whole, "10" = "adults"),
         age_whole = as.numeric(as.character(age_whole)))




p2 = ggplot(mapping = aes(x = age, 
                     y = difference,
                     color = question)) + 
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  geom_smooth(data = df.prediction,
              mapping = aes(y = estimate,
                            ymin = q10,
                            ymax = q90,
                            color = question,
                            fill = question),
              stat = "identity",
              alpha = 0.2) +
  geom_pointrange(data = df.means,
                  mapping = aes(x = age_whole,
                                y = response,
                                ymin = low,
                                ymax = high,
                                fill = question,
                                shape = question),
                  color = "black",
                  size = 0.5,
                  show.legend = FALSE,
                  alpha = 0.8,
                  position = position_dodge(width = 0.3)) +
  ylab(element_blank()) +
  scale_fill_manual(values = c("made" = "#4DAF4A", "lexical" = "#377EB8"), breaks=c("made", "lexical")) +
  scale_color_manual(values = c("made" = "#4DAF4A", "lexical" = "#377EB8"), breaks=c("made", "lexical")) +
  scale_shape_manual(values = c(23, 21)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = c("100% \n proximal", "75%", "50%", "75%", "100% \n distal"),
                     limits = c(0, 1)) + 
  scale_x_continuous(breaks = 4:10,
                     labels = c("4", "5", "6", "7", "8", "9", "Adults")) +
  theme(plot.title = element_text(hjust = 0.5),
        legend.title = element_blank(),
        text = element_text(size = 18))

```

#### Combine Cause and Made Plots

```{r fig.height=4, fig.width=12}

plot = p1 + p2 + 
plot_layout(nrow = 1) &
plot_annotation(tag_levels = "A") &
theme(plot.tag = element_text(face = "bold"))

ggsave(plot, filename = "../../figures/experiment1/chain.pdf", height = 4, width = 12)

plot


```


# EXPERIMENT 2: ABSENCES
## CAUSE V LEXICAL (BURN & FLOOD)
### ADULTS
#### DATA
##### Read in data

```{r message=FALSE, warning=FALSE}

df.exp2_cause_adults = read_csv("../../data/experiment2/cause/adults/exp2_cause_adults.csv")

```

##### Wrangle
```{r message=FALSE, warning=FALSE}

# clean data
df.exp2_cause_adults = df.exp2_cause_adults %>% 
  mutate(condition = str_extract(string = responses,
                                 pattern = "sunburn_simple_response|sunburn_cause_response|flood_simple_response|flood_cause_response"),
         response = str_extract(string = responses, 
                                pattern = ":(.*)"),
         response = str_remove_all(string = response,
                                   pattern = "\""),
         response = str_remove_all(string = response,
                                   pattern = ":"),
         response = str_remove_all(string = response,
                                   pattern = "\\}"),
         response = str_remove_all(string = response,
                                   pattern = "\\."),
         response = str_remove_all(string = response,
                                   pattern = "\\,"),
         response = str_remove_all(string = response,
                                   pattern = "\\\\n"),
         response = str_to_lower(response)) %>% 
  separate(condition, c("scenario", "question", "extra"), "_") %>% 
  rename(participant = workerid) %>% 
  select(participant, scenario, question, response)

# code responses
df.exp2_cause_adults = df.exp2_cause_adults %>%
  mutate(direct = ifelse(str_detect(response,
                                    "^sun$|sun | sun$"), 1, 0),
         direct = ifelse(str_detect(response,
                                    "^water$|water | water$"), 1, direct),
         direct = ifelse(str_detect(response,
                                    "^rain$|rain | rain$"), 1, direct),
         absence = ifelse(str_detect(response,
                                     "^sunscreen$|sunscreen | sunscreen$"), 1, 0),
         absence = ifelse(str_detect(response,
                                     "^window$|window | window$"), 1, absence),
         absence = ifelse(str_detect(response,
                                     "^latch$|latch | latch$"), 1, absence))

## replace simple with lexical
df.exp2_cause_adults = df.exp2_cause_adults %>% 
  mutate(question = str_replace_all(question, "simple", "lexical"))


```

##### Demographics

```{r message=FALSE, warning=FALSE}

df.exp2_cause_adults_demo = read_csv("../../data/experiment2/cause/adults/exp2_cause_adults_demo.csv")

df.exp2_cause_adults_demo %>% 
  summarise(age_mean = mean(as.numeric(age), na.rm = TRUE))

df.exp2_cause_adults_demo %>% 
  summarise(age_sd = sd(as.numeric(age), na.rm = TRUE))

df.exp2_cause_adults_demo %>% 
  group_by(gender) %>% 
  count() 

df.exp2_cause_adults_demo %>% 
  group_by(race) %>% 
  count() 

df.exp2_cause_adults_demo %>% 
  group_by(ethnicity) %>% 
  count() 

```

#### STATS
##### Bayesian Models
###### Direct

```{r}

df.model = df.exp2_cause_adults  %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "cause"))

# Check contrast values
 contrasts(df.model$question)

fit.brm.direct = brm(formula = direct ~ 1 + question + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_adult_direct") 
fit.brm.direct

```

###### Absent
```{r}

fit.brm.absent = brm(formula = absence ~ 1 + question + (1 | participant) + (1 | scenario),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/cause_adult_absent") 

fit.brm.absent

```

### CHILDREN
#### DATA
##### Read in data

```{r message=FALSE, warning=FALSE}

df.exp2_cause_children = read_csv("../../data/experiment2/cause/children/exp2_cause_children.csv")

```

##### Wrangle
```{r message=FALSE, warning=FALSE}

# clean responses
df.exp2_cause_children = df.exp2_cause_children %>% 
  rename(response = full_response,
         question = question_type) %>% 
  mutate(response = str_remove_all(string = response,
                                   pattern = "\""),
         response = str_remove_all(string = response,
                                   pattern = ":"),
         response = str_remove_all(string = response,
                                   pattern = "\\}"),
         response = str_remove_all(string = response,
                                   pattern = "\\."),
         response = str_remove_all(string = response,
                                   pattern = "\\,"),
         response = str_remove_all(string = response,
                                   pattern = "\\\\n"),
         response = str_to_lower(response))


# code responses
df.exp2_cause_children = df.exp2_cause_children %>%
  mutate(direct = ifelse(str_detect(response,
                                    "^sun$|sun | sun$"), 1, 0),
         direct = ifelse(str_detect(response,
                                    "^water$|water | water$"), 1, direct),
         direct = ifelse(str_detect(response,
                                    "^rain$|rain | rain$"), 1, direct),
         absence = ifelse(str_detect(response,
                                     "^sunscreen$|sunscreen | sunscreen$"), 1, 0),
         # note the first response in the data is 'windows' but this doesn't capture that
         absence = ifelse(str_detect(response,
                                     "^window$|window | window$"), 1, absence),
         absence = ifelse(str_detect(response,
                                     "^latch$|latch | latch$"), 1, absence)) 


# compute age and replace simple with lexical
df.exp2_cause_children = df.exp2_cause_children %>%
  mutate(age = round(rounded_age / 365, digits = 2),
         age_whole =as.integer(age),
         question = str_replace_all(question, "simple", "lexical"))

```

##### Demographics

```{r}

```

#### STATS
##### Bayesian Models
###### Direct
```{r}


df.model = df.exp2_cause_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "caused"),
         age = age - mean(age))

# Check contrast values
 contrasts(df.model$question)

fit.brm.direct = brm(formula = direct ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_children_direct") 
fit.brm.direct

```

###### Absent
```{r}

# removed random intercepts for scenario to avoid divergent transition errors
fit.brm.absent = brm(formula = absence ~ 1 + question*age + (1 | participant),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/cause_children_absent") 


fit.brm.absent

```

## MADE V LEXICAL (BURN & FLOOD)
### ADULTS
#### DATA
##### Read in data

```{r message=FALSE, warning=FALSE}

df.exp2_made_adults = read_csv("../../data/experiment2/made/adults/exp2_made_adults.csv")

```

##### Wrangle

```{r message=FALSE, warning=FALSE}

# clean responses
df.exp2_made_adults = df.exp2_made_adults %>% 
  mutate(condition = str_extract(string = responses,
                                 pattern = "sunburn_simple_response|sunburn_made_response|flood_simple_response|flood_made_response"),
         response = str_extract(string = responses, 
                                pattern = ":(.*)"),
         response = str_remove_all(string = response,
                                   pattern = "\""),
         response = str_remove_all(string = response,
                                   pattern = ":"),
         response = str_remove_all(string = response,
                                   pattern = "\\}"),
         response = str_remove_all(string = response,
                                   pattern = "\\."),
         response = str_remove_all(string = response,
                                   pattern = "\\,"),
         response = str_remove_all(string = response,
                                   pattern = "\\\\n"),
         response = str_to_lower(response)) %>% 
  separate(condition, c("scenario", "question", "extra"), "_") %>% 
  rename(participant = workerid) %>% 
  select(participant, scenario, question, response)

# code responses
df.exp2_made_adults = df.exp2_made_adults %>%
  mutate(direct = ifelse(str_detect(response,
                                    "^sun$|sun | sun$"), 1, 0),
         direct = ifelse(str_detect(response,
                                    "^water$|water | water$"), 1, direct),
         direct = ifelse(str_detect(response,
                                    "^rain$|rain | rain$"), 1, direct),
         absence = ifelse(str_detect(response,
                                     "^sunscreen$|sunscreen | sunscreen$"), 1, 0),
         absence = ifelse(str_detect(response,
                                     "^window$|window | window$"), 1, absence),
         absence = ifelse(str_detect(response,
                                     "^latch$|latch | latch$"), 1, absence))


## replace simple with lexical
df.exp2_made_adults = df.exp2_made_adults %>% 
  mutate(question = str_replace_all(question, "simple", "lexical"))

```

##### Demographics

```{r message=FALSE, warning=FALSE}

df.exp2_made_adults_demo = read_csv("../../data/experiment2/made/adults/exp2_made_adults_demo.csv")

df.exp2_made_adults_demo %>% 
  summarise(age_mean = mean(as.numeric(age), na.rm = TRUE))

df.exp2_made_adults_demo %>% 
  summarise(age_sd = sd(as.numeric(age), na.rm = TRUE))

df.exp2_made_adults_demo %>% 
  group_by(gender) %>% 
  count() 

df.exp2_made_adults_demo %>% 
  group_by(race) %>% 
  count() 

df.exp2_made_adults_demo %>% 
  group_by(ethnicity) %>% 
  count() 

```

#### STATS
##### Bayesian Models
###### Direct

```{r}

df.model = df.exp2_made_adults %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "made"))

# Check contrast values
 contrasts(df.model$question)

fit.brm.direct = brm(formula = direct ~ 1 + question + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/made_adult_direct") 
fit.brm.direct

```

###### Absent

```{r}

fit.brm.absent = brm(formula = absence ~ 1 + question + (1 | participant) + (1 | scenario),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/made_adult_absent") 

fit.brm.absent

```

### CHILDREN
#### DATA
##### Read in data

```{r message=FALSE, warning=FALSE}

df.exp2_made_children = read_csv("../../data/experiment2/made/children/exp2_made_children.csv")

```

##### Wrangle
```{r message=FALSE, warning=FALSE}

# clean responses
df.exp2_made_children = df.exp2_made_children %>% 
  rename(response = full_response,
         question = question_type) %>% 
  mutate(response = str_remove_all(string = response,
                                   pattern = "\""),
         response = str_remove_all(string = response,
                                   pattern = ":"),
         response = str_remove_all(string = response,
                                   pattern = "\\}"),
         response = str_remove_all(string = response,
                                   pattern = "\\."),
         response = str_remove_all(string = response,
                                   pattern = "\\,"),
         response = str_remove_all(string = response,
                                   pattern = "\\\\n"),
         response = str_to_lower(response))

# code responses
df.exp2_made_children = df.exp2_made_children %>%
  mutate(direct = ifelse(str_detect(response,
                                    "^sun$|sun | sun$"), 1, 0),
         direct = ifelse(str_detect(response,
                                    "^water$|water | water$"), 1, direct),
         direct = ifelse(str_detect(response,
                                    "^rain$|rain | rain$"), 1, direct),
         absence = ifelse(str_detect(response,
                                     "^sunscreen$|sunscreen | sunscreen$"), 1, 0),
         # note the first response in the data is 'windows' but this doesn't capture that
         absence = ifelse(str_detect(response,
                                     "^window$|window | window$"), 1, absence),
         absence = ifelse(str_detect(response,
                                     "^latch$|latch | latch$"), 1, absence)) 


# compute age and replace simple with lexical
df.exp2_made_children = df.exp2_made_children %>%
  mutate(age = round(rounded_age / 365, digits = 2),
         age_whole = as.integer(age),
         question = str_replace_all(question, "simple", "lexical")) 


```

##### Demographics

```{r}

```

#### STATS
##### Bayesian Models
###### Direct

```{r}

df.model = df.exp2_made_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "made"),
         age = age - mean(age)) 

# Check contrast values
 contrasts(df.model$question)

fit.brm.direct = brm(formula = direct ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/made_children_direct") 
fit.brm.direct

```

###### Absent
```{r}

# removed random intercepts for scenario to avoid divergent transition errors
fit.brm.absent = brm(formula = absence ~ 1 + question*age + (1 | participant),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/made_children_absent") 


fit.brm.absent

```

##PLOTS
### Data
#### Different Responses

```{r message=FALSE, warning=FALSE}

df.exp2_cause_adults_differnece = df.exp2_cause_adults %>% 
  select(question, direct, absence) %>% 
  mutate(age = rep("adults"))

df.exp2_made_adults_difference = df.exp2_made_adults %>% 
  select(question, direct, absence) %>% 
  mutate(age = rep("adults"))

df.exp2_cause_children_difference = df.exp2_cause_children %>% 
  select(question, direct, absence) %>% 
  mutate(question = str_replace_all(question, "caused", "cause")) %>% 
  mutate(age = rep("children"))

df.exp2_made_children_difference = df.exp2_made_children %>% 
  select(question, direct, absence) %>% 
  mutate(age = rep("children"))

df.difference_combined = df.exp2_cause_adults_differnece %>% 
  bind_rows(df.exp2_made_adults_difference,
            df.exp2_cause_children_difference,
            df.exp2_made_children_difference) %>% 
   mutate(response_pattern = case_when(
    direct == 1 & absence == 1 ~ "both",
    direct == 0 & absence == 0 ~ "neither",
    TRUE ~ "different"
  ))
 
df.difference_combined %>% 
  group_by(age, question, response_pattern) %>% 
  summarize(n = n()) %>% 
  ungroup() %>%
  group_by(age, question) %>% 
  mutate(percentage = n / sum(n) * 100)

```

### Difference Plots
#### Cause

```{r message=FALSE, warning=FALSE}

df.cause_children_differnet = df.exp2_cause_children %>% 
  mutate(response_pattern = case_when(
    direct == 1 & absence == 1 ~ "both",
    direct == 0 & absence == 0 ~ "neither",
    TRUE ~ "different"
  )) %>% 
  filter(response_pattern == "different")



df.model = df.cause_children_differnet %>% 
  mutate(difference = absence - direct,
        difference = recode(difference, `-1` = 0),
        question = str_replace_all(question, "caused", "cause"))


fit.brm.absence_cause.difference = brm(formula = difference ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .9999),
                     file = "cache/absence_cause_difference")


df.data = expand_grid(age = seq(4, 9, 0.1),
                      question = c("cause", "lexical"))

df.prediction = fit.brm.absence_cause.difference %>% 
  fitted(newdata = df.data,
         re_formula = NA,
          probs = c(0.1, 0.9)) %>% 
  as_tibble() %>% 
  bind_cols(df.data) %>% 
  clean_names()


df.adults = df.exp2_cause_adults %>% 
   mutate(response_pattern = case_when(
    direct == 1 & absence == 1 ~ "both",
    direct == 0 & absence == 0 ~ "neither",
    TRUE ~ "different"
  )) %>% 
  filter(response_pattern == "different") %>% 
  select(-response) %>% 
  mutate(age_whole = rep(10)) %>% 
  mutate(difference = absence - direct,
        difference = recode(difference, `-1` = 0))



df.means = df.model %>% 
  bind_rows(df.adults) %>% 
  mutate(age_whole = factor(age_whole, 
                            levels = c(4, 5, 6, 7, 8, 9, 10), 
                            labels = c("4", "5", "6", "7", "8", "9", "adults"))) %>% 
  group_by(age_whole, question) %>% 
  summarize(
    response = Hmisc::smean.cl.boot(difference)) %>%
    mutate(index = c("response", "low", "high")) %>%
    ungroup() %>% 
    pivot_wider(names_from = index,
                values_from = response) %>% 
  mutate(age_whole = fct_recode(age_whole, "10" = "adults"),
         age_whole = as.numeric(as.character(age_whole)))



p3 = ggplot(mapping = aes(x = age, 
                     y = difference,
                     color = question)) + 
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  geom_smooth(data = df.prediction,
              mapping = aes(y = estimate,
                            ymin = q10,
                            ymax = q90,
                            color = question,
                            fill = question),
              stat = "identity",
              alpha = 0.2) +
  geom_pointrange(data = df.means,
                  mapping = aes(x = age_whole,
                                y = response,
                                ymin = low,
                                ymax = high,
                                fill = question,
                                shape = question),
                  color = "black",
                  size = 0.5,
                  show.legend = FALSE,
                  alpha = 0.8,
                  position = position_dodge(width = 0.3)) +
  ylab("Probability of selecting \n absence or direct cause") +
  scale_fill_brewer(palette = "Set1") + 
  scale_color_brewer(palette = "Set1") +
  scale_shape_manual(values = c(21, 23)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = c("100% \n direct", "75%", "50%", "75%", "100% \n absent"),
                      limits = c(0, 1)) +  
 scale_x_continuous(breaks = 4:10,
                     labels = c("4", "5", "6", "7", "8", "9", "Adults")) +
  theme(plot.title = element_text(hjust = 0.5),
        legend.title = element_blank(),
        text = element_text(size = 18))


```

#### Made

```{r message=FALSE, warning=FALSE}

df.made_children_differnet = df.exp2_made_children %>% 
  mutate(response_pattern = case_when(
    direct == 1 & absence == 1 ~ "both",
    direct == 0 & absence == 0 ~ "neither",
    TRUE ~ "different"
  )) %>% 
  filter(response_pattern == "different")

df.model = df.made_children_differnet %>% 
  mutate(difference = absence - direct,
        difference = recode(difference, `-1` = 0),
         age_whole = as.integer(age))


fit.brm.absence_made.difference = brm(formula = difference ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .9999),
                     file = "cache/absence_made_difference")


df.data = expand_grid(age = seq(4, 9, 0.1),
                      question = c("made", "lexical"))

df.prediction = fit.brm.absence_made.difference %>% 
  fitted(newdata = df.data,
         re_formula = NA,
          probs = c(0.1, 0.9)) %>% 
  as_tibble() %>% 
  bind_cols(df.data) %>% 
  clean_names()



df.adults = df.exp2_made_adults %>% 
   mutate(response_pattern = case_when(
    direct == 1 & absence == 1 ~ "both",
    direct == 0 & absence == 0 ~ "neither",
    TRUE ~ "different"
  )) %>% 
  filter(response_pattern == "different") %>% 
  select(-response) %>% 
  mutate(age_whole = rep(10)) %>% 
  mutate(difference = absence - direct,
        difference = recode(difference, `-1` = 0))



df.means = df.model %>% 
  bind_rows(df.adults) %>% 
  mutate(age_whole = factor(age_whole, 
                            levels = c(4, 5, 6, 7, 8, 9, 10), 
                            labels = c("4", "5", "6", "7", "8", "9", "adults"))) %>% 
  group_by(age_whole, question) %>% 
  summarize(
    response = Hmisc::smean.cl.boot(difference)) %>%
    mutate(index = c("response", "low", "high")) %>%
    ungroup() %>% 
    pivot_wider(names_from = index,
                values_from = response) %>% 
  mutate(age_whole = fct_recode(age_whole, "10" = "adults"),
         age_whole = as.numeric(as.character(age_whole)))




p4 = ggplot(mapping = aes(x = age, 
                     y = difference,
                     color = question)) + 
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  geom_smooth(data = df.prediction,
              mapping = aes(y = estimate,
                            ymin = q10,
                            ymax = q90,
                            color = question,
                            fill = question),
              stat = "identity",
              alpha = 0.2) +
  geom_pointrange(data = df.means,
                  mapping = aes(x = age_whole,
                                y = response,
                                ymin = low,
                                ymax = high,
                                fill = question,
                                shape = question),
                  color = "black",
                  size = 0.5,
                  show.legend = FALSE,
                  alpha = 0.8,
                  position = position_dodge(width = 0.3)) +
  ylab(element_blank()) +
  scale_fill_manual(values = c("made" = "#4DAF4A", "lexical" = "#377EB8"), breaks=c("made", "lexical")) +
  scale_color_manual(values = c("made" = "#4DAF4A", "lexical" = "#377EB8"), breaks=c("made", "lexical")) +
  scale_shape_manual(values = c(23, 21)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = c("100% \n direct", "75%", "50%", "75%", "100% \n absent"),
                     limits = c(0, 1)) + 
  scale_x_continuous(breaks = 4:10,
                     labels = c("4", "5", "6", "7", "8", "9", "Adults")) +
  theme(plot.title = element_text(hjust = 0.5),
        legend.title = element_blank(),
        text = element_text(size = 18))


```

###### Combine Cause and Made Plots
```{r fig.height=4, fig.width=12}

plot = p3 + p4 + 
plot_layout(nrow = 1) &
plot_annotation(tag_levels = "A") &
theme(plot.tag = element_text(face = "bold"))

ggsave(plot, filename = "../../figures/experiment2/absence.pdf", height = 4, width = 12)

plot


```

# EXPERIMENT 3: ABSENCES 
## EXPLANATION
### ADULTS
#### DATA
##### Read in data

```{r message=FALSE, warning=FALSE}

df.exp3_adults = read_csv("../../data/experiment3/adults/exp3_adults.csv")

```

#### Wrangle

```{r message=FALSE, warning=FALSE}

# clean responses
df.exp3_adults = df.exp3_adults %>% 
  mutate(condition = str_extract(string = responses,
                                 pattern = "sunburn_simple_response|sunburn_made_response|flood_simple_response|flood_made_response"),
         response = str_extract(string = responses, 
                                pattern = ":(.*)"),
         response = str_remove_all(string = response,
                                   pattern = "\""),
         response = str_remove_all(string = response,
                                   pattern = ":"),
         response = str_remove_all(string = response,
                                   pattern = "\\}"),
         response = str_remove_all(string = response,
                                   pattern = "\\."),
         response = str_remove_all(string = response,
                                   pattern = "\\,"),
         response = str_remove_all(string = response,
                                   pattern = "\\\\n"),
         response = str_to_lower(response)) %>% 
  separate(condition, c("scenario", "question", "extra"), "_") %>% 
  rename(participant = workerid) %>% 
  select(participant, scenario, question, response)

# code responses
df.exp3_adults = df.exp3_adults %>%
  mutate(direct = ifelse(str_detect(response,
                                    "^sun$|sun | sun$"), 1, 0),
         direct = ifelse(str_detect(response,
                                    "^water$|water | water$"), 1, direct),
         direct = ifelse(str_detect(response,
                                    "^rain$|rain | rain$"), 1, direct),
         absence = ifelse(str_detect(response,
                                     "^sunscreen$|sunscreen | sunscreen$"), 1, 0),
         absence = ifelse(str_detect(response,
                                     "^window$|window | window$"), 1, absence),
         absence = ifelse(str_detect(response,
                                     "^latch$|latch | latch$"), 1, absence))


```

#### Demographics

```{r message=FALSE, warning=FALSE}

df.exp3_adults_demo = read_csv("../../data/experiment3/adults/exp3_adults_demo.csv")

df.exp3_adults_demo %>% 
  summarise(age_mean = mean(as.numeric(age), na.rm = TRUE))

df.exp3_adults_demo %>% 
  summarise(age_sd = sd(as.numeric(age), na.rm = TRUE))

df.exp3_adults_demo %>% 
  group_by(gender) %>% 
  count() 

df.exp3_adults_demo %>% 
  group_by(race) %>% 
  count() 

df.exp3_adults_demo %>% 
  group_by(ethnicity) %>% 
  count() 


```

#### STATS
##### Bayesian Model

```{r}

# dummy coding
options(contrasts = c("contr.treatment", "contr.poly"))

df.model = df.exp3_adults %>% 
  select(-response) %>% 
  pivot_longer(cols = direct:absence,
               names_to = "causal_candidate",
               values_to = "response") %>% 
mutate(causal_candidate = factor(causal_candidate, levels = c("direct", "absence")))

# check levels of causal_candidate
contrasts(df.model$causal_candidate)

fit.brm.exp = brm(formula = response ~ 1 + causal_candidate + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/explanation_adult") 
fit.brm.exp

```

### CHILDREN
#### DATA
##### Read in Data

```{r message=FALSE, warning=FALSE}

df.exp3_children = read_csv("../../data/experiment3/children/exp3_children.csv")

```

##### Wrangle

```{r message=FALSE, warning=FALSE}

# clean data
df.exp3_children = df.exp3_children %>% 
  clean_names() %>% 
  rename(response_1 = full_response_11,
         response_2 = full_response_13) %>% 
  select(participant_number, rounded_age, scenario_1, scenario_2, response_1, response_2) %>% 
 drop_na() %>% 
 pivot_longer(
    cols = c(-participant_number, -rounded_age),
    names_to = c(".value"),
    names_pattern = "(^scenario|^response)"
  ) %>% 
mutate(response = str_remove_all(string = response,
                                   pattern = "\""),
         response = str_remove_all(string = response,
                                   pattern = ":"),
       response = str_remove_all(string = response,
                                   pattern = "\\("),
       response = str_remove_all(string = response,
                                   pattern = "\\)"),
         response = str_remove_all(string = response,
                                   pattern = "\\}"),
         response = str_remove_all(string = response,
                                   pattern = "\\."),
         response = str_remove_all(string = response,
                                   pattern = "\\,"),
         response = str_remove_all(string = response,
                                   pattern = "\\\\n"),
         response = str_to_lower(response))

# code responses
df.exp3_children = df.exp3_children %>%
  mutate(direct = ifelse(str_detect(response,
                                    "^sun$|sun | sun$"), 1, 0),
         direct = ifelse(str_detect(response,
                                    "^water$|water | water$"), 1, direct),
         direct = ifelse(str_detect(response,
                                    "^rain$|rain | rain$"), 1, direct),
         absence = ifelse(str_detect(response,
                                     "^sunscreen$|sunscreen | sunscreen$"), 1, 0),
         # note the first response in the data is 'windows' but this doesn't capture that
         absence = ifelse(str_detect(response,
                                     "^window$|window | window$"), 1, absence),
         absence = ifelse(str_detect(response,
                                     "^windows$|windows | windows$"), 1, absence),
         absence = ifelse(str_detect(response,
                                     "^latch$|latch | latch$"), 1, absence),
         age = round(rounded_age / 365, digits = 2)) 
```

##### Demographics

```{r}

```

#### STATS
##### Bayesian Model

```{r}
# dummy coding
options(contrasts = c("contr.treatment", "contr.poly"))

df.model = df.exp3_children %>% 
  select(-response) %>% 
  rename(participant = participant_number) %>% 
  pivot_longer(cols = direct:absence,
               names_to = "causal_candidate",
               values_to = "response") %>% 
mutate(causal_candidate = factor(causal_candidate, levels = c("direct", "absence")))


# check levels of causal_candidate
contrasts(df.model$causal_candidate)

# removed random intercepts for scenario to avoid divergent transition errors
fit.brm.exp = brm(formula = response ~ 1 + causal_candidate + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/explanation_children") 
fit.brm.exp

```

#### PLOTS

```{r fig.height=3, fig.width=4, message=FALSE, warning=FALSE}

df.model = df.exp3_children %>% 
  select(-response) %>% 
  rename(participant = participant_number) %>% 
  pivot_longer(cols = direct:absence,
               names_to = "causal_candidate",
               values_to = "response") %>% 
mutate(causal_candidate = factor(causal_candidate, levels = c("direct", "absence")))




fit.brm.explanation = brm(formula = response ~ 1 + causal_candidate*age + (1 | participant) + (1 | scenario),
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 6000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     cores = 8,
                     file = "cache/explanation_children_age") 


fit.brm.explanation




df.data = expand_grid(age = seq(4, 6, 0.1),
                      causal_candidate = c("direct", "absence"))

df.prediction = fit.brm.explanation %>% 
  fitted(newdata = df.data,
         re_formula = NA,
          probs = c(0.1, 0.9)) %>% 
  as_tibble() %>% 
  bind_cols(df.data) %>% 
  clean_names() %>% 
  rename(type = causal_candidate) %>% 
  mutate(type = ifelse(type == "direct", "direct (sun, rain)", "absent (sunscreen, latch)"))

df.adults = df.exp3_adults %>% 
  select(-response) %>% 
  mutate(age_whole = rep(7)) %>% 
  pivot_longer(cols = (direct:absence),
    names_to = "type",
    values_to = "response")


df.children = df.exp3_children %>% 
  select(-response) %>% 
  mutate(age_whole = as.integer(age)) %>% 
  pivot_longer(cols = (direct:absence),
    names_to = "type",
    values_to = "response")


df.means = df.children %>% 
  bind_rows(df.adults) %>% 
  mutate(age_whole = factor(age_whole, 
                            levels = c(4, 5, 6, 7), 
                            labels = c("4", "5", "6","adults"))) %>% 
  group_by(age_whole, question, type) %>% 
  summarize(
    response = Hmisc::smean.cl.boot(response)) %>%
    mutate(index = c("response", "low", "high")) %>%
    ungroup() %>% 
    pivot_wider(names_from = index,
                values_from = response) %>% 
  mutate(age_whole = fct_recode(age_whole, "7" = "adults"),
         age_whole = as.numeric(as.character(age_whole)),
         type = ifelse(type == "direct", "direct (sun, rain)", "absent (sunscreen, latch)"))




ggplot(mapping = aes(x = age, 
                     y = response,
                     color = type)) + 
  geom_hline(yintercept=0.50, linetype="dashed", color = "black") +
  geom_smooth(data = df.prediction,
              mapping = aes(y = estimate,
                            ymin = q10,
                            ymax = q90,
                            color = type,
                            fill = type),
              stat = "identity",
              alpha = 0.2) +
  geom_pointrange(data = df.means,
                  mapping = aes(x = age_whole,
                                y = response,
                                ymin = low,
                                ymax = high,
                                fill = type,
                                shape = type),
                  color = "black",
                  size = 0.5,
                  show.legend = FALSE,
                  alpha = 0.8,
                  position = position_dodge(width = 0.1)) +
  ylab("Probability of selecting \n causal candidate") +
   scale_fill_manual(values = c("direct (sun, rain)" = "#FF7F00", "absent (sunscreen, latch)" = "#984EA3"), breaks=c("absent (sunscreen, latch)", "direct (sun, rain)"), guide = guide_legend(nrow = 2)) +
  scale_color_manual(values = c("direct (sun, rain)" = "#FF7F00", "absent (sunscreen, latch)" = "#984EA3"), breaks=c("absent (sunscreen, latch)", "direct (sun, rain)"), guide = guide_legend(nrow = 2)) +
  scale_shape_manual(values = c(21, 23), guide = guide_legend(nrow = 2)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = str_c(seq(0, 1, 0.25) * 100, "%"),
                     limits = c(0, 1)) +
  scale_x_continuous(breaks = 4:7,
                     labels = c("4", "5", "6", "Adults")) +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = "bottom",
        legend.title = element_blank())



ggsave("../../figures/experiment3/explanation.pdf", height = 3, width = 4)

```
