---
title: "Cause and Burn in Development"
author: "David Rose, Siying Zhang, Shaun Nichols, Ellen Markman & Tobias Gerstenberg"
date: "`r Sys.Date()`"
output:
  bookdown::html_document2:
    toc: true
    toc_depth: 6
    theme: cosmo
    highlight: tango
---

# Load packages
```{r eval=TRUE, include=FALSE, message=FALSE, warning=FALSE}

library("janitor")        # for cleaning variable nqmes
library("emmeans")        # for comparing means
library("brms")           # for Bayesian data analysis
library("patchwork")      # for combining figures
library("knitr")          # for knitting 
library("tidyverse")      # for everything else

```

# Settings

```{r message=FALSE, warning=FALSE}

# set theme 
theme_set(theme_classic())

# sum coding
options(contrasts = c("contr.sum","contr.poly"))

# suppress grouping warning 
options(dplyr.summarise.inform = F)
```

# EXPERIMENT 1: CHAINS
## CAUSE V LEXICAL (BREAK & CRACK)
### ADULTS
#### DATA
##### Read in data
```{r message=FALSE, warning=FALSE}

df.exp1_cause_adults = read_csv("../../data/experiment1/cause/adults/exp1_cause_adults.csv")

```

##### Wrangle 

```{r message=FALSE, warning=FALSE}

df.exp1_cause_adults = df.exp1_cause_adults %>% 
  mutate(participant = 1:n()) %>% 
  select(participant, break_cause_processed, break_simple_processed, crack_cause_processed, crack_simple_processed, counterbalance) %>% 
  pivot_longer(-c(participant,counterbalance),
               names_to = "tmp_name",
               values_to = "response") %>% 
  separate(.,
           col = tmp_name,
           into = c("verb", "question", "tmp"),
           sep = "_") %>% 
  select(-tmp) %>% 
  mutate(distal = ifelse(counterbalance == "order_1" & str_detect(response,
                                                                  "Andy|Sophia"), 1, 0),
         distal = ifelse(counterbalance == "order_2" & str_detect(response,
                                                                  "Suzy|Bobby"), 1, distal),
         proximal = ifelse(counterbalance == "order_1" & str_detect(response,
                                                                    "Suzy|Bobby"), 1, 0),
         proximal = ifelse(counterbalance == "order_2" & str_detect(response,
                                                                    "Andy|Sophia"), 1, proximal), 
         question = str_replace_all(question, "simple", "lexical"),
         question = str_replace_all(question, "cause", "caused")) %>% 
  rename(scenario = verb)

```

##### Demographics

```{r message=FALSE, warning=FALSE}

df.exp1_cause_adults_demo = read_csv("../../data/experiment1/cause/adults/exp1_cause_adults_demo.csv")

df.exp1_cause_adults_demo  %>% 
  summarise(age_mean = mean(as.numeric(age), na.rm = TRUE))

df.exp1_cause_adults_demo  %>% 
  summarise(age_sd = sd(as.numeric(age), na.rm = TRUE))

df.exp1_cause_adults_demo  %>% 
  group_by(gender) %>% 
  count() 

df.exp1_cause_adults_demo  %>% 
  group_by(race) %>% 
  count() 

```


#### STATS
##### Bayesian Model

```{r message=FALSE, warning=FALSE}


df.cause_adults_differnet = df.exp1_cause_adults %>%
  mutate(response_pattern = case_when(
    distal == 1 & proximal == 1 ~ "both",
    distal == 0 & proximal == 0 ~ "neither",
    TRUE ~ "different"
  )) %>%
  filter(response_pattern == "different") %>%
  mutate(difference = distal - proximal,
        difference = recode(difference, `-1` = 0))

df.cause_adults_both = df.exp1_cause_adults %>%
  mutate(response_pattern = case_when(
    distal == 1 & proximal == 1 ~ "both",
    distal == 0 & proximal == 0 ~ "neither",
    TRUE ~ "different"
  )) %>%
  filter(response_pattern == "both")
  
  
df.cause_adults_both = df.cause_adults_both %>% 
  mutate(difference = 1) %>%
  bind_rows(df.cause_adults_both %>% 
              mutate(difference = 0)) 

df.model = df.cause_adults_differnet %>% 
  bind_rows(df.cause_adults_both) %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "caused"))

# Check contrast values
 contrasts(df.model$question)


fit.brm.cause.adult = brm(formula = difference ~ 1 + question + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/chain_cause_adult_difference") 

fit.brm.cause.adult


```


### CHILDREN
#### DATA
##### Read in data

```{r message=FALSE, warning=FALSE}

df.exp1_cause_children = read_csv("../../data/experiment1/cause/children/exp1_cause_children.csv")

```

##### Wrangle
```{r message=FALSE, warning=FALSE}

#clean data
df.exp1_cause_children = df.exp1_cause_children %>% 
  clean_names() %>% 
  rename(
         question = question_type) %>% 
  mutate(response = str_remove_all(string = response,
                                   pattern = "\""),
         response = str_remove_all(string = response,
                                   pattern = ":"),
         response = str_remove_all(string = response,
                                   pattern = "\\}"),
         response = str_remove_all(string = response,
                                   pattern = "\\."),
         response = str_remove_all(string = response,
                                   pattern = "\\,"),
         response = str_remove_all(string = response,
                                   pattern = "\\\\n"),
         response = str_to_lower(response)) %>% 
  select(-(response_id : age_range), -notes, -full_response) 


# code responses
df.exp1_cause_children = df.exp1_cause_children %>% 
  mutate(distal = ifelse(counterbalance == "andy" & str_detect(response, "andy"), 1, 0),
         distal = ifelse(counterbalance == "suzy" & str_detect(response, "suzy"), 1, distal),
         distal = ifelse(counterbalance == "bobby" & str_detect(response, "bobby"), 1, distal),
         distal = ifelse(counterbalance == "sophia" & str_detect(response, "sophia"), 1, distal),
         proximal = ifelse(counterbalance == "andy" & str_detect(response, "suzy"), 1, 0),
         proximal = ifelse(counterbalance == "suzy" & str_detect(response, "andy"), 1, proximal),
         proximal = ifelse(counterbalance == "bobby" & str_detect(response, "sophia"), 1, proximal),
         proximal = ifelse(counterbalance == "sophia" & str_detect(response, "bobby"), 1, proximal),
         age = round(rounded_age / 365, digits = 2),
         question = str_replace_all(question, "break|crack", "simple")) %>% 
  na.omit()

# compute age and replace simple with lexical
df.exp1_cause_children = df.exp1_cause_children %>% 
  mutate(age_whole = as.integer(age)) %>%
  mutate(age_character = as.character(age_whole)) %>%
  mutate(age_character = recode(age_character, "7" = "7-9", "8" = "7-9", "9" = "7-9"),
         question = str_replace_all(question, "simple", "lexical")) %>%
  rename(participant = participant_number) 
 
```

##### Demographics

```{r message=FALSE, warning=FALSE}

 # gender
df.exp1_cause_children %>%
  group_by(gender) %>%
  summarise(n = n_distinct(participant)) %>%
  print()

  
  # language spoken
df.exp1_cause_children %>%
    mutate(en_occurrence = ifelse(str_detect(lan_spoken, "en"), "en", "non-en")) %>%
    group_by(en_occurrence) %>%
    summarise(n = n_distinct(participant)) %>%
    print()


```

#### STATS


##### Bayesian Model
```{r message=FALSE, warning=FALSE}


df.cause_children_differnet = df.exp1_cause_children %>%
  mutate(response_pattern = case_when(
    distal == 1 & proximal == 1 ~ "both",
    distal == 0 & proximal == 0 ~ "neither",
    TRUE ~ "different"
  )) %>%
  filter(response_pattern == "different") %>%
  mutate(difference = distal - proximal,
        difference = recode(difference, `-1` = 0))

df.cause_children_both = df.exp1_cause_children %>%
  mutate(response_pattern = case_when(
    distal == 1 & proximal == 1 ~ "both",
    distal == 0 & proximal == 0 ~ "neither",
    TRUE ~ "different"
  )) %>%
  filter(response_pattern == "both") 


 df.cause_children_both = df.cause_children_both %>% 
  mutate(difference = 1) %>%
  bind_rows(df.cause_children_both %>% 
              mutate(difference = 0)) 

df.model = df.cause_children_differnet %>% 
  bind_rows(df.cause_children_both) %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "caused"))



# Check contrast values
 contrasts(df.model$question)


fit.brm.cause.children = brm(formula = difference ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/chain_cause_children_difference") 

fit.brm.cause.children


```

## MADE v LEXICAL (BREAK & CRACK)
### ADULTS
#### DATA
##### Read in data

```{r message=FALSE, warning=FALSE}

df.exp1_made_adults = read_csv("../../data/experiment1/made/adults/exp1_made_adults.csv")

```

##### Wrangle

```{r message=FALSE, warning=FALSE}

df.exp1_made_adults = df.exp1_made_adults %>% 
  mutate(participant = 1:n()) %>% 
  select(participant, break_cause_processed, break_simple_processed, crack_cause_processed, crack_simple_processed, counterbalance) %>% 
  pivot_longer(-c(participant,counterbalance),
               names_to = "tmp_name",
               values_to = "response") %>% 
  separate(.,
           col = tmp_name,
           into = c("verb", "question", "tmp"),
           sep = "_") %>% 
  select(-tmp) %>% 
  mutate(distal = ifelse(counterbalance == "order_1" & str_detect(response,
                                    "Andy|Sophia"), 1, 0),
         distal = ifelse(counterbalance == "order_2" & str_detect(response,
                                    "Suzy|Bobby"), 1, distal),
         proximal = ifelse(counterbalance == "order_1" & str_detect(response,
                                    "Suzy|Bobby"), 1, 0),
         proximal = ifelse(counterbalance == "order_2" & str_detect(response,
                                    "Andy|Sophia"), 1, proximal),
         question = str_replace_all(question, "cause", "made"),
         question = str_replace_all(question, "simple", "lexical")) %>% 
  rename(scenario = verb)

```

##### Demographics

```{r message=FALSE, warning=FALSE}

df.exp1_made_adults_demo = read_csv("../../data/experiment1/made/adults/exp1_made_adults_demo.csv")

df.exp1_made_adults_demo %>% 
  summarise(age_mean = mean(as.numeric(age), na.rm = TRUE))

df.exp1_made_adults_demo %>% 
  summarise(age_sd = sd(as.numeric(age), na.rm = TRUE))

df.exp1_made_adults_demo %>% 
  group_by(gender) %>% 
  count() 

df.exp1_made_adults_demo %>% 
  group_by(race) %>% 
  count() 

```

#### STATS



##### Bayesian Model

```{r message=FALSE, warning=FALSE}


df.made_adults_differnet = df.exp1_made_adults %>%
  mutate(response_pattern = case_when(
    distal == 1 & proximal == 1 ~ "both",
    distal == 0 & proximal == 0 ~ "neither",
    TRUE ~ "different"
  )) %>%
  filter(response_pattern == "different") %>%
  mutate(difference = distal - proximal,
        difference = recode(difference, `-1` = 0))

df.made_adults_both = df.exp1_made_adults %>%
  mutate(response_pattern = case_when(
    distal == 1 & proximal == 1 ~ "both",
    distal == 0 & proximal == 0 ~ "neither",
    TRUE ~ "different"
  )) %>%
  filter(response_pattern == "both")


df.made_adults_both = df.made_adults_both %>% 
  mutate(difference = 1) %>%
  bind_rows(df.made_adults_both %>% 
              mutate(difference = 0)) 

df.model = df.made_adults_differnet %>% 
  bind_rows(df.made_adults_both) %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "caused"))

# Check contrast values
 contrasts(df.model$question)


fit.brm.made.adult = brm(formula = difference ~ 1 + question + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/chain_made_adult_difference") 

fit.brm.made.adult


```

### CHILDREN
#### DATA
##### Read in data

```{r message=FALSE, warning=FALSE}

df.exp1_made_children = read_csv("../../data/experiment1/made/children/exp1_made_children.csv")

```

##### Wrangle

```{r message=FALSE, warning=FALSE}

#clean data
df.exp1_made_children = df.exp1_made_children %>% 
  clean_names() %>% 
  rename(
         question = question_type) %>% 
  mutate(response = str_to_lower(response),
         counterbalance = str_to_lower(counterbalance)) %>% 
  select(-(response_id : age_range), -notes, -full_response) 

#code responses
df.exp1_made_children = df.exp1_made_children %>% 
  mutate(distal = ifelse(counterbalance == "andy" & str_detect(response, "andy"), 1, 0),
         distal = ifelse(counterbalance == "suzy" & str_detect(response, "suzy"), 1, distal),
         distal = ifelse(counterbalance == "bobby" & str_detect(response, "bobby"), 1, distal),
         distal = ifelse(counterbalance == "sophia" & str_detect(response, "sophia"), 1, distal),
         proximal = ifelse(counterbalance == "andy" & str_detect(response, "suzy"), 1, 0),
         proximal = ifelse(counterbalance == "suzy" & str_detect(response, "andy"), 1, proximal),
         proximal = ifelse(counterbalance == "bobby" & str_detect(response, "sophia"), 1, proximal),
         proximal = ifelse(counterbalance == "sophia" & str_detect(response, "bobby"), 1, proximal),
         age = round(rounded_age / 365, digits = 2),
         question = str_replace_all(question, "break|crack", "simple")) %>% 
  na.omit()

# compute age and recode question
df.exp1_made_children = df.exp1_made_children %>% 
  mutate(age_whole =as.integer(age)) %>%
  mutate(age_character = as.character(age_whole)) %>%
  mutate(age_character = recode(age_character, "7" = "7-9", "8" = "7-9", "9" = "7-9"),
         question = str_replace_all(question, "simple", "lexical"),
         scenario = str_replace_all(scenario, "mirror_break", "mirror_crack")) %>%
  rename(participant = participant_number) 

```

##### Demographics
```{r message=FALSE, warning=FALSE}

 # gender
df.exp1_made_children %>%
  group_by(gender) %>%
  summarise(n = n_distinct(participant)) %>%
  print()
  
  
  # language spoken
df.exp1_made_children %>%
    mutate(en_occurrence = ifelse(str_detect(lan_spoken, "en"), "en", "non-en")) %>%
    group_by(en_occurrence) %>%
    summarise(n = n_distinct(participant)) %>%
    print()

```

#### STATS



##### Bayesian Model
```{r message=FALSE, warning=FALSE}


df.made_children_differnet = df.exp1_made_children %>%
  mutate(response_pattern = case_when(
    distal == 1 & proximal == 1 ~ "both",
    distal == 0 & proximal == 0 ~ "neither",
    TRUE ~ "different"
  )) %>%
  filter(response_pattern == "different") %>%
  mutate(difference = distal - proximal,
        difference = recode(difference, `-1` = 0))

df.made_children_both = df.exp1_made_children %>%
  mutate(response_pattern = case_when(
    distal == 1 & proximal == 1 ~ "both",
    distal == 0 & proximal == 0 ~ "neither",
    TRUE ~ "different"
  )) %>%
  filter(response_pattern == "both")

df.made_children_both = df.made_children_both %>% 
  mutate(difference = 1) %>%
  bind_rows(df.made_children_both %>% 
              mutate(difference = 0)) 

df.model = df.made_children_differnet %>% 
  bind_rows(df.made_children_both) %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "caused"))


# Check contrast values
 contrasts(df.model$question)
 


fit.brm.made.children = brm(formula = difference ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/chain_made_children_difference") 

fit.brm.made.children


```

## PLOTS
### Data
#### Different Responses

```{r message=FALSE, warning=FALSE}

df.exp1_cause_adults_differnece = df.exp1_cause_adults %>%
  select(question, distal, proximal) %>%
  mutate(age = rep("adults"))

df.exp1_made_adults_difference = df.exp1_made_adults %>%
  select(question, distal, proximal) %>%
  mutate(age = rep("adults"))

df.exp1_cause_children_difference = df.exp1_cause_children %>%
  select(question, distal, proximal) %>%
  mutate(question = str_replace_all(question, "caused", "cause")) %>%
  mutate(age = rep("children"))

df.exp1_made_children_difference = df.exp1_made_children %>%
  select(question, distal, proximal) %>%
  mutate(age = rep("children"))

df.difference_combined = df.exp1_cause_adults_differnece %>%
  bind_rows(df.exp1_made_adults_difference,
            df.exp1_cause_children_difference,
            df.exp1_made_children_difference) %>%
   mutate(response_pattern = case_when(
    distal == 1 & proximal == 1 ~ "both",
    distal == 0 & proximal == 0 ~ "neither",
    TRUE ~ "different"
  ))

df.difference_combined %>%
  group_by(age, question, response_pattern) %>%
  summarize(n = n()) %>%
  ungroup() %>%
  group_by(age, question) %>%
  mutate(percentage = n / sum(n) * 100)

```

### Different Responses Plots
#### Cause
```{r message=FALSE, warning=FALSE}

df.cause_children_differnet = df.exp1_cause_children %>%
  mutate(response_pattern = case_when(
    distal == 1 & proximal == 1 ~ "both",
    distal == 0 & proximal == 0 ~ "neither",
    TRUE ~ "different"
  )) %>%
  filter(response_pattern == "different")


df.model = df.cause_children_differnet %>%
  mutate(difference = distal - proximal,
        difference = recode(difference, `-1` = 0),
        question = str_replace_all(question, "caused", "cause"))


fit.brm.chain_cause.difference = brm(formula = difference ~ 1 + question*age + (1 | participant) + (1 | scenario),
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .9999),
                     file = "cache/chain_cause_difference")


df.data = expand_grid(age = seq(4, 9, 0.1),
                      question = c("cause", "lexical"))

df.prediction = fit.brm.chain_cause.difference %>%
  fitted(newdata = df.data,
         re_formula = NA,
          probs = c(0.1, 0.9)) %>%
  as_tibble() %>%
  bind_cols(df.data) %>%
  clean_names()


df.adults = df.exp1_cause_adults %>%
  mutate(response_pattern = case_when(
    distal == 1 & proximal == 1 ~ "both",
    distal == 0 & proximal == 0 ~ "neither",
    TRUE ~ "different"
  )) %>%
  filter(response_pattern == "different") %>%
  select(-response) %>%
  mutate(age_whole = rep(10)) %>%
  mutate(difference = distal - proximal,
         difference = recode(difference, `-1` = 0))



df.means = df.model %>%
  bind_rows(df.adults) %>%
  mutate(age_whole = factor(age_whole,
                            levels = c(4, 5, 6, 7, 8, 9, 10),
                            labels = c("4", "5", "6", "7", "8", "9", "adults"))) %>%
  group_by(age_whole, question) %>%
  summarize(
    response = Hmisc::smean.cl.boot(difference)) %>%
    mutate(index = c("response", "low", "high")) %>%
    ungroup() %>%
    pivot_wider(names_from = index,
                values_from = response) %>%
  mutate(age_whole = fct_recode(age_whole, "10" = "adults"),
         age_whole = as.numeric(as.character(age_whole)))



p1 = ggplot(mapping = aes(x = age,
                     y = difference,
                     color = question)) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  geom_smooth(data = df.prediction,
              mapping = aes(y = estimate,
                            ymin = q10,
                            ymax = q90,
                            color = question,
                            fill = question),
              stat = "identity",
              alpha = 0.2,
              show.legend = F) +
  geom_pointrange(data = df.means,
                  mapping = aes(x = age_whole,
                                y = response,
                                ymin = low,
                                ymax = high,
                                fill = question,
                                shape = question),
                  color = "black",
                  size = 0.5,
                  show.legend = TRUE,
                  alpha = 0.8,
                  position = position_dodge(width = 0.3)) +
  scale_fill_manual(values = c("cause" = "#E41A1C",
                               "lexical" = "#377EB8")) +
  scale_color_manual(values = c("cause" = "#E41A1C",
                                "lexical" = "#377EB8")) +
  scale_shape_manual(values = c("cause" = 21,
                               "lexical" = 23)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = c("100% \n proximal", "75%", "50%", "75%", "100% \n distal"),
                      limits = c(0, 1)) +
 scale_x_continuous(breaks = 4:10,
                     labels = c("4", "5", "6", "7", "8", "9", "Adults")) +
  labs(y = "Probability of selecting \n proximal or distal cause") +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        text = element_text(size = 18)) +
  guides(fill = "none",
         color = "none",
         shape = guide_legend(override.aes = list(fill = c("#377EB8", "#E41A1C")),
                              reverse = T))


```


#### Made
```{r message=FALSE, warning=FALSE}

df.made_children_differnet = df.exp1_made_children %>%
  mutate(response_pattern = case_when(
    distal == 1 & proximal == 1 ~ "both",
    distal == 0 & proximal == 0 ~ "neither",
    TRUE ~ "different"
  )) %>%
  filter(response_pattern == "different")

df.model = df.made_children_differnet %>%
  mutate(difference = distal - proximal,
        difference = recode(difference, `-1` = 0))


fit.brm.chain_made.difference = brm(formula = difference ~ 1 + question*age + (1 | participant) + (1 | scenario),
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .9999),
                     file = "cache/chain_made_difference")


df.data = expand_grid(age = seq(4, 9, 0.1),
                      question = c("made", "lexical"))

df.prediction = fit.brm.chain_made.difference %>%
  fitted(newdata = df.data,
         re_formula = NA,
          probs = c(0.1, 0.9)) %>%
  as_tibble() %>%
  bind_cols(df.data) %>%
  clean_names()



df.adults = df.exp1_made_adults %>%
    mutate(response_pattern = case_when(
    distal == 1 & proximal == 1 ~ "both",
    distal == 0 & proximal == 0 ~ "neither",
    TRUE ~ "different"
  )) %>%
  filter(response_pattern == "different") %>%
  select(-response) %>%
  mutate(age_whole = rep(10)) %>%
  mutate(difference = distal - proximal,
        difference = recode(difference, `-1` = 0))



df.means = df.model %>%
  bind_rows(df.adults) %>%
  mutate(age_whole = factor(age_whole,
                            levels = c(4, 5, 6, 7, 8, 9, 10),
                            labels = c("4", "5", "6", "7", "8", "9", "adults"))) %>%
  group_by(age_whole, question) %>%
  summarize(
    response = Hmisc::smean.cl.boot(difference)) %>%
    mutate(index = c("response", "low", "high")) %>%
    ungroup() %>%
    pivot_wider(names_from = index,
                values_from = response) %>%
  mutate(age_whole = fct_recode(age_whole, "10" = "adults"),
         age_whole = as.numeric(as.character(age_whole)))




p2 = ggplot(mapping = aes(x = age,
                          y = difference,
                          color = question)) +
  geom_hline(yintercept = 0.5,
             linetype = "dashed",
             color = "black") +
  geom_smooth(data = df.prediction,
              mapping = aes(y = estimate,
                            ymin = q10,
                            ymax = q90,
                            color = question,
                            fill = question),
              stat = "identity",
              alpha = 0.2,
              show.legend = F) +
  geom_pointrange(data = df.means,
                  mapping = aes(x = age_whole,
                                y = response,
                                ymin = low,
                                ymax = high,
                                fill = question,
                                shape = question),
                  color = "black",
                  size = 0.5,
                  show.legend = TRUE,
                  alpha = 0.8,
                  position = position_dodge(width = 0.3)) +
  scale_fill_manual(values = c("made" = "#4DAF4A",
                               "lexical" = "#377EB8"),
                    breaks = c("made",
                               "lexical")) +
  scale_color_manual(values = c("made" = "#4DAF4A",
                                "lexical" = "#377EB8"),
                     breaks= c("made", "lexical")) +
  scale_shape_manual(values = c("made" = 21,
                               "lexical" = 23)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = c("100% \n proximal", "75%", "50%", "75%", "100% \n distal"),
                     limits = c(0, 1)) +
  scale_x_continuous(breaks = 4:10,
                     labels = c("4", "5", "6", "7", "8", "9", "Adults")) +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        axis.title.y = element_blank(),
        text = element_text(size = 18)) +
  guides(fill = "none",
         color = "none",
         shape = guide_legend(override.aes = list(fill = c("#377EB8", "#4DAF4A"))))

```

#### Combine Cause and Made Plots

```{r fig.height=5, fig.width=12, message=FALSE, warning=FALSE}

plot = p1 + p2 +
plot_layout(nrow = 1) &
plot_annotation(tag_levels = "A") &
theme(plot.tag = element_text(face = "bold"))

ggsave(plot, filename = "../../figures/experiment1/chain_different.pdf", height = 5, width = 12)

plot


```




#### Responses Patterns Overall
```{r}

df.plot = df.exp1_cause_adults %>% 
  mutate(age = "adults") %>% 
  bind_rows(df.exp1_made_adults %>% 
              mutate(age = "adults")) %>% 
  bind_rows(df.exp1_cause_children %>% 
              mutate(age = "children")) %>% 
  bind_rows(df.exp1_made_children %>% 
              mutate(age = "children")) %>% 
  mutate(response_pattern = case_when(
    distal == 1 & proximal == 1 ~ "both",
    distal == 0 & proximal == 0 ~ "neither",
    distal == 1 & proximal == 0  ~ "distal only",
    distal == 0 & proximal == 1  ~ "proximal only",
  ),
  question = recode(question, "cause" = "caused")) %>% 
  group_by(age, question, response_pattern) %>% 
  summarize(n = n()) %>% 
  ungroup() %>%
  group_by(age, question) %>%
  mutate(percentage = n / sum(n) * 100) %>%
  ungroup() %>% 
  mutate(question = factor(question, levels = c("caused", "made", "lexical")),
         response_pattern = factor(response_pattern, levels = c("distal only", "proximal only", "both", "neither")))


ggplot(data = df.plot,
       mapping = aes(x = age,
                     y = percentage,
                     group = response_pattern,
                     color = response_pattern,
                     fill = response_pattern)) +
  geom_col(color = "black") +
  scale_fill_brewer(palette = "Set1") + 
  scale_color_brewer(palette = "Set1") +
  scale_shape_manual(values = c(21, 23)) +
  scale_y_continuous(breaks = seq(0, 100, 25),
                     labels = str_c(seq(0, 100, 25), "%")) +
  labs(y = "Response pattern \n\ probability") +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        text = element_text(size = 18),
        axis.title.x = element_blank()) +
  facet_wrap(~question)

ggsave("../../figures/experiment1/chain_response_patterns.pdf", height = 4, width = 8)

```

#### Responses Patterns by Age
##### Cause v Lexical
```{r}

df.plot = df.exp1_cause_adults %>% 
  mutate(age_whole = 10) %>% 
  bind_rows(df.exp1_cause_children) %>% 
  mutate(response_pattern = case_when(
    distal == 1 & proximal == 1 ~ "both",
    distal == 0 & proximal == 0 ~ "neither",
    distal == 1 & proximal == 0  ~ "distal only",
    distal == 0 & proximal == 1  ~ "proximal only",
  ),
  question = recode(question, "cause" = "caused"),
  age_whole = as.factor(age_whole)) %>% 
  group_by(age_whole, question, response_pattern) %>% 
  summarize(n = n()) %>% 
  ungroup() %>%
  group_by(age_whole, question) %>%
  mutate(percentage = n / sum(n) * 100) %>%
  ungroup() %>% 
  mutate(question = factor(question, levels = c("caused", "lexical")),
         response_pattern = factor(response_pattern, levels = c("distal only", "proximal only", "both", "neither")))


p1 = ggplot(data = df.plot,
       mapping = aes(x = age_whole,
                     y = percentage,
                     group = response_pattern,
                     color = response_pattern,
                     fill = response_pattern)) +
  geom_col(color = "black") +
  scale_fill_brewer(palette = "Set1") + 
  scale_color_brewer(palette = "Set1") +
  scale_shape_manual(values = c(21, 23)) +
  scale_y_continuous(breaks = seq(0, 100, 25),
                     labels = str_c(seq(0, 100, 25), "%")) +
  scale_x_discrete(breaks = 4:10,
                     labels = c("4", "5", "6", "7", "8", "9", "Adults")) +
  labs(y = "Response pattern \n\ probability") +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        text = element_text(size = 18),
        axis.title.x = element_blank()) +
  facet_wrap(~question)

# ggsave("../../figures/experiment1/chain_response_patterns_age.pdf", height = 4, width = 8)

```

##### Made v Lexical
```{r}

df.plot = df.exp1_made_adults %>% 
  mutate(age_whole = 10) %>% 
  bind_rows(df.exp1_made_children) %>% 
  mutate(response_pattern = case_when(
    distal == 1 & proximal == 1 ~ "both",
    distal == 0 & proximal == 0 ~ "neither",
    distal == 1 & proximal == 0  ~ "distal only",
    distal == 0 & proximal == 1  ~ "proximal only",
  ),
  age_whole = as.factor(age_whole)) %>% 
  group_by(age_whole, question, response_pattern) %>% 
  summarize(n = n()) %>% 
  ungroup() %>%
  group_by(age_whole, question) %>%
  mutate(percentage = n / sum(n) * 100) %>%
  ungroup() %>% 
  mutate(question = factor(question, levels = c("made", "lexical")),
         response_pattern = factor(response_pattern, levels = c("distal only", "proximal only", "both", "neither")))


p2 = ggplot(data = df.plot,
       mapping = aes(x = age_whole,
                     y = percentage,
                     group = response_pattern,
                     color = response_pattern,
                     fill = response_pattern)) +
  geom_col(color = "black") +
  scale_fill_brewer(palette = "Set1") + 
  scale_color_brewer(palette = "Set1") +
  scale_shape_manual(values = c(21, 23)) +
  scale_y_continuous(breaks = seq(0, 100, 25),
                     labels = str_c(seq(0, 100, 25), "%")) +
  scale_x_discrete(breaks = 4:10,
                     labels = c("4", "5", "6", "7", "8", "9", "Adults")) +
  labs(y = "Response pattern \n\ probability") +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        text = element_text(size = 18),
        axis.title.x = element_blank()) +
  facet_wrap(~question)

# ggsave("../../figures/experiment1/chain_response_patterns_age.pdf", height = 4, width = 8)

```
##### Combine Cause and Made Plots
```{r fig.height=5, fig.width=18, message=FALSE, warning=FALSE}

plot = p1 + p2 + 
plot_layout(nrow = 1) &
plot_annotation(tag_levels = "A") &
theme(plot.tag = element_text(face = "bold"))

ggsave(plot, filename = "../../figures/experiment1/chain_response_patterns_age.pdf", height = 5, width = 18)

plot


```



# EXPERIMENT 2: ABSENCES
## CAUSE V LEXICAL (BURN & FLOOD)
### ADULTS
#### DATA
##### Read in data

```{r message=FALSE, warning=FALSE}

df.exp2_cause_adults = read_csv("../../data/experiment2/cause/adults/exp2_cause_adults.csv")

```

##### Wrangle
```{r message=FALSE, warning=FALSE}

# clean data
df.exp2_cause_adults = df.exp2_cause_adults %>% 
  mutate(condition = str_extract(string = responses,
                                 pattern = "sunburn_simple_response|sunburn_cause_response|flood_simple_response|flood_cause_response"),
         response = str_extract(string = responses, 
                                pattern = ":(.*)"),
         response = str_remove_all(string = response,
                                   pattern = "\""),
         response = str_remove_all(string = response,
                                   pattern = ":"),
         response = str_remove_all(string = response,
                                   pattern = "\\}"),
         response = str_remove_all(string = response,
                                   pattern = "\\."),
         response = str_remove_all(string = response,
                                   pattern = "\\,"),
         response = str_remove_all(string = response,
                                   pattern = "\\\\n"),
         response = str_to_lower(response)) %>% 
  separate(condition, c("scenario", "question", "extra"), "_") %>% 
  rename(participant = workerid) %>% 
  select(participant, scenario, question, response)

# code responses
df.exp2_cause_adults = df.exp2_cause_adults %>%
  mutate(direct = ifelse(str_detect(response,
                                    "^sun$|sun | sun$"), 1, 0),
         direct = ifelse(str_detect(response,
                                    "^water$|water | water$"), 1, direct),
         direct = ifelse(str_detect(response,
                                    "^rain$|rain | rain$"), 1, direct),
         absence = ifelse(str_detect(response,
                                     "^sunscreen$|sunscreen | sunscreen$"), 1, 0),
         absence = ifelse(str_detect(response,
                                     "^window$|window | window$"), 1, absence),
         absence = ifelse(str_detect(response,
                                     "^latch$|latch | latch$"), 1, absence))

## replace simple with lexical
df.exp2_cause_adults = df.exp2_cause_adults %>% 
  mutate(question = str_replace_all(question, "simple", "lexical"),
         question = str_replace_all(question, "cause", "caused"))


```

##### Demographics

```{r message=FALSE, warning=FALSE}

df.exp2_cause_adults_demo = read_csv("../../data/experiment2/cause/adults/exp2_cause_adults_demo.csv")

df.exp2_cause_adults_demo %>% 
  summarise(age_mean = mean(as.numeric(age), na.rm = TRUE))

df.exp2_cause_adults_demo %>% 
  summarise(age_sd = sd(as.numeric(age), na.rm = TRUE))

df.exp2_cause_adults_demo %>% 
  group_by(gender) %>% 
  count() 

df.exp2_cause_adults_demo %>% 
  group_by(race) %>% 
  count() 

df.exp2_cause_adults_demo %>% 
  group_by(ethnicity) %>% 
  count() 

```

#### STATS

##### Descriptives
```{r} 

df.exp2_cause_adults %>% 
  mutate(response_pattern = case_when(
    direct == 1 & absence == 1 ~ "both",
    direct == 0 & absence == 0 ~ "neither",
    direct == 1 & absence == 0  ~ "direct only",
    direct == 0 & absence == 1  ~ "absence only",
  )) %>% 
  group_by(question, response_pattern) %>% 
  summarize(n = n()) %>% 
  ungroup() %>%
  group_by(question) %>%
  mutate(percentage = n / sum(n) * 100) %>%
  ungroup()


```

##### Bayesian Models
###### Direct

```{r message=FALSE, warning=FALSE}

df.model = df.exp2_cause_adults  %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "cause"))

# Check contrast values
 contrasts(df.model$question)

fit.brm.direct = brm(formula = direct ~ 1 + question + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_adult_direct") 
fit.brm.direct

```

###### Absent
```{r}

fit.brm.absent = brm(formula = absence ~ 1 + question + (1 | participant) + (1 | scenario),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/cause_adult_absent") 

fit.brm.absent

```

### CHILDREN
#### DATA
##### Read in data

```{r message=FALSE, warning=FALSE}

df.exp2_cause_children = read_csv("../../data/experiment2/cause/children/exp2_cause_children.csv")

```

##### Wrangle
```{r message=FALSE, warning=FALSE}

# clean responses
df.exp2_cause_children = df.exp2_cause_children %>% 
  rename(response = full_response,
         question = question_type) %>% 
  mutate(response = str_remove_all(string = response,
                                   pattern = "\""),
         response = str_remove_all(string = response,
                                   pattern = ":"),
         response = str_remove_all(string = response,
                                   pattern = "\\}"),
         response = str_remove_all(string = response,
                                   pattern = "\\."),
         response = str_remove_all(string = response,
                                   pattern = "\\,"),
         response = str_remove_all(string = response,
                                   pattern = "\\\\n"),
         response = str_to_lower(response))


# code responses
df.exp2_cause_children = df.exp2_cause_children %>%
  mutate(direct = ifelse(str_detect(response,
                                    "^sun$|sun | sun$"), 1, 0),
         direct = ifelse(str_detect(response,
                                    "^water$|water | water$"), 1, direct),
         direct = ifelse(str_detect(response,
                                    "^rain$|rain | rain$"), 1, direct),
         absence = ifelse(str_detect(response,
                                     "^sunscreen$|sunscreen | sunscreen$"), 1, 0),
         absence = ifelse(str_detect(response,
                                     "^window$|window | window$"), 1, absence),
         absence = ifelse(str_detect(response,
                                     "^latch$|latch | latch$"), 1, absence)) 


# compute age and replace simple with lexical
df.exp2_cause_children = df.exp2_cause_children %>%
  mutate(age = round(rounded_age / 365, digits = 2),
         age_whole =as.integer(age),
         question = str_replace_all(question, "simple", "lexical"),
         question = str_replace_all(question, "cause", "caused"))

```

##### Demographics

```{r message=FALSE, warning=FALSE}

 # gender
df.exp2_cause_children %>%
  group_by(gender) %>%
  summarise(n = n_distinct(participant)) %>%
  print()
  
  
  # language spoken
df.exp2_cause_children %>%
    mutate(en_occurrence = ifelse(str_detect(lan_spoken, "en"), "en", "non-en")) %>%
    group_by(en_occurrence) %>%
    summarise(n = n_distinct(participant)) %>%
    print()

```

#### STATS

##### Descriptives

```{r} 

df.exp2_cause_children %>% 
  mutate(response_pattern = case_when(
    direct == 1 & absence == 1 ~ "both",
    direct == 0 & absence == 0 ~ "neither",
    direct == 1 & absence == 0  ~ "direct only",
    direct == 0 & absence == 1  ~ "absence only",
  )) %>% 
  group_by(question, response_pattern) %>% 
  summarize(n = n()) %>% 
  ungroup() %>%
  group_by(question) %>%
  mutate(percentage = n / sum(n) * 100) %>%
  ungroup()


```

##### Bayesian Models
###### Direct
```{r message=FALSE, warning=FALSE}

df.model = df.exp2_cause_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "caused"),
         age = age - mean(age))

# Check contrast values
 contrasts(df.model$question)

fit.brm.direct = brm(formula = direct ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_children_direct") 
fit.brm.direct

```

###### Absent
```{r message=FALSE, warning=FALSE}

# removed random intercepts for scenario to avoid divergent transition errors
fit.brm.absent = brm(formula = absence ~ 1 + question*age + (1 | participant),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/cause_children_absent") 


fit.brm.absent

```

## MADE V LEXICAL (BURN & FLOOD)
### ADULTS
#### DATA
##### Read in data

```{r message=FALSE, warning=FALSE}

df.exp2_made_adults = read_csv("../../data/experiment2/made/adults/exp2_made_adults.csv")

```

##### Wrangle

```{r message=FALSE, warning=FALSE}

# clean responses
df.exp2_made_adults = df.exp2_made_adults %>% 
  mutate(condition = str_extract(string = responses,
                                 pattern = "sunburn_simple_response|sunburn_made_response|flood_simple_response|flood_made_response"),
         response = str_extract(string = responses, 
                                pattern = ":(.*)"),
         response = str_remove_all(string = response,
                                   pattern = "\""),
         response = str_remove_all(string = response,
                                   pattern = ":"),
         response = str_remove_all(string = response,
                                   pattern = "\\}"),
         response = str_remove_all(string = response,
                                   pattern = "\\."),
         response = str_remove_all(string = response,
                                   pattern = "\\,"),
         response = str_remove_all(string = response,
                                   pattern = "\\\\n"),
         response = str_to_lower(response)) %>% 
  separate(condition, c("scenario", "question", "extra"), "_") %>% 
  rename(participant = workerid) %>% 
  select(participant, scenario, question, response)

# code responses
df.exp2_made_adults = df.exp2_made_adults %>%
  mutate(direct = ifelse(str_detect(response,
                                    "^sun$|sun | sun$"), 1, 0),
         direct = ifelse(str_detect(response,
                                    "^water$|water | water$"), 1, direct),
         direct = ifelse(str_detect(response,
                                    "^rain$|rain | rain$"), 1, direct),
         absence = ifelse(str_detect(response,
                                     "^sunscreen$|sunscreen | sunscreen$"), 1, 0),
         absence = ifelse(str_detect(response,
                                     "^window$|window | window$"), 1, absence),
         absence = ifelse(str_detect(response,
                                     "^latch$|latch | latch$"), 1, absence))


## replace simple with lexical
df.exp2_made_adults = df.exp2_made_adults %>% 
  mutate(question = str_replace_all(question, "simple", "lexical"))

```

##### Demographics

```{r message=FALSE, warning=FALSE}

df.exp2_made_adults_demo = read_csv("../../data/experiment2/made/adults/exp2_made_adults_demo.csv")

df.exp2_made_adults_demo %>% 
  summarise(age_mean = mean(as.numeric(age), na.rm = TRUE))

df.exp2_made_adults_demo %>% 
  summarise(age_sd = sd(as.numeric(age), na.rm = TRUE))

df.exp2_made_adults_demo %>% 
  group_by(gender) %>% 
  count() 

df.exp2_made_adults_demo %>% 
  group_by(race) %>% 
  count() 

df.exp2_made_adults_demo %>% 
  group_by(ethnicity) %>% 
  count() 

```

#### STATS
##### Descriptives
```{r} 

df.exp2_made_adults %>% 
  mutate(response_pattern = case_when(
    direct == 1 & absence == 1 ~ "both",
    direct == 0 & absence == 0 ~ "neither",
    direct == 1 & absence == 0  ~ "direct only",
    direct == 0 & absence == 1  ~ "absence only",
  )) %>% 
  group_by(question, response_pattern) %>% 
  summarize(n = n()) %>% 
  ungroup() %>%
  group_by(question) %>%
  mutate(percentage = n / sum(n) * 100) %>%
  ungroup()


```
##### Bayesian Models
###### Direct

```{r}

df.model = df.exp2_made_adults %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "made"))

# Check contrast values
 contrasts(df.model$question)

fit.brm.direct = brm(formula = direct ~ 1 + question + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/made_adult_direct") 
fit.brm.direct

```

###### Absent

```{r}

fit.brm.absent = brm(formula = absence ~ 1 + question + (1 | participant) + (1 | scenario),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/made_adult_absent") 

fit.brm.absent

```

### CHILDREN
#### DATA
##### Read in data

```{r message=FALSE, warning=FALSE}

df.exp2_made_children = read_csv("../../data/experiment2/made/children/exp2_made_children.csv")

```

##### Wrangle
```{r message=FALSE, warning=FALSE}

# clean responses
df.exp2_made_children = df.exp2_made_children %>% 
  rename(response = full_response,
         question = question_type) %>% 
  mutate(response = str_remove_all(string = response,
                                   pattern = "\""),
         response = str_remove_all(string = response,
                                   pattern = ":"),
         response = str_remove_all(string = response,
                                   pattern = "\\}"),
         response = str_remove_all(string = response,
                                   pattern = "\\."),
         response = str_remove_all(string = response,
                                   pattern = "\\,"),
         response = str_remove_all(string = response,
                                   pattern = "\\\\n"),
         response = str_to_lower(response))

# code responses
df.exp2_made_children = df.exp2_made_children %>%
  mutate(direct = ifelse(str_detect(response,
                                    "^sun$|sun | sun$"), 1, 0),
         direct = ifelse(str_detect(response,
                                    "^water$|water | water$"), 1, direct),
         direct = ifelse(str_detect(response,
                                    "^rain$|rain | rain$"), 1, direct),
         absence = ifelse(str_detect(response,
                                     "^sunscreen$|sunscreen | sunscreen$"), 1, 0),
         # note the first response in the data is 'windows' but this doesn't capture that
         absence = ifelse(str_detect(response,
                                     "^window$|window | window$"), 1, absence),
         absence = ifelse(str_detect(response,
                                     "^latch$|latch | latch$"), 1, absence)) 


# compute age and replace simple with lexical
df.exp2_made_children = df.exp2_made_children %>%
  mutate(age = round(rounded_age / 365, digits = 2),
         age_whole = as.integer(age),
         question = str_replace_all(question, "simple", "lexical")) %>% 
  rename(participant = `participant _number`)


```

##### Demographics

```{r message=FALSE, warning=FALSE}

 # gender
df.exp2_made_children %>%
  group_by(gender) %>%
  summarise(n = n_distinct(participant)) %>%
  print()
  
  
  # language spoken
df.exp2_made_children %>%
    mutate(en_occurrence = ifelse(str_detect(lan_spoken, "en"), "en", "non-en")) %>%
    group_by(en_occurrence) %>%
    summarise(n = n_distinct(participant)) %>%
    print()

```

#### STATS
##### Descriptives
```{r} 

df.exp2_made_children %>% 
  mutate(response_pattern = case_when(
    direct == 1 & absence == 1 ~ "both",
    direct == 0 & absence == 0 ~ "neither",
    direct == 1 & absence == 0  ~ "direct only",
    direct == 0 & absence == 1  ~ "absence only",
  )) %>% 
  group_by(question, response_pattern) %>% 
  summarize(n = n()) %>% 
  ungroup() %>%
  group_by(question) %>%
  mutate(percentage = n / sum(n) * 100) %>%
  ungroup()


```
##### Bayesian Models
###### Direct

```{r message=FALSE, warning=FALSE}

df.model = df.exp2_made_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "made"),
         age = age - mean(age)) 

# Check contrast values
 contrasts(df.model$question)

fit.brm.direct = brm(formula = direct ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/made_children_direct") 
fit.brm.direct

```

###### Absent
```{r message=FALSE, warning=FALSE}

# removed random intercepts for scenario to avoid divergent transition errors
fit.brm.absent = brm(formula = absence ~ 1 + question*age + (1 | participant),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/made_children_absent") 


fit.brm.absent

```

## CAUSE v MADE
### ADULTS
#### DATA
##### Wrangle

```{r message=FALSE, warning=FALSE}

df.exp2_cause_made_adults = df.exp2_cause_adults %>% 
  filter(question == "cause") %>% 
  select(-participant) %>% 
  bind_rows(df.exp2_made_adults %>% 
  filter(question == "made") %>% 
  select(-participant)) %>% 
  mutate(participant = rep(1:(n()/2), each = 2))


```

#### STATS

##### Bayesian Models
###### Direct

```{r message=FALSE, warning=FALSE}

df.model = df.exp2_cause_made_adults %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "made"))

# Check contrast values
 contrasts(df.model$question)


fit.brm.cause.made.adult.direct = brm(formula = direct ~ 1 + question + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_made_adult_direct") 

fit.brm.cause.made.adult.direct



```

###### Absent

```{r message=FALSE, warning=FALSE}

fit.brm.cause.made.adult.absent = brm(formula = absence ~ 1 + question + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_made_adult_absence") 

fit.brm.cause.made.adult.absent

```

### CHILDREN
#### DATA
##### Wrangle

```{r message=FALSE, warning=FALSE}

df.exp2_cause_made_children = df.exp2_cause_children %>% 
  filter(question == "caused") %>% 
  select(-cause_question_order, participant) %>% 
  bind_rows(df.exp2_made_children %>% 
  filter(question == "made") %>% 
  select(-made_question_order, participant)) %>% 
  mutate(participant = rep(1:(n()/2), each = 2))


```

#### STATS

##### Bayesian Models
###### Direct

```{r message=FALSE, warning=FALSE}

df.model = df.exp2_cause_made_children %>% 
  mutate(question = fct_relevel(question, "made"),
         age = age - mean(age))

# Check contrast values
 contrasts(df.model$question)



fit.brm.cause.made.children.direct = brm(formula = direct ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_made_children_direct.rds") 

fit.brm.cause.made.children.direct


```

###### Absent

```{r message=FALSE, warning=FALSE}


fit.brm.cause.made.children.absent = brm(formula = absence ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_made_children_absence.rds") 

fit.brm.cause.made.children.absent


```
## ORDER EFFECTS
## FIRST SCENARIO
### ADULTS
#### DATA
##### Wrangle

```{r}

# code order
df.tmp = df.exp2_cause_adults %>% 
  group_by(participant) %>% 
  filter(row_number() == 1) %>% 
  mutate(scenario_order = str_c(scenario, "_first"),
         question_order = str_c(question, "_first")) %>% 
  select(participant,
         contains("order"))

df.exp2_cause_adults_order = df.exp2_cause_adults %>% 
  left_join(df.tmp,
            by = "participant") %>% 
  relocate(contains("order"), .after = question) %>% 
  mutate(caused_question_order = case_when(question_order == "lexical_first" ~ "second",
                                          question_order == "cause_first" ~ "first"),
         question = as_factor(question),
         question = fct_relevel(question, "lexical"),
         caused_question_order = as_factor(caused_question_order),
         caused_question_order = fct_relevel(caused_question_order, "first")) %>% 
   group_by(participant) %>%
   filter(row_number() <= 2) %>%
  ungroup()


# code order
df.tmp = df.exp2_made_adults %>% 
  group_by(participant) %>% 
  filter(row_number() == 1) %>% 
  mutate(scenario_order = str_c(scenario, "_first"),
         question_order = str_c(question, "_first")) %>% 
  select(participant,
         contains("order"))

df.exp2_made_adults_order = df.exp2_made_adults %>% 
  left_join(df.tmp,
            by = "participant") %>% 
  relocate(contains("order"), .after = question) %>% 
  mutate(made_question_order = case_when(question_order == "lexical_first" ~ "second",
                                          question_order == "made_first" ~ "first"),
         question = as_factor(question),
         question = fct_relevel(question, "lexical"),
         made_question_order = as_factor(made_question_order),
         made_question_order = fct_relevel(made_question_order, "first")) %>% 
   group_by(participant) %>%
   filter(row_number() <= 2) %>%
  ungroup()

df.exp2_lexical_adults_order = df.exp2_cause_adults_order %>% 
  filter(question == "lexical") %>% 
  rename(periphrastic_question_order = caused_question_order) %>% 
  select(-participant) %>% 
  bind_rows(df.exp2_made_adults_order %>% 
             filter(question == "lexical") %>% 
  rename(periphrastic_question_order = made_question_order) %>% 
  select(-participant)) %>% 
  mutate(participant = rep(1:n()),
         periphrastic_question_order = as_factor(periphrastic_question_order),
         periphrastic_question_order = fct_relevel(periphrastic_question_order, "first"))

```

#### STATS

##### Bayesian Models
###### Direct

```{r message=FALSE, warning=FALSE}

df.model = df.exp2_cause_adults_order %>% 
  filter(question == "cause")

# Check contrast values
 contrasts(df.model$caused_question_order)


cause_adults_direct_order = brm(formula = direct ~ 1 + caused_question_order + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_adults_direct_order") 

cause_adults_direct_order


df.model = df.exp2_made_adults_order %>% 
  filter(question == "made")

# Check contrast values
 contrasts(df.model$made_question_order)


made_adults_direct_order = brm(formula = direct ~ 1 + made_question_order + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/made_adults_direct_order") 

made_adults_direct_order


df.model = df.exp2_lexical_adults_order

# Check contrast values
 contrasts(df.model$periphrastic_question_order)
 
lexical_adults_direct_order = brm(formula = direct ~ 1 + periphrastic_question_order + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/lexical_adults_direct_order") 

lexical_adults_direct_order



```

###### Absent

```{r message=FALSE, warning=FALSE}

df.model = df.exp2_cause_adults_order %>% 
  filter(question == "cause")

# Check contrast values
 contrasts(df.model$caused_question_order)
 
cause_adults_absent_order = brm(formula = absence ~ 1 + caused_question_order + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_adults_absence_order") 

cause_adults_absent_order




df.model = df.exp2_made_adults_order %>% 
  filter(question == "made")

# Check contrast values
 contrasts(df.model$made_question_order)
 
made_adults_absent_order = brm(formula = absence ~ 1 + made_question_order + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/made_adults_absence_order") 

made_adults_absent_order



df.model = df.exp2_lexical_adults_order

# Check contrast values
 contrasts(df.model$periphrastic_question_order)
 
lexical_adults_absent_order = brm(formula = absence ~ 1 + periphrastic_question_order + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/lexical_adults_absence_order") 

lexical_adults_absent_order



```

### CHILDREN
#### DATA
##### Wrangle

```{r}

df.exp2_cause_children_order = df.exp2_cause_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "lexical"),
         caused_question_order = as_factor(cause_question_order),
         caused_question_order = fct_relevel(caused_question_order, "first")) %>% 
   group_by(participant) %>%
   filter(row_number() <= 2) %>%
  ungroup()



df.exp2_made_children_order = df.exp2_made_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "lexical"),
         made_question_order = str_replace_all(made_question_order, "frst", "first"),
         made_question_order = str_replace_all(made_question_order, "scond", "second"),
         made_question_order = as_factor(made_question_order),
         made_question_order = fct_relevel(made_question_order, "first")) %>% 
   group_by(participant) %>%
   filter(row_number() <= 2) %>%
  ungroup()

df.exp2_lexical_children_order = df.exp2_cause_children_order %>% 
  filter(question == "lexical") %>% 
  rename(periphrastic_question_order = caused_question_order) %>% 
  select(-participant) %>% 
  bind_rows(df.exp2_made_children_order %>% 
             filter(question == "lexical") %>% 
  rename(periphrastic_question_order = made_question_order) %>% 
  select(-participant)) %>% 
  mutate(participant = rep(1:n()),
         periphrastic_question_order = as_factor(periphrastic_question_order),
         periphrastic_question_order = fct_relevel(periphrastic_question_order, "first"))


```

#### STATS

##### Bayesian Models
###### Direct

```{r message=FALSE, warning=FALSE}

df.model = df.exp2_cause_children_order %>% 
  filter(question == "caused")

# Check contrast values
 contrasts(df.model$caused_question_order)


cause_children_direct_order = brm(formula = direct ~ 1 + caused_question_order + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_children_direct_order") 

cause_children_direct_order


df.model = df.exp2_made_children_order %>% 
  filter(question == "made")

# Check contrast values
 contrasts(df.model$made_question_order)


made_children_direct_order = brm(formula = direct ~ 1 + made_question_order + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/made_children_direct_order") 

made_children_direct_order


df.model = df.exp2_lexical_children_order

# Check contrast values
 contrasts(df.model$periphrastic_question_order)
 
lexical_children_direct_order = brm(formula = direct ~ 1 + periphrastic_question_order + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/lexical_children_direct_order") 

lexical_children_direct_order



```
###### Absent

```{r message=FALSE, warning=FALSE}

df.model = df.exp2_cause_children_order %>% 
  filter(question == "caused")

# Check contrast values
 contrasts(df.model$caused_question_order)


cause_children_absent_order = brm(formula = absence ~ 1 + caused_question_order + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_children_absent_order") 

cause_children_absent_order


df.model = df.exp2_made_children_order %>% 
  filter(question == "made")

# Check contrast values
 contrasts(df.model$made_question_order)


made_children_absent_order = brm(formula = absence ~ 1 + made_question_order + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/made_children_absent_order") 

made_children_absent_order


df.model = df.exp2_lexical_children_order

# Check contrast values
 contrasts(df.model$periphrastic_question_order)
 
lexical_children_absent_order = brm(formula = absence ~ 1 + periphrastic_question_order + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/lexical_children_absent_order") 

lexical_children_absent_order



```

## PLOTS
### Data
#### Different Responses

```{r message=FALSE, warning=FALSE}

df.exp2_cause_adults_differnece = df.exp2_cause_adults %>%
  select(question, direct, absence) %>%
  mutate(age = rep("adults"))

df.exp2_made_adults_difference = df.exp2_made_adults %>%
  select(question, direct, absence) %>%
  mutate(age = rep("adults"))

df.exp2_cause_children_difference = df.exp2_cause_children %>%
  select(question, direct, absence) %>%
  mutate(question = str_replace_all(question, "caused", "cause")) %>%
  mutate(age = rep("children"))

df.exp2_made_children_difference = df.exp2_made_children %>%
  select(question, direct, absence) %>%
  mutate(age = rep("children"))

df.difference_combined = df.exp2_cause_adults_differnece %>%
  bind_rows(df.exp2_made_adults_difference,
            df.exp2_cause_children_difference,
            df.exp2_made_children_difference) %>%
   mutate(response_pattern = case_when(
    direct == 1 & absence == 1 ~ "both",
    direct == 0 & absence == 0 ~ "neither",
    TRUE ~ "different"
  ))

df.difference_combined %>%
  group_by(age, question, response_pattern) %>%
  summarize(n = n()) %>%
  ungroup() %>%
  group_by(age, question) %>%
  mutate(percentage = n / sum(n) * 100)

```

### Different Responses Plots
#### Cause

```{r message=FALSE, warning=FALSE}

df.cause_children_differnet = df.exp2_cause_children %>%
  mutate(response_pattern = case_when(
    direct == 1 & absence == 1 ~ "both",
    direct == 0 & absence == 0 ~ "neither",
    TRUE ~ "different"
  )) %>%
  filter(response_pattern == "different")



df.model = df.cause_children_differnet %>%
  mutate(difference = absence - direct,
        difference = recode(difference, `-1` = 0),
        question = str_replace_all(question, "caused", "cause"))


fit.brm.absence_cause.difference = brm(formula = difference ~ 1 + question*age + (1 | participant) + (1 | scenario),
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .9999),
                     file = "cache/absence_cause_difference")


df.data = expand_grid(age = seq(4, 9, 0.1),
                      question = c("cause", "lexical"))

df.prediction = fit.brm.absence_cause.difference %>%
  fitted(newdata = df.data,
         re_formula = NA,
          probs = c(0.1, 0.9)) %>%
  as_tibble() %>%
  bind_cols(df.data) %>%
  clean_names()


df.adults = df.exp2_cause_adults %>%
   mutate(response_pattern = case_when(
    direct == 1 & absence == 1 ~ "both",
    direct == 0 & absence == 0 ~ "neither",
    TRUE ~ "different"
  )) %>%
  filter(response_pattern == "different") %>%
  select(-response) %>%
  mutate(age_whole = rep(10)) %>%
  mutate(difference = absence - direct,
        difference = recode(difference, `-1` = 0))



df.means = df.model %>%
  bind_rows(df.adults) %>%
  mutate(age_whole = factor(age_whole,
                            levels = c(4, 5, 6, 7, 8, 9, 10),
                            labels = c("4", "5", "6", "7", "8", "9", "adults"))) %>%
  group_by(age_whole, question) %>%
  summarize(
    response = Hmisc::smean.cl.boot(difference)) %>%
    mutate(index = c("response", "low", "high")) %>%
    ungroup() %>%
    pivot_wider(names_from = index,
                values_from = response) %>%
  mutate(age_whole = fct_recode(age_whole, "10" = "adults"),
         age_whole = as.numeric(as.character(age_whole)))



p5 = ggplot(mapping = aes(x = age,
                     y = difference,
                     color = question)) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  geom_smooth(data = df.prediction,
              mapping = aes(y = estimate,
                            ymin = q10,
                            ymax = q90,
                            color = question,
                            fill = question),
              stat = "identity",
              alpha = 0.2) +
  geom_pointrange(data = df.means,
                  mapping = aes(x = age_whole,
                                y = response,
                                ymin = low,
                                ymax = high,
                                fill = question,
                                shape = question),
                  color = "black",
                  size = 0.5,
                  show.legend = TRUE,
                  alpha = 0.8,
                  position = position_dodge(width = 0.3)) +
  ylab("Probability of selecting \n direct or absent cause") +
  scale_fill_manual(values = c("cause" = "#E41A1C",
                               "lexical" = "#377EB8")) +
  scale_color_manual(values = c("cause" = "#E41A1C",
                                "lexical" = "#377EB8")) +
  scale_shape_manual(values = c("cause" = 21,
                                "lexical" = 23)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = c("100% \n proximal", "75%", "50%", "75%", "100% \n distal"),
                     limits = c(0, 1)) +
  scale_x_continuous(breaks = 4:10,
                     labels = c("4", "5", "6", "7", "8", "9", "Adults")) +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        text = element_text(size = 18)) +
  guides(fill = "none",
         color = "none",
         shape = guide_legend(override.aes = list(fill = c("#377EB8", "#E41A1C")),
                              reverse = T))



```

#### Made

```{r message=FALSE, warning=FALSE}

df.made_children_differnet = df.exp2_made_children %>%
  mutate(response_pattern = case_when(
    direct == 1 & absence == 1 ~ "both",
    direct == 0 & absence == 0 ~ "neither",
    TRUE ~ "different"
  )) %>%
  filter(response_pattern == "different")

df.model = df.made_children_differnet %>%
  mutate(difference = absence - direct,
        difference = recode(difference, `-1` = 0),
         age_whole = as.integer(age))


fit.brm.absence_made.difference = brm(formula = difference ~ 1 + question*age + (1 | participant) + (1 | scenario),
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .9999),
                     file = "cache/absence_made_difference")


df.data = expand_grid(age = seq(4, 9, 0.1),
                      question = c("made", "lexical"))

df.prediction = fit.brm.absence_made.difference %>%
  fitted(newdata = df.data,
         re_formula = NA,
          probs = c(0.1, 0.9)) %>%
  as_tibble() %>%
  bind_cols(df.data) %>%
  clean_names()



df.adults = df.exp2_made_adults %>%
   mutate(response_pattern = case_when(
    direct == 1 & absence == 1 ~ "both",
    direct == 0 & absence == 0 ~ "neither",
    TRUE ~ "different"
  )) %>%
  filter(response_pattern == "different") %>%
  select(-response) %>%
  mutate(age_whole = rep(10)) %>%
  mutate(difference = absence - direct,
        difference = recode(difference, `-1` = 0))



df.means = df.model %>%
  bind_rows(df.adults) %>%
  mutate(age_whole = factor(age_whole,
                            levels = c(4, 5, 6, 7, 8, 9, 10),
                            labels = c("4", "5", "6", "7", "8", "9", "adults"))) %>%
  group_by(age_whole, question) %>%
  summarize(
    response = Hmisc::smean.cl.boot(difference)) %>%
    mutate(index = c("response", "low", "high")) %>%
    ungroup() %>%
    pivot_wider(names_from = index,
                values_from = response) %>%
  mutate(age_whole = fct_recode(age_whole, "10" = "adults"),
         age_whole = as.numeric(as.character(age_whole)))




p6 = ggplot(mapping = aes(x = age,
                     y = difference,
                     color = question)) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  geom_smooth(data = df.prediction,
              mapping = aes(y = estimate,
                            ymin = q10,
                            ymax = q90,
                            color = question,
                            fill = question),
              stat = "identity",
              alpha = 0.2) +
  geom_pointrange(data = df.means,
                  mapping = aes(x = age_whole,
                                y = response,
                                ymin = low,
                                ymax = high,
                                fill = question,
                                shape = question),
                  color = "black",
                  size = 0.5,
                  show.legend = TRUE,
                  alpha = 0.8,
                  position = position_dodge(width = 0.3)) +
  scale_fill_manual(values = c("made" = "#4DAF4A",
                               "lexical" = "#377EB8"),
                    breaks = c("made",
                               "lexical")) +
  scale_color_manual(values = c("made" = "#4DAF4A",
                                "lexical" = "#377EB8"),
                     breaks= c("made", "lexical")) +
  scale_shape_manual(values = c("made" = 21,
                                "lexical" = 23)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = c("100% \n proximal", "75%", "50%", "75%", "100% \n distal"),
                     limits = c(0, 1)) +
  scale_x_continuous(breaks = 4:10,
                     labels = c("4", "5", "6", "7", "8", "9", "Adults")) +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        axis.title.y = element_blank(),
        text = element_text(size = 18)) +
  guides(fill = "none",
         color = "none",
         shape = guide_legend(override.aes = list(fill = c("#377EB8", "#4DAF4A"))))


```

#### Combine Cause and Made Plots
```{r fig.height=4, fig.width=12, message=FALSE, warning=FALSE}

plot = p5 + p6 +
plot_layout(nrow = 1) &
plot_annotation(tag_levels = "A") &
theme(plot.tag = element_text(face = "bold"))

ggsave(plot, filename = "../../figures/experiment2/absence_different.pdf", height = 5, width = 12)

plot


```

### Response Plots
#### Cause
```{r message=FALSE, warning=FALSE}

df.model = df.exp2_cause_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "caused"))

# removed random intercepts for scenario to avoid divergent transition errors
fit.brm.present.cause.age2 = brm(formula = direct ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 6000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999,
                                    max_treedepth = 15),
                     file = "cache/fit.brm.present.cause.age2") 



fit.brm.absence.cause.age2 = brm(formula = absence ~ 1 + question*age + (1 | participant) + (1 | scenario),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 6000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999,
                                     max_treedepth = 15),
                      file = "cache/fit.brm.absence.cause.age2") 



df.data = expand_grid(age = seq(4, 9, 0.1),
                      question = c("caused", "lexical"))

df.prediction = fit.brm.present.cause.age2 %>% 
  fitted(newdata = df.data,
         re_formula = NA,
          probs = c(0.1, 0.9)) %>% 
  as_tibble() %>% 
  bind_cols(df.data) %>% 
  mutate(type = "presence") %>% 
  bind_rows(fit.brm.absence.cause.age2 %>% 
              fitted(newdata = df.data,
                     re_formula = NA,
                     probs = c(0.1, 0.9)) %>% 
              as_tibble() %>% 
              bind_cols(df.data) %>% 
              mutate(type = "absence")) %>% 
  clean_names()

df.adults = df.exp2_cause_adults %>% 
  select(-response) %>% 
  mutate(age_whole = rep(10)) %>% 
  pivot_longer(cols = (direct:absence),
    names_to = "type",
    values_to = "response")



df.children = df.exp2_cause_children%>%
  select(-response) %>% 
 pivot_longer(cols = (direct:absence),
               names_to = "type",
               values_to = "response")

df.means = df.children %>% 
  bind_rows(df.adults) %>% 
  mutate(age_whole = factor(age_whole, 
                            levels = c(4, 5, 6, 7, 8, 9, 10), 
                            labels = c("4", "5", "6", "7", "8", "9", "adults")),
         question = recode(question, "cause" = "caused"),
         type = recode(type, "direct" = "presence")) %>% 
  group_by(age_whole, question, type) %>% 
  summarize(
    response = Hmisc::smean.cl.boot(response)) %>%
    mutate(index = c("response", "low", "high")) %>%
    ungroup() %>% 
    pivot_wider(names_from = index,
                values_from = response) %>% 
  mutate(age_whole = fct_recode(age_whole, "10" = "adults"),
         age_whole = as.numeric(as.character(age_whole)))



custom_labels = as_labeller(c("absence" = "Absent Cause", "presence" = "Direct Cause"))

p7 = ggplot(mapping = aes(x = age, 
                     y = response,
                     color = question)) + 
  geom_hline(yintercept=0.50, linetype="dashed", color = "black") +
  geom_smooth(data = df.prediction,
              mapping = aes(y = estimate,
                            ymin = q10,
                            ymax = q90,
                            color = question,
                            fill = question),
              stat = "identity",
              alpha = 0.2,
              show.legend = F) +
  geom_pointrange(data = df.means,
                  mapping = aes(x = age_whole,
                                y = response,
                                ymin = low,
                                ymax = high,
                                fill = question,
                                shape = question),
                  color = "black",
                  size = 0.5,
                  show.legend = TRUE,
                  alpha = 0.8,
                  position = position_dodge(width = 0.5)) +
    facet_wrap(~type,
             labeller = custom_labels) + 
  scale_fill_brewer(palette = "Set1") + 
  scale_color_brewer(palette = "Set1") +
  scale_shape_manual(values = c(21, 23)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                      labels = str_c(seq(0, 1, 0.25) * 100, "%")) +
  scale_x_continuous(breaks = 4:10,
                     labels = c("4", "5", "6", "7", "8", "9", "Adults")) +
  labs(y = "Probability of selecting \n causal candidate") +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        text = element_text(size = 18)) +
  guides(color = guide_legend(reverse = TRUE),
         fill = guide_legend(reverse = TRUE),
         shape = guide_legend(reverse = TRUE))

  
```

#### Made

```{r message=FALSE, warning=FALSE}

df.model = df.exp2_made_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "made"))


fit.brm.present.made.age2 = brm(formula = direct ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 8000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999,
                                    max_treedepth = 15),
                     file = "cache/fit.brm.present.made.age2") 



fit.brm.absence.made.age2 = brm(formula = absence ~ 1 + question*age + (1 | participant) + (1 | scenario),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 6000,
                      control = list(adapt_delta = .999999,
                                     max_treedepth = 15),
                      file = "cache/fit.brm.absence.made.age2") 



df.data = expand_grid(age = seq(4, 9, 0.1),
                      question = c("made", "lexical"))

df.prediction = fit.brm.present.made.age2 %>% 
  fitted(newdata = df.data,
         re_formula = NA,
          probs = c(0.1, 0.9)) %>% 
  as_tibble() %>% 
  bind_cols(df.data) %>% 
  mutate(type = "presence") %>% 
  bind_rows(fit.brm.absence.made.age2 %>% 
              fitted(newdata = df.data,
                     re_formula = NA,
                     probs = c(0.1, 0.9)) %>% 
              as_tibble() %>% 
              bind_cols(df.data) %>% 
              mutate(type = "absence")) %>% 
  clean_names()

df.adults = df.exp2_made_adults %>% 
  select(-response) %>% 
  mutate(age_whole = rep(10)) %>% 
  pivot_longer(cols = (direct:absence),
    names_to = "type",
    values_to = "response")


df.children = df.exp2_made_children %>%
  select(-response) %>% 
  pivot_longer(cols = (direct:absence),
               names_to = "type",
               values_to = "response")

df.means = df.children %>% 
  mutate(age_whole = as.integer(age)) %>%
  bind_rows(df.adults) %>% 
  mutate(age_whole = factor(age_whole, 
                            levels = c(4, 5, 6, 7, 8, 9, 10), 
                            labels = c("4", "5", "6", "7", "8", "9", "adults")),
         type = recode(type, "direct" = "presence")) %>% 
  group_by(age_whole, question, type) %>% 
  summarize(
    response = Hmisc::smean.cl.boot(response)) %>%
    mutate(index = c("response", "low", "high")) %>%
    ungroup() %>% 
    pivot_wider(names_from = index,
                values_from = response) %>% 
  mutate(age_whole = fct_recode(age_whole, "10" = "adults"),
         age_whole = as.numeric(as.character(age_whole)),
         question = factor(question, levels = c("made", "lexical")))


custom_labels = as_labeller(c("absence" = "Absent Cause", "presence" = "Direct Cause"))


p8 = ggplot(mapping = aes(x = age, 
                     y = response,
                     color = question)) + 
  geom_hline(yintercept=0.50, linetype="dashed", color = "black") +
  geom_smooth(data = df.prediction,
              mapping = aes(y = estimate,
                            ymin = q10,
                            ymax = q90,
                            color = question,
                            fill = question),
              stat = "identity",
              alpha = 0.2,
              show.legend = F) +
  geom_pointrange(data = df.means,
                  mapping = aes(x = age_whole,
                                y = response,
                                ymin = low,
                                ymax = high,
                                fill = question,
                                shape = question),
                  color = "black",
                  size = 0.5,
                  show.legend = TRUE,
                  alpha = 0.8,
                  position = position_dodge(width = 0.4)) +
  facet_wrap(~type,
             labeller = custom_labels) + 
  scale_fill_manual(values = c("made" = "#4DAF4A", "lexical" = "#377EB8"), breaks=c("made", "lexical")) +
  scale_color_manual(values = c("made" = "#4DAF4A", "lexical" = "#377EB8"), breaks=c("made", "lexical")) +
  scale_shape_manual(values = c(21, 23), breaks=c("made", "lexical")) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = str_c(seq(0, 1, 0.25) * 100, "%"),
                     limits = c(0, 1)) +
  scale_x_continuous(breaks = 4:10,
                     labels = c("4", "5", "6", "7", "8", "9", "Adults")) +
  labs(y = "Probability of selecting \n causal candidate") +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        text = element_text(size = 18)) 


```

#### Combine Cause and Made Plots

```{r fig.height=5, fig.width=18, message=FALSE, warning=FALSE}

plot = p7 + p8 + 
plot_layout(nrow = 1) &
plot_annotation(tag_levels = "A") &
theme(plot.tag = element_text(face = "bold"))

ggsave(plot, filename = "../../figures/experiment2/absence_all.pdf", height = 5, width = 18)

plot


```

#### Responses Patterns
```{r}

df.plot = df.exp2_cause_adults %>% 
  mutate(age = "adults") %>% 
  bind_rows(df.exp2_made_adults %>% 
              mutate(age = "adults")) %>% 
  bind_rows(df.exp2_cause_children %>% 
              mutate(age = "children")) %>% 
  bind_rows(df.exp2_made_children %>% 
              mutate(age = "children")) %>% 
   mutate(response_pattern = case_when(
    direct == 1 & absence == 1 ~ "both",
    direct == 0 & absence == 0 ~ "neither",
    direct == 1 & absence == 0  ~ "direct only",
    direct == 0 & absence == 1  ~ "absence only",
  ),
  question = recode(question, "cause" = "caused")) %>% 
  group_by(age, question, response_pattern) %>% 
  summarize(n = n()) %>% 
  ungroup() %>%
  group_by(age, question) %>%
  mutate(percentage = n / sum(n) * 100) %>%
  ungroup() %>% 
  mutate(question = factor(question, levels = c("caused", "made", "lexical")),
         response_pattern = factor(response_pattern, levels = c("absence only", "direct only", "both", "neither")))


ggplot(data = df.plot,
       mapping = aes(x = age,
                     y = percentage,
                     group = response_pattern,
                     color = response_pattern,
                     fill = response_pattern)) +
  geom_col(color = "black") +
  scale_fill_brewer(palette = "Set1") + 
  scale_color_brewer(palette = "Set1") +
  scale_shape_manual(values = c(21, 23)) +
  scale_y_continuous(breaks = seq(0, 100, 25),
                     labels = str_c(seq(0, 100, 25), "%")) +
  labs(y = "Response pattern \n\ probability") +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        text = element_text(size = 18),
        axis.title.x = element_blank()) +
  facet_wrap(~question)

ggsave("../../figures/experiment2/absence_response_patterns.pdf", height = 4, width = 8)

```

#### Responses Patterns by Age
##### Cause v Lexical
```{r}

df.plot = df.exp2_cause_adults %>% 
  mutate(age_whole = 10) %>% 
  bind_rows(df.exp2_cause_children) %>% 
  mutate(response_pattern = case_when(
    direct == 1 & absence == 1 ~ "both",
    direct == 0 & absence == 0 ~ "neither",
    direct == 1 & absence == 0  ~ "direct only",
    direct == 0 & absence == 1  ~ "absence only",
  ),
  question = recode(question, "cause" = "caused"),
  age_whole = as.factor(age_whole)) %>% 
  group_by(age_whole, question, response_pattern) %>% 
  summarize(n = n()) %>% 
  ungroup() %>%
  group_by(age_whole, question) %>%
  mutate(percentage = n / sum(n) * 100) %>%
  ungroup() %>% 
  mutate(question = factor(question, levels = c("caused", "lexical")),
          response_pattern = factor(response_pattern, levels = c("absence only", "direct only", "both", "neither")))


p1 = ggplot(data = df.plot,
       mapping = aes(x = age_whole,
                     y = percentage,
                     group = response_pattern,
                     color = response_pattern,
                     fill = response_pattern)) +
  geom_col(color = "black") +
  scale_fill_brewer(palette = "Set1") + 
  scale_color_brewer(palette = "Set1") +
  scale_shape_manual(values = c(21, 23)) +
  scale_y_continuous(breaks = seq(0, 100, 25),
                     labels = str_c(seq(0, 100, 25), "%")) +
  scale_x_discrete(breaks = 4:10,
                     labels = c("4", "5", "6", "7", "8", "9", "Adults")) +
  labs(y = "Response pattern \n\ probability") +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        text = element_text(size = 18),
        axis.title.x = element_blank()) +
  facet_wrap(~question)



```

##### Made v Lexical
```{r}

df.plot = df.exp2_made_adults %>% 
  mutate(age_whole = 10) %>% 
  bind_rows(df.exp2_made_children) %>% 
  mutate(response_pattern = case_when(
    direct == 1 & absence == 1 ~ "both",
    direct == 0 & absence == 0 ~ "neither",
    direct == 1 & absence == 0  ~ "direct only",
    direct == 0 & absence == 1  ~ "absence only",
  ),
  age_whole = as.factor(age_whole)) %>% 
  group_by(age_whole, question, response_pattern) %>% 
  summarize(n = n()) %>% 
  ungroup() %>%
  group_by(age_whole, question) %>%
  mutate(percentage = n / sum(n) * 100) %>%
  ungroup() %>% 
  mutate(question = factor(question, levels = c("made", "lexical")),
         response_pattern = factor(response_pattern, levels = c("absence only", "direct only", "both", "neither")))


p2 = ggplot(data = df.plot,
       mapping = aes(x = age_whole,
                     y = percentage,
                     group = response_pattern,
                     color = response_pattern,
                     fill = response_pattern)) +
  geom_col(color = "black") +
  scale_fill_brewer(palette = "Set1") + 
  scale_color_brewer(palette = "Set1") +
  scale_shape_manual(values = c(21, 23)) +
  scale_y_continuous(breaks = seq(0, 100, 25),
                     labels = str_c(seq(0, 100, 25), "%")) +
  scale_x_discrete(breaks = 4:10,
                     labels = c("4", "5", "6", "7", "8", "9", "Adults")) +
  labs(y = "Response pattern \n\ probability") +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        text = element_text(size = 18),
        axis.title.x = element_blank()) +
  facet_wrap(~question)



```
##### Combine Cause and Made Plots
```{r fig.height=5, fig.width=18, message=FALSE, warning=FALSE}

plot = p1 + p2 + 
plot_layout(nrow = 1) &
plot_annotation(tag_levels = "A") &
theme(plot.tag = element_text(face = "bold"))

ggsave(plot, filename = "../../figures/experiment2/absence_response_patterns_age.pdf", height = 5, width = 18)

plot


```


### Order Effects
#### First Scenario

```{r fig.height=4, fig.width=9.5, message=FALSE, warning=FALSE}

df.plot = df.exp2_cause_children_order %>% 
  rename(periphrastic_question_order = caused_question_order) %>% 
  select(question, direct, absence, periphrastic_question_order) %>% 
  mutate(age = rep("children")) %>% 
  bind_rows(df.exp2_made_children_order %>% 
              rename(periphrastic_question_order = made_question_order) %>% 
              select(question, direct, absence, periphrastic_question_order) %>% 
  mutate(age = rep("children")),
            df.exp2_cause_adults_order %>% 
              rename(periphrastic_question_order = caused_question_order) %>% 
              select(question, direct, absence, periphrastic_question_order) %>% 
  mutate(age = rep("adults")),
            df.exp2_made_adults_order %>% 
              rename(periphrastic_question_order = made_question_order) %>% 
    select(question, direct, absence, periphrastic_question_order) %>% 
  mutate(age = rep("adults"))) %>% 
  pivot_longer(cols = direct:absence,
               names_to = "type",
               values_to = "response") %>% 
  mutate(question = str_replace_all(question, "\\bcause\\b", "caused"),
          age = factor(age, levels = c("children", "adults")))

custom_labels = as_labeller(c("direct" = "Direct Cause", "absence" = "Absent Cause"))

ggplot(data = df.plot,
       mapping = aes(x = factor(question, levels = c("caused", "made", "lexical")),
                     y = response,
                     group = interaction(periphrastic_question_order, age),
                     color = periphrastic_question_order,
                     fill = periphrastic_question_order,
                     shape = age)) + 
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  stat_summary(fun.data = "mean_cl_boot",
               position = position_dodge(width = 0.8),
               size = .9,
               color = "black") +  
  scale_fill_brewer(palette = "Set3") +
  scale_color_brewer(palette = "Set3") +
 scale_y_continuous(breaks = seq(0, 1, 0.25),
                      labels = str_c(seq(0, 1, 0.25) * 100, "%"),
                      limits = c(0, 1)) +
  ylab("Probability of selecting \n causal candidate") + 
 scale_shape_manual(values = c(21, 23)) +
  guides(fill = guide_legend(order = 1, override.aes = list(shape = 22, color = NA)),
         color = guide_legend(order = 1, override.aes = list(shape = 22, color = NA)),
         shape = guide_legend(order = 2, override.aes = list(color = "black"))) +
  ylab("Probability of selecting \n causal candidate") +
  theme(legend.position = "bottom",
        legend.box = "vertical",
        axis.title.x = element_blank(),
        text = element_text(size = 18)) +  
  labs(color = "  periphrastic \n\ question order", 
       fill = "   periphrastic \n\ question order",
       shape = "age") +
   facet_wrap(~type,
             labeller = custom_labels) 

ggsave("../../figures/experiment2/absent_order_effect_first_scenario.pdf", height = 4, width = 9.5)


```

#### Second Scenario

```{r fig.height=4, fig.width=9.5, message=FALSE, warning=FALSE}

df.exp2_cause_children_order_second = df.exp2_cause_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "lexical"),
         caused_question_order = as_factor(cause_question_order),
         caused_question_order = fct_relevel(caused_question_order, "first")) %>% 
   group_by(participant) %>%
   filter(row_number() %in% 3:4) %>%
  ungroup()



df.exp2_made_children_order_second = df.exp2_made_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "lexical"),
         made_question_order = str_replace_all(made_question_order, "frst", "first"),
         made_question_order = str_replace_all(made_question_order, "scond", "second"),
         made_question_order = as_factor(made_question_order),
         made_question_order = fct_relevel(made_question_order, "first")) %>% 
   group_by(participant) %>%
   filter(row_number() %in% 3:4) %>%
  ungroup()

# code order
df.tmp = df.exp2_cause_adults %>% 
  group_by(participant) %>% 
  filter(row_number() == 1) %>% 
  mutate(scenario_order = str_c(scenario, "_first"),
         question_order = str_c(question, "_first")) %>% 
  select(participant,
         contains("order"))

df.exp2_cause_adults_order_second = df.exp2_cause_adults %>% 
  left_join(df.tmp,
            by = "participant") %>% 
  relocate(contains("order"), .after = question) %>% 
  mutate(caused_question_order = case_when(question_order == "lexical_first" ~ "second",
                                          question_order == "cause_first" ~ "first"),
         question = as_factor(question),
         question = fct_relevel(question, "lexical"),
         caused_question_order = as_factor(caused_question_order),
         caused_question_order = fct_relevel(caused_question_order, "first")) %>% 
   group_by(participant) %>%
   filter(row_number() %in% 3:4) %>%
  ungroup()


# code order
df.tmp = df.exp2_made_adults %>% 
  group_by(participant) %>% 
  filter(row_number() == 1) %>% 
  mutate(scenario_order = str_c(scenario, "_first"),
         question_order = str_c(question, "_first")) %>% 
  select(participant,
         contains("order"))

df.exp2_made_adults_order_second = df.exp2_made_adults %>% 
  left_join(df.tmp,
            by = "participant") %>% 
  relocate(contains("order"), .after = question) %>% 
  mutate(made_question_order = case_when(question_order == "lexical_first" ~ "second",
                                          question_order == "made_first" ~ "first"),
         question = as_factor(question),
         question = fct_relevel(question, "lexical"),
         made_question_order = as_factor(made_question_order),
         made_question_order = fct_relevel(made_question_order, "first")) %>% 
   group_by(participant) %>%
   filter(row_number() %in% 3:4) %>%
  ungroup()



df.plot = df.exp2_cause_children_order_second %>% 
  rename(periphrastic_question_order = caused_question_order) %>% 
  select(question, direct, absence, periphrastic_question_order) %>% 
  mutate(age = rep("children")) %>% 
  bind_rows(df.exp2_made_children_order_second %>% 
              rename(periphrastic_question_order = made_question_order) %>% 
              select(question, direct, absence, periphrastic_question_order) %>% 
  mutate(age = rep("children")),
            df.exp2_cause_adults_order_second %>% 
              rename(periphrastic_question_order = caused_question_order) %>% 
              select(question, direct, absence, periphrastic_question_order) %>% 
  mutate(age = rep("adults")),
            df.exp2_made_adults_order_second %>% 
              rename(periphrastic_question_order = made_question_order) %>% 
    select(question, direct, absence, periphrastic_question_order) %>% 
  mutate(age = rep("adults"))) %>% 
  pivot_longer(cols = direct:absence,
               names_to = "type",
               values_to = "response") %>% 
  mutate(question = str_replace_all(question, "\\bcause\\b", "caused"),
         age = factor(age, levels = c("children", "adults")))
  

custom_labels = as_labeller(c("direct" = "Direct Cause", "absence" = "Absent Cause"))

ggplot(data = df.plot,
       mapping = aes(x = factor(question, levels = c("caused", "made", "lexical")),
                     y = response,
                     group = interaction(periphrastic_question_order, age),
                     color = periphrastic_question_order,
                     fill = periphrastic_question_order,
                     shape = age)) + 
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  stat_summary(fun.data = "mean_cl_boot",
               position = position_dodge(width = 0.8),
               size = .9,
               color = "black") +  
  scale_fill_brewer(palette = "Set3") +
  scale_color_brewer(palette = "Set3") +
 scale_y_continuous(breaks = seq(0, 1, 0.25),
                      labels = str_c(seq(0, 1, 0.25) * 100, "%"),
                      limits = c(0, 1)) +
  ylab("Probability of selecting \n causal candidate") + 
 scale_shape_manual(values = c(21, 23)) +
  guides(fill = guide_legend(order = 1, override.aes = list(shape = 22, color = NA)),
         color = guide_legend(order = 1, override.aes = list(shape = 22, color = NA)),
         shape = guide_legend(order = 2, override.aes = list(color = "black"))) +
  ylab("Probability of selecting \n causal candidate") +
  theme(legend.position = "bottom",
        legend.box = "vertical",
        axis.title.x = element_blank(),
        text = element_text(size = 18)) +  
  labs(color = "  periphrastic \n\ question order", 
       fill = "   periphrastic \n\ question order",
       shape = "age") +
   facet_wrap(~type,
             labeller = custom_labels) 

ggsave("../../figures/experiment2/absent_order_effect_second_scenario.pdf", height = 4, width = 9.5)


```

# EXPERIMENT 3: ABSENCES 
## EXPLANATION
### ADULTS
#### DATA
##### Read in data

```{r message=FALSE, warning=FALSE}

df.exp3_adults = read_csv("../../data/experiment3/adults/exp3_adults.csv")

```

##### Wrangle

```{r message=FALSE, warning=FALSE}

# clean responses
df.exp3_adults = df.exp3_adults %>% 
  mutate(condition = str_extract(string = responses,
                                 pattern = "sunburn_simple_response|sunburn_made_response|flood_simple_response|flood_made_response"),
         response = str_extract(string = responses, 
                                pattern = ":(.*)"),
         response = str_remove_all(string = response,
                                   pattern = "\""),
         response = str_remove_all(string = response,
                                   pattern = ":"),
         response = str_remove_all(string = response,
                                   pattern = "\\}"),
         response = str_remove_all(string = response,
                                   pattern = "\\."),
         response = str_remove_all(string = response,
                                   pattern = "\\,"),
         response = str_remove_all(string = response,
                                   pattern = "\\\\n"),
         response = str_to_lower(response)) %>% 
  separate(condition, c("scenario", "question", "extra"), "_") %>% 
  rename(participant = workerid) %>% 
  select(participant, scenario, question, response)

# code responses
df.exp3_adults = df.exp3_adults %>%
  mutate(direct = ifelse(str_detect(response,
                                    "^sun$|sun | sun$"), 1, 0),
         direct = ifelse(str_detect(response,
                                    "^water$|water | water$"), 1, direct),
         direct = ifelse(str_detect(response,
                                    "^rain$|rain | rain$"), 1, direct),
         absence = ifelse(str_detect(response,
                                     "^sunscreen$|sunscreen | sunscreen$"), 1, 0),
         absence = ifelse(str_detect(response,
                                     "^window$|window | window$"), 1, absence),
         absence = ifelse(str_detect(response,
                                     "^latch$|latch | latch$"), 1, absence))


```

##### Demographics

```{r message=FALSE, warning=FALSE}

df.exp3_adults_demo = read_csv("../../data/experiment3/adults/exp3_adults_demo.csv")

df.exp3_adults_demo %>% 
  summarise(age_mean = mean(as.numeric(age), na.rm = TRUE))

df.exp3_adults_demo %>% 
  summarise(age_sd = sd(as.numeric(age), na.rm = TRUE))

df.exp3_adults_demo %>% 
  group_by(gender) %>% 
  count() 

df.exp3_adults_demo %>% 
  group_by(race) %>% 
  count() 

df.exp3_adults_demo %>% 
  group_by(ethnicity) %>% 
  count() 


```

#### STATS
##### Descriptives
```{r} 

df.exp3_adults %>% 
  mutate(response_pattern = case_when(
    direct == 1 & absence == 1 ~ "both",
    direct == 0 & absence == 0 ~ "neither",
    direct == 1 & absence == 0  ~ "direct only",
    direct == 0 & absence == 1  ~ "absence only",
  )) %>% 
  group_by(response_pattern) %>% 
  summarize(n = n()) %>% 
  mutate(percentage = n / sum(n) * 100) %>%
  ungroup()


```
##### Bayesian Model

```{r}

# dummy coding
options(contrasts = c("contr.treatment", "contr.poly"))

df.model = df.exp3_adults %>% 
  select(-response) %>% 
  pivot_longer(cols = direct:absence,
               names_to = "causal_candidate",
               values_to = "response") %>% 
mutate(causal_candidate = factor(causal_candidate, levels = c("direct", "absence")))

# check levels of causal_candidate
contrasts(df.model$causal_candidate)

fit.brm.exp = brm(formula = response ~ 1 + causal_candidate + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/explanation_adult") 
fit.brm.exp

```

### CHILDREN
#### DATA
##### Read in Data

```{r message=FALSE, warning=FALSE}

df.exp3_children = read_csv("../../data/experiment3/children/exp3_children.csv")

```

##### Wrangle

```{r message=FALSE, warning=FALSE}

# clean data
df.exp3_children = df.exp3_children %>% 
  clean_names() %>% 
  rename(response_1 = full_response_11,
         response_2 = full_response_13) %>% 
  select(participant_number, rounded_age, scenario_1, scenario_2, response_1, response_2, gender, lan_spoken) %>%
  drop_na() %>% 
  pivot_longer(
    cols = c(-participant_number, -rounded_age, -gender, -lan_spoken),
    names_to = c(".value"),
    names_pattern = "(^scenario|^response)"
  ) %>% 
  mutate(response = str_remove_all(string = response,
                                   pattern = "\""),
         response = str_remove_all(string = response,
                                   pattern = ":"),
         response = str_remove_all(string = response,
                                   pattern = "\\("),
         response = str_remove_all(string = response,
                                   pattern = "\\)"),
         response = str_remove_all(string = response,
                                   pattern = "\\}"),
         response = str_remove_all(string = response,
                                   pattern = "\\."),
         response = str_remove_all(string = response,
                                   pattern = "\\,"),
         response = str_remove_all(string = response,
                                   pattern = "\\\\n"),
         response = str_to_lower(response))

# code responses
df.exp3_children = df.exp3_children %>%
  mutate(direct = ifelse(str_detect(response,
                                    "^sun$|sun | sun$"), 1, 0),
         direct = ifelse(str_detect(response,
                                    "^water$|water | water$"), 1, direct),
         direct = ifelse(str_detect(response,
                                    "^rain$|rain | rain$"), 1, direct),
         absence = ifelse(str_detect(response,
                                     "^sunscreen$|sunscreen | sunscreen$"), 1, 0),
         absence = ifelse(str_detect(response,
                                     "^window$|window | window$"), 1, absence),
         absence = ifelse(str_detect(response,
                                     "^windows$|windows | windows$"), 1, absence),
         absence = ifelse(str_detect(response,
                                     "^latch$|latch | latch$"), 1, absence),
         age = round(rounded_age / 365, digits = 2)) %>% 
  rename(participant = participant_number)
```

##### Demographics

```{r message=FALSE, warning=FALSE}

 # gender
df.exp3_children %>%
  group_by(gender) %>%
  summarise(n = n_distinct(participant)) %>%
  print()
  
  
  # language spoken
df.exp3_children %>%
    mutate(en_occurrence = ifelse(str_detect(lan_spoken, "en"), "en", "non-en")) %>%
    group_by(en_occurrence) %>%
    summarise(n = n_distinct(participant)) %>%
    print()

```

#### STATS
##### Descriptives
```{r} 

df.exp3_children %>% 
  mutate(response_pattern = case_when(
    direct == 1 & absence == 1 ~ "both",
    direct == 0 & absence == 0 ~ "neither",
    direct == 1 & absence == 0  ~ "direct only",
    direct == 0 & absence == 1  ~ "absence only",
  )) %>% 
  group_by(response_pattern) %>% 
  summarize(n = n()) %>% 
  mutate(percentage = n / sum(n) * 100) %>%
  ungroup()


```
##### Bayesian Model

```{r message=FALSE, warning=FALSE}
# dummy coding
options(contrasts = c("contr.treatment", "contr.poly"))

df.model = df.exp3_children %>% 
  select(-response) %>% 
  pivot_longer(cols = direct:absence,
               names_to = "causal_candidate",
               values_to = "response") %>% 
  mutate(causal_candidate = factor(causal_candidate, levels = c("direct", "absence")))


# check levels of causal_candidate
contrasts(df.model$causal_candidate)

# removed random intercepts for scenario to avoid divergent transition errors
fit.brm.exp = brm(formula = response ~ 1 + causal_candidate + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/explanation_children") 
fit.brm.exp

```

### PLOTS
#### Explanation 

```{r fig.height=4, fig.width=5, message=FALSE, warning=FALSE}

df.model = df.exp3_children %>% 
  select(-response) %>% 
  pivot_longer(cols = direct:absence,
               names_to = "causal_candidate",
               values_to = "response") %>% 
  mutate(causal_candidate = factor(causal_candidate, levels = c("direct", "absence")))




fit.brm.explanation = brm(formula = response ~ 1 + causal_candidate*age + (1 | participant) + (1 | scenario),
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 6000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/explanation_children_age") 


fit.brm.explanation




df.data = expand_grid(age = seq(4, 6, 0.1),
                      causal_candidate = c("direct", "absence"))

df.prediction = fit.brm.explanation %>% 
  fitted(newdata = df.data,
         re_formula = NA,
          probs = c(0.1, 0.9)) %>% 
  as_tibble() %>% 
  bind_cols(df.data) %>% 
  clean_names() %>% 
  rename(type = causal_candidate) %>% 
  mutate(type = ifelse(type == "direct", "direct", "absent"))

df.adults = df.exp3_adults %>% 
  select(-response) %>% 
  mutate(age_whole = rep(7)) %>% 
  pivot_longer(cols = (direct:absence),
    names_to = "type",
    values_to = "response")


df.children = df.exp3_children %>% 
  select(-response) %>% 
  mutate(age_whole = as.integer(age)) %>% 
  pivot_longer(cols = (direct:absence),
    names_to = "type",
    values_to = "response")


df.means = df.children %>% 
  bind_rows(df.adults) %>% 
  mutate(age_whole = factor(age_whole, 
                            levels = c(4, 5, 6, 7), 
                            labels = c("4", "5", "6","adults"))) %>% 
  group_by(age_whole, question, type) %>% 
  summarize(
    response = Hmisc::smean.cl.boot(response)) %>%
    mutate(index = c("response", "low", "high")) %>%
    ungroup() %>% 
    pivot_wider(names_from = index,
                values_from = response) %>% 
  mutate(age_whole = fct_recode(age_whole, "7" = "adults"),
         age_whole = as.numeric(as.character(age_whole)),
         type = ifelse(type == "direct", "direct", "absent"))




ggplot(mapping = aes(x = age, 
                     y = response,
                     color = type)) + 
  geom_hline(yintercept=0.50, linetype="dashed", color = "black") +
  geom_smooth(data = df.prediction,
              mapping = aes(y = estimate,
                            ymin = q10,
                            ymax = q90,
                            color = type,
                            fill = type),
              stat = "identity",
              alpha = 0.2) +
  geom_pointrange(data = df.means,
                  mapping = aes(x = age_whole,
                                y = response,
                                ymin = low,
                                ymax = high,
                                fill = type,
                                shape = type),
                  color = "black",
                  size = 0.5,
                  show.legend = TRUE,
                  alpha = 0.8,
                  position = position_dodge(width = 0.1)) +
  scale_fill_manual(values = c("direct" = "#FF7F00", 
                               "absent" = "#984EA3"),
                    breaks = c("direct",
                               "absent")) +
  scale_color_manual(values = c("direct" = "#FF7F00", 
                                "absent" = "#984EA3"),
                     breaks= c("direct",
                               "absent")) +
  scale_shape_manual(values = c("absent" = 21, 
                                "direct" = 23)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = str_c(seq(0, 1, 0.25) * 100, "%"),
                     limits = c(0, 1)) +
  scale_x_continuous(breaks = 4:7,
                     labels = c("4", "5", "6", "Adults")) +
  labs(y = "Probability of selecting \n causal candidate") +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        text = element_text(size = 18)) +
  guides(fill = "none",
         color = "none",
         shape = guide_legend(override.aes = list(fill = c("#FF7F00", "#984EA3")),
                              reverse = T))
  
  
  

ggsave("../../figures/experiment3/explanation.pdf", height = 4, width = 5)

```

#### Responses Patterns
```{r}

df.plot = df.exp3_adults %>% 
  mutate(age = "adults") %>% 
  bind_rows(df.exp3_children %>% 
              mutate(age = "children")) %>% 
   mutate(response_pattern = case_when(
    direct == 1 & absence == 1 ~ "both",
    direct == 0 & absence == 0 ~ "neither",
    direct == 1 & absence == 0  ~ "direct only",
    direct == 0 & absence == 1  ~ "absence only",
  ),
  question = recode(question, "cause" = "caused")) %>% 
  group_by(age, response_pattern) %>% 
  summarize(n = n()) %>% 
  ungroup() %>%
  group_by(age) %>%
  mutate(percentage = n / sum(n) * 100) %>%
  ungroup() %>% 
  mutate(response_pattern = factor(response_pattern, levels = c("absence only", "direct only", "both", "neither")))


ggplot(data = df.plot,
       mapping = aes(x = age,
                     y = percentage,
                     group = response_pattern,
                     color = response_pattern,
                     fill = response_pattern)) +
  geom_col(color = "black") +
  scale_fill_brewer(palette = "Set1") + 
  scale_color_brewer(palette = "Set1") +
  scale_shape_manual(values = c(21, 23)) +
  scale_y_continuous(breaks = seq(0, 100, 25),
                     labels = str_c(seq(0, 100, 25), "%")) +
  labs(y = "Response pattern \n\ probability") +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        text = element_text(size = 18),
        axis.title.x = element_blank()) 

ggsave("../../figures/experiment3/explanation_response_patterns.pdf", height = 4, width = 6)

```
#### Responses Patterns by Age
```{r}

df.plot = df.exp3_adults %>% 
  mutate(age_whole = 7) %>% 
  bind_rows(df.exp3_children %>% 
               mutate(age_whole = as.integer(age))) %>% 
  mutate(response_pattern = case_when(
    direct == 1 & absence == 1 ~ "both",
    direct == 0 & absence == 0 ~ "neither",
    direct == 1 & absence == 0  ~ "direct only",
    direct == 0 & absence == 1  ~ "absence only",
  ),
  question = recode(question, "cause" = "caused"),
  age_whole = as.factor(age_whole)) %>% 
  group_by(age_whole, response_pattern) %>% 
  summarize(n = n()) %>% 
  ungroup() %>%
  group_by(age_whole) %>%
  mutate(percentage = n / sum(n) * 100) %>%
  ungroup() %>% 
  mutate(response_pattern = factor(response_pattern, levels = c("absence only", "direct only", "both", "neither")))


ggplot(data = df.plot,
       mapping = aes(x = age_whole,
                     y = percentage,
                     group = response_pattern,
                     color = response_pattern,
                     fill = response_pattern)) +
  geom_col(color = "black") +
  scale_fill_brewer(palette = "Set1") + 
  scale_color_brewer(palette = "Set1") +
  scale_shape_manual(values = c(21, 23)) +
  scale_y_continuous(breaks = seq(0, 100, 25),
                     labels = str_c(seq(0, 100, 25), "%")) +
  scale_x_discrete(breaks = 4:7,
                     labels = c("4", "5", "6", "Adults")) +
  labs(y = "Response pattern \n\ probability") +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        text = element_text(size = 18),
        axis.title.x = element_blank()) 


ggsave("../../figures/experiment3/explanation_response_patterns_age.pdf", height = 4, width = 6)

```


# APPENDIX
# EXPERIMENT 1: CHAINS
## CAUSE V LEXICAL (BREAK & CRACK)
### ADULTS
#### STATS
##### Bayesian Models
###### Distal

```{r message=FALSE, warning=FALSE}


df.model = df.exp1_cause_adults %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "cause"))

# Check contrast values
 contrasts(df.model$question)

# removed random intercepts for scenario to avoid divergent transition errors
fit.brm.cause.adult.distal = brm(formula = distal ~ 1 + question + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_adult_distal") 
fit.brm.cause.adult.distal


```

###### Proximal

```{r}

fit.brm.cause.adult.proximal = brm(formula = proximal ~ 1 + question + (1 | participant) + (1 | scenario),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/cause_adult_proximal") 

fit.brm.cause.adult.proximal

```

### CHILDREN
#### STATS
##### Bayesian Models
###### Distal

```{r message=FALSE, warning=FALSE}

df.model = df.exp1_cause_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "caused"),
         age = age - mean(age))

# Check contrast values
 contrasts(df.model$question)


fit.brm.cause.children.distal = brm(formula = distal ~ 1 + question + (1 | participant) + (1 | scenario),
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_children_distal") 

fit.brm.cause.children.distal


fit.brm.cause.children.distal.age = brm(formula = distal ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_children_distal_age") 

fit.brm.cause.children.distal.age 

```

###### Proximal
```{r message=FALSE, warning=FALSE}

# removed random intercepts for scenario to avoid divergent transition errors
fit.brm.cause.children.proximal = brm(formula = proximal ~ 1 + question + (1 | participant),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/cause_children_proximal") 

fit.brm.cause.children.proximal


fit.brm.cause.children.proximal.age = brm(formula = proximal ~ 1 + question*age + (1 | participant) + (1 | scenario),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/cause_children_proximal_age") 

fit.brm.cause.children.proximal.age


```

## MADE v LEXICAL (BREAK & CRACK)
### ADULTS
#### STATS
##### Bayesian Models
###### Distal

```{r message=FALSE, warning=FALSE}

df.model = df.exp1_made_adults %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "made"))

# Check contrast values
 contrasts(df.model$question)


fit.brm.made.adult.distal = brm(formula = distal ~ 1 + question + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/made_adult_distal") 

fit.brm.made.adult.distal




```

###### Proximal

```{r message=FALSE, warning=FALSE}

fit.brm.made.adult.proximal = brm(formula = proximal ~ 1 + question + (1 | participant) + (1 | scenario),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/made_adult_proximal") 

fit.brm.made.adult.proximal


```

### CHILDREN
#### STATS
##### Bayesian Models
###### Distal
```{r message=FALSE, warning=FALSE}

df.model = df.exp1_made_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "made"),
         age = age - mean(age))

# Check contrast values
 contrasts(df.model$question)


fit.brm.made.children.distal = brm(formula = distal ~ 1 + question + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/made_children_distal") 

fit.brm.made.children.distal


fit.brm.made.children.distal.age = brm(formula = distal ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/made_children_distal_age") 

fit.brm.made.children.distal.age

```

###### Proximal

```{r message=FALSE, warning=FALSE}

fit.brm.proximal = brm(formula = proximal ~ 1 + question + (1 | participant) + (1 | scenario),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/made_children_proximal") 

fit.brm.proximal


fit.brm.proximal.age = brm(formula = proximal ~ 1 + question*age + (1 | participant) + (1 | scenario),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/made_children_proximal_age") 

fit.brm.proximal.age



```

## CAUSE v MADE
### ADULTS
#### DATA
##### Wrangle

```{r message=FALSE, warning=FALSE}

df.exp1_cause_made_adults = df.exp1_cause_adults %>% 
  filter(question == "cause") %>% 
  select(-participant) %>% 
  bind_rows(df.exp1_made_adults %>% 
  filter(question == "made") %>% 
  select(-participant)) %>% 
  mutate(participant = rep(1:(n()/2), each = 2))


```

#### STATS

##### Bayesian Models
###### Distal

```{r message=FALSE, warning=FALSE}

df.model = df.exp1_cause_made_adults %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "made"))

# Check contrast values
 contrasts(df.model$question)


fit.brm.cause.made.adult.distal = brm(formula = distal ~ 1 + question + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_made_adult_distal") 

fit.brm.cause.made.adult.distal



```

###### Proximal

```{r message=FALSE, warning=FALSE}

fit.brm.cause.made.adult.proximal = brm(formula = proximal ~ 1 + question + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_made_adult_proximal") 

fit.brm.cause.made.adult.proximal

```

### CHILDREN
#### DATA
##### Wrangle

```{r message=FALSE, warning=FALSE}

df.exp1_cause_made_children = df.exp1_cause_children %>% 
  filter(question == "caused") %>% 
  select(-caused_question_order, participant) %>% 
  bind_rows(df.exp1_made_children %>% 
  filter(question == "made") %>% 
  select(-made_question_order, participant)) %>% 
  mutate(participant = rep(1:(n()/2), each = 2))


```

#### STATS

##### Bayesian Models
###### Distal

```{r message=FALSE, warning=FALSE}

df.model = df.exp1_cause_made_children %>% 
  mutate(question = fct_relevel(question, "made"),
         age = age - mean(age))

# Check contrast values
 contrasts(df.model$question)



fit.brm.cause.made.children.distal = brm(formula = distal ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_made_children_distal.rds") 

fit.brm.cause.made.children.distal


```

###### Proximal

```{r message=FALSE, warning=FALSE}

fit.brm.cause.made.children.proximal = brm(formula = proximal ~ 1 + question*age + (1 | participant) + (1 | scenario),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/cause_made_children_proximal") 

fit.brm.cause.made.children.proximal



```


## ORDER EFFECTS
### CHILDREN
#### DATA
##### Wrangle

```{r}

df.exp1_cause_children_order = df.exp1_cause_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "lexical"),
         caused_question_order = as_factor(caused_question_order),
         caused_question_order = fct_relevel(caused_question_order, "first")) %>% 
   group_by(participant) %>%
   filter(row_number() <= 2) %>%
  ungroup()



df.exp1_made_children_order = df.exp1_made_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "lexical"),
         made_question_order = as_factor(made_question_order),
         made_question_order = fct_relevel(made_question_order, "first")) %>% 
   group_by(participant) %>%
   filter(row_number() <= 2) %>%
  ungroup()

df.exp1_lexical_children_order = df.exp1_cause_children_order %>% 
  filter(question == "lexical") %>% 
  rename(periphrastic_question_order = caused_question_order) %>% 
  select(-participant) %>% 
  bind_rows(df.exp1_made_children_order %>% 
             filter(question == "lexical") %>% 
  rename(periphrastic_question_order = made_question_order) %>% 
  select(-participant)) %>% 
  mutate(participant = rep(1:n()),
         periphrastic_question_order = as_factor(periphrastic_question_order),
         periphrastic_question_order = fct_relevel(periphrastic_question_order, "first"))


```

#### STATS

##### Bayesian Models
###### Distal

```{r message=FALSE, warning=FALSE}

df.model = df.exp1_cause_children_order %>% 
  filter(question == "caused")

# Check contrast values
 contrasts(df.model$caused_question_order)


cause_children_distal_order = brm(formula = distal ~ 1 + caused_question_order + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_children_distal_order") 

cause_children_distal_order


df.model = df.exp1_made_children_order %>% 
  filter(question == "made")

# Check contrast values
 contrasts(df.model$made_question_order)


made_children_distal_order = brm(formula = distal ~ 1 + made_question_order + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/made_children_distal_order") 

made_children_distal_order


df.model = df.exp1_lexical_children_order

# Check contrast values
 contrasts(df.model$periphrastic_question_order)
 
lexical_children_distal_order = brm(formula = distal ~ 1 + periphrastic_question_order + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/lexical_children_distal_order") 

lexical_children_distal_order



```

###### Proximal

```{r message=FALSE, warning=FALSE}

df.model = df.exp1_cause_children_order %>% 
  filter(question == "caused")

# Check contrast values
 contrasts(df.model$caused_question_order)


cause_children_proximal_order = brm(formula = proximal ~ 1 + caused_question_order + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_children_proximal_order") 

cause_children_proximal_order


df.model = df.exp1_made_children_order %>% 
  filter(question == "made")

# Check contrast values
 contrasts(df.model$made_question_order)


made_children_proximal_order = brm(formula = proximal ~ 1 + made_question_order + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/made_children_proximal_order") 

made_children_proximal_order


df.model = df.exp1_lexical_children_order

# Check contrast values
 contrasts(df.model$periphrastic_question_order)
 
lexical_children_proximal_order = brm(formula = proximal ~ 1 + periphrastic_question_order + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/lexical_children_proximal_order") 

lexical_children_proximal_order



```

## PLOTS
### Response Plots
#### Cause
```{r message=FALSE, warning=FALSE}

df.model = df.exp1_cause_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "caused"))

fit.brm.distal.cause.age2 = brm(formula = distal ~ 1 + question*age + (1 | participant) + (1 | scenario),
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .9999),
                     file = "cache/fit.brm.distal.cause.age2")


fit.brm.proximal.cause.age2 = brm(formula = proximal ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 6000,
                     warmup = 1000,
                     control = list(adapt_delta = .9999),
                     file = "cache/fit.brm.proximal.cause.age2")

df.data = expand_grid(age = seq(4, 9, 0.1),
                      question = c("caused", "lexical"))

df.prediction = fit.brm.distal.cause.age2 %>% 
  fitted(newdata = df.data,
         re_formula = NA,
          probs = c(0.1, 0.9)) %>% 
  as_tibble() %>% 
  bind_cols(df.data) %>% 
  mutate(type = "distal") %>% 
  bind_rows(fit.brm.proximal.cause.age2 %>% 
              fitted(newdata = df.data,
                     re_formula = NA,
                     probs = c(0.1, 0.9)) %>% 
              as_tibble() %>% 
              bind_cols(df.data) %>% 
              mutate(type = "proximal")) %>% 
  clean_names()

df.adults = df.exp1_cause_adults %>% 
  select(-response) %>% 
  mutate(age_whole = rep(10)) %>% 
  pivot_longer(cols = (proximal:distal),
               names_to = "type",
               values_to = "response")

df.children = df.exp1_cause_children %>% 
  select(-response) %>% 
  pivot_longer(cols = distal:proximal,
               names_to = "type",
               values_to = "response")

df.means = df.children %>% 
  bind_rows(df.adults) %>% 
  mutate(age_whole = factor(age_whole, 
                            levels = c(4, 5, 6, 7, 8, 9, 10), 
                            labels = c("4", "5", "6", "7", "8", "9", "adults")),
         question = recode(question, "cause" = "caused")) %>% 
  group_by(age_whole, question, type) %>% 
  summarize(
    response = Hmisc::smean.cl.boot(response)) %>%
    mutate(index = c("response", "low", "high")) %>%
    ungroup() %>% 
    pivot_wider(names_from = index,
                values_from = response) %>% 
  mutate(age_whole = fct_recode(age_whole, "10" = "adults"),
         age_whole = as.numeric(as.character(age_whole)))


custom_labels = as_labeller(c("distal" = "Distal Cause", "proximal" = "Proximal Cause"))

p3 = ggplot(mapping = aes(x = age, 
                     y = response,
                     color = question)) + 
  geom_hline(yintercept=0.50, linetype="dashed", color = "black") +
  geom_smooth(data = df.prediction,
              mapping = aes(y = estimate,
                            ymin = q10,
                            ymax = q90,
                            color = question,
                            fill = question),
              stat = "identity",
              alpha = 0.2,
              show.legend = F) +
  geom_pointrange(data = df.means,
                  mapping = aes(x = age_whole,
                                y = response,
                                ymin = low,
                                ymax = high,
                                fill = question,
                                shape = question),
                  color = "black",
                  size = 0.5,
                  show.legend = TRUE,
                  alpha = 0.8,
                  position = position_dodge(width = 0.1)) +
    facet_wrap(~type,
             labeller = custom_labels) + 
  scale_fill_brewer(palette = "Set1") + 
  scale_color_brewer(palette = "Set1") +
  scale_shape_manual(values = c(21, 23)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                      labels = str_c(seq(0, 1, 0.25) * 100, "%")) +
  scale_x_continuous(breaks = 4:10,
                     labels = c("4", "5", "6", "7", "8", "9", "Adults")) +
  labs(y = "Probability of selecting \n causal candidate") +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        text = element_text(size = 18)) +
  guides(color = guide_legend(reverse = TRUE),
         fill = guide_legend(reverse = TRUE),
         shape = guide_legend(reverse = TRUE))




```

#### Made
```{r message=FALSE, warning=FALSE}


df.model = df.exp1_made_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "made"))


fit.brm.distal.age2.made = brm(formula = distal ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .9999),
                     file = "cache/fit.brm.distal.age2.made")


fit.brm.proximal.age2.made = brm(formula = proximal ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .9999),
                     file = "cache/fit.brm.proximal.age2.made")

df.data = expand_grid(age = seq(4, 9, 0.1),
                      question = c("made", "lexical"))

df.prediction = fit.brm.distal.age2.made %>% 
  fitted(newdata = df.data,
         re_formula = NA,
          probs = c(0.1, 0.9)) %>% 
  as_tibble() %>% 
  bind_cols(df.data) %>% 
  mutate(type = "distal") %>% 
  bind_rows(fit.brm.proximal.age2.made %>% 
              fitted(newdata = df.data,
                     re_formula = NA,
                     probs = c(0.1, 0.9)) %>% 
              as_tibble() %>% 
              bind_cols(df.data) %>% 
              mutate(type = "proximal")) %>% 
  clean_names()

df.adults = df.exp1_made_adults %>% 
  select(-response) %>% 
  mutate(age_whole = rep(10)) %>% 
  pivot_longer(cols = (proximal:distal),
               names_to = "type",
               values_to = "response")

df.children = df.exp1_made_children %>% 
  select(-response) %>% 
  pivot_longer(cols = distal:proximal,
               names_to = "type",
               values_to = "response")

df.means = df.children %>% 
  bind_rows(df.adults) %>% 
  mutate(age_whole = factor(age_whole, 
                            levels = c(4, 5, 6, 7, 8, 9, 10), 
                            labels = c("4", "5", "6", "7", "8", "9", "adults"))) %>% 
  group_by(age_whole, question, type) %>% 
  summarize(
    response = Hmisc::smean.cl.boot(response)) %>%
    mutate(index = c("response", "low", "high")) %>%
    ungroup() %>% 
    pivot_wider(names_from = index,
                values_from = response) %>% 
  mutate(age_whole = fct_recode(age_whole, "10" = "adults"),
         age_whole = as.numeric(as.character(age_whole)))

custom_labels = as_labeller(c("distal" = "Distal Cause", "proximal" = "Proximal Cause"))

df.means = df.means %>%
  mutate(question = factor(question, levels = c("made", "lexical")))

p4 = ggplot(mapping = aes(x = age, 
                     y = response,
                     color = question)) + 
  geom_hline(yintercept=0.50, linetype="dashed", color = "black") +
  geom_smooth(data = df.prediction,
              mapping = aes(y = estimate,
                            ymin = q10,
                            ymax = q90,
                            color = question,
                            fill = question),
              stat = "identity",
              alpha = 0.2,
              show.legend = F) +
  geom_pointrange(data = df.means,
                  mapping = aes(x = age_whole,
                                y = response,
                                ymin = low,
                                ymax = high,
                                fill = question,
                                shape = question),
                  color = "black",
                  size = 0.5,
                  show.legend = TRUE,
                  alpha = 0.8,
                  position = position_dodge(width = 0.3)) +
  facet_wrap(~type,
             labeller = custom_labels) + 
  scale_fill_manual(values = c("made" = "#4DAF4A", "lexical" = "#377EB8"), breaks=c("made", "lexical")) +
  scale_color_manual(values = c("made" = "#4DAF4A", "lexical" = "#377EB8"), breaks=c("made", "lexical")) +
  scale_shape_manual(values = c(21, 23), breaks=c("made", "lexical")) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = str_c(seq(0, 1, 0.25) * 100, "%"),
                     limits = c(0, 1)) +
  scale_x_continuous(breaks = 4:10,
                     labels = c("4", "5", "6", "7", "8", "9", "Adults")) +
  labs(y = "Probability of selecting \n causal candidate") + 
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        text = element_text(size = 18)) 

  
```

#### Combine Cause and Made Plots
```{r fig.height=5, fig.width=18, message=FALSE, warning=FALSE}

plot = p3 + p4 + 
plot_layout(nrow = 1) &
plot_annotation(tag_levels = "A") &
theme(plot.tag = element_text(face = "bold"))

ggsave(plot, filename = "../../figures/experiment1/chain_all.pdf", height = 5, width = 18)

plot


```

### Order Effects 
#### First Scenario

```{r fig.height=4, fig.width=8, message=FALSE, warning=FALSE}

df.plot = df.exp1_cause_children_order %>% 
  rename(periphrastic_question_order = caused_question_order) %>% 
  bind_rows(df.exp1_made_children_order %>% 
              rename(periphrastic_question_order = made_question_order)) %>% 
  select(-response) %>% 
  pivot_longer(cols = distal:proximal,
               names_to = "type",
               values_to = "response")

custom_labels = as_labeller(c("distal" = "Distal Cause", "proximal" = "Proximal Cause"))


ggplot(data = df.plot,
       mapping = aes(x = factor(question, levels = c("caused", "made", "lexical")),
                     y = response,
                     color = periphrastic_question_order,
                     fill = periphrastic_question_order)) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
   stat_summary(fun.data = "mean_cl_boot",
               position = position_dodge(width = 0.5),
               shape = 21,
               color = "black",
               size = 1) +
  scale_fill_brewer(palette = "Set3") +
  scale_color_brewer(palette = "Set3") +
   scale_y_continuous(breaks = seq(0, 1, 0.25),
                      labels = str_c(seq(0, 1, 0.25) * 100, "%"),
                      limits = c(0, 1)) +
  ylab("Probability of selecting \n causal candidate") +
  theme(legend.position = "bottom",
        legend.box = "vertical",
        axis.title.x = element_blank(),
        text = element_text(size = 18)) +
  labs(color = "  periphrastic \n\ question order",
       fill = "   periphrastic \n\ question order") +
  guides(color = guide_legend(override.aes = list(fill = NA))) +
   facet_wrap(~type,
             labeller = custom_labels) 

ggsave("../../figures/experiment1/chain_order_effect_first_scenario.pdf", height = 4, width = 8)


```

#### Second Scenario

```{r fig.height=4, fig.width=8, message=FALSE, warning=FALSE}

df.exp1_cause_children_order_second = df.exp1_cause_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "lexical"),
         caused_question_order = as_factor(caused_question_order),
         caused_question_order = fct_relevel(caused_question_order, "first")) %>% 
   group_by(participant) %>%
   filter(row_number() %in% 3:4) %>%
  ungroup()



df.exp1_made_children_order_second = df.exp1_made_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "lexical"),
         made_question_order = as_factor(made_question_order),
         made_question_order = fct_relevel(made_question_order, "first")) %>% 
   group_by(participant) %>%
   filter(row_number() %in% 3:4) %>%
  ungroup()



df.plot = df.exp1_cause_children_order_second %>% 
  rename(periphrastic_question_order = caused_question_order) %>% 
  bind_rows(df.exp1_made_children_order_second %>% 
              rename(periphrastic_question_order = made_question_order)) %>% 
  select(-response) %>% 
  pivot_longer(cols = distal:proximal,
               names_to = "type",
               values_to = "response")

custom_labels = as_labeller(c("distal" = "Distal Cause", "proximal" = "Proximal Cause"))


ggplot(data = df.plot,
       mapping = aes(x = factor(question, levels = c("caused", "made", "lexical")),
                     y = response,
                     color = periphrastic_question_order,
                     fill = periphrastic_question_order)) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
   stat_summary(fun.data = "mean_cl_boot",
               position = position_dodge(width = 0.5),
               shape = 21,
               color = "black",
               size = 1) +
  scale_fill_brewer(palette = "Set3") +
  scale_color_brewer(palette = "Set3") +
   scale_y_continuous(breaks = seq(0, 1, 0.25),
                      labels = str_c(seq(0, 1, 0.25) * 100, "%"),
                      limits = c(0, 1)) +
  ylab("Probability of selecting \n causal candidate") +
  theme(legend.position = "bottom",
        legend.box = "vertical",
        axis.title.x = element_blank(),
        text = element_text(size = 18)) +
  labs(color = "  periphrastic \n\ question order",
       fill = "   periphrastic \n\ question order") +
  guides(color = guide_legend(override.aes = list(fill = NA))) +
   facet_wrap(~type,
             labeller = custom_labels) 

ggsave("../../figures/experiment1/chain_order_effect_second_scenario.pdf", height = 4, width = 8)


```


# EXPERIMENT 2: ABSENCES
## CAUSE V LEXICAL (BURN & FLOOD)
### ADULTS
#### STATS
##### Bayesian Models
###### Direct

```{r message=FALSE, warning=FALSE}

df.model = df.exp2_cause_adults  %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "cause"))

# Check contrast values
 contrasts(df.model$question)

fit.brm.direct = brm(formula = direct ~ 1 + question + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_adult_direct") 
fit.brm.direct

```

###### Absent
```{r}

fit.brm.absent = brm(formula = absence ~ 1 + question + (1 | participant) + (1 | scenario),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/cause_adult_absent") 

fit.brm.absent

```

### CHILDREN
#### STATS

##### Bayesian Models
###### Direct
```{r message=FALSE, warning=FALSE}

df.model = df.exp2_cause_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "caused"),
         age = age - mean(age))

# Check contrast values
 contrasts(df.model$question)

fit.brm.direct = brm(formula = direct ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_children_direct") 
fit.brm.direct

```

###### Absent
```{r message=FALSE, warning=FALSE}

# removed random intercepts for scenario to avoid divergent transition errors
fit.brm.absent = brm(formula = absence ~ 1 + question*age + (1 | participant),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/cause_children_absent") 


fit.brm.absent

```

## MADE V LEXICAL (BURN & FLOOD)
### ADULTS
##### Bayesian Models
###### Direct

```{r}

df.model = df.exp2_made_adults %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "made"))

# Check contrast values
 contrasts(df.model$question)

fit.brm.direct = brm(formula = direct ~ 1 + question + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/made_adult_direct") 
fit.brm.direct

```

###### Absent

```{r}

fit.brm.absent = brm(formula = absence ~ 1 + question + (1 | participant) + (1 | scenario),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/made_adult_absent") 

fit.brm.absent

```

### CHILDREN
#### STATS
##### Bayesian Models
###### Direct

```{r message=FALSE, warning=FALSE}

df.model = df.exp2_made_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "made"),
         age = age - mean(age)) 

# Check contrast values
 contrasts(df.model$question)

fit.brm.direct = brm(formula = direct ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/made_children_direct") 
fit.brm.direct

```

###### Absent
```{r message=FALSE, warning=FALSE}

# removed random intercepts for scenario to avoid divergent transition errors
fit.brm.absent = brm(formula = absence ~ 1 + question*age + (1 | participant),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/made_children_absent") 


fit.brm.absent

```

## CAUSE v MADE
### ADULTS
#### DATA
##### Wrangle

```{r message=FALSE, warning=FALSE}

df.exp2_cause_made_adults = df.exp2_cause_adults %>% 
  filter(question == "cause") %>% 
  select(-participant) %>% 
  bind_rows(df.exp2_made_adults %>% 
  filter(question == "made") %>% 
  select(-participant)) %>% 
  mutate(participant = rep(1:(n()/2), each = 2))


```

#### STATS

##### Bayesian Models
###### Direct

```{r message=FALSE, warning=FALSE}

df.model = df.exp2_cause_made_adults %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "made"))

# Check contrast values
 contrasts(df.model$question)


fit.brm.cause.made.adult.direct = brm(formula = direct ~ 1 + question + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_made_adult_direct") 

fit.brm.cause.made.adult.direct



```

###### Absent

```{r message=FALSE, warning=FALSE}

fit.brm.cause.made.adult.absent = brm(formula = absence ~ 1 + question + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_made_adult_absence") 

fit.brm.cause.made.adult.absent

```

### CHILDREN
#### DATA
##### Wrangle

```{r message=FALSE, warning=FALSE}

df.exp2_cause_made_children = df.exp2_cause_children %>% 
  filter(question == "caused") %>% 
  select(-cause_question_order, participant) %>% 
  bind_rows(df.exp2_made_children %>% 
  filter(question == "made") %>% 
  select(-made_question_order, participant)) %>% 
  mutate(participant = rep(1:(n()/2), each = 2))


```

#### STATS

##### Bayesian Models
###### Direct

```{r message=FALSE, warning=FALSE}

df.model = df.exp2_cause_made_children %>% 
  mutate(question = fct_relevel(question, "made"),
         age = age - mean(age))

# Check contrast values
 contrasts(df.model$question)



fit.brm.cause.made.children.direct = brm(formula = direct ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_made_children_direct.rds") 

fit.brm.cause.made.children.direct


```

###### Absent

```{r message=FALSE, warning=FALSE}


fit.brm.cause.made.children.absent = brm(formula = absence ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_made_children_absence.rds") 

fit.brm.cause.made.children.absent


```
## ORDER EFFECTS
### ADULTS
#### DATA
##### Wrangle

```{r}

# code order
df.tmp = df.exp2_cause_adults %>% 
  group_by(participant) %>% 
  filter(row_number() == 1) %>% 
  mutate(scenario_order = str_c(scenario, "_first"),
         question_order = str_c(question, "_first")) %>% 
  select(participant,
         contains("order"))

df.exp2_cause_adults_order = df.exp2_cause_adults %>% 
  left_join(df.tmp,
            by = "participant") %>% 
  relocate(contains("order"), .after = question) %>% 
  mutate(caused_question_order = case_when(question_order == "lexical_first" ~ "second",
                                          question_order == "cause_first" ~ "first"),
         question = as_factor(question),
         question = fct_relevel(question, "lexical"),
         caused_question_order = as_factor(caused_question_order),
         caused_question_order = fct_relevel(caused_question_order, "first")) %>% 
   group_by(participant) %>%
   filter(row_number() <= 2) %>%
  ungroup()


# code order
df.tmp = df.exp2_made_adults %>% 
  group_by(participant) %>% 
  filter(row_number() == 1) %>% 
  mutate(scenario_order = str_c(scenario, "_first"),
         question_order = str_c(question, "_first")) %>% 
  select(participant,
         contains("order"))

df.exp2_made_adults_order = df.exp2_made_adults %>% 
  left_join(df.tmp,
            by = "participant") %>% 
  relocate(contains("order"), .after = question) %>% 
  mutate(made_question_order = case_when(question_order == "lexical_first" ~ "second",
                                          question_order == "made_first" ~ "first"),
         question = as_factor(question),
         question = fct_relevel(question, "lexical"),
         made_question_order = as_factor(made_question_order),
         made_question_order = fct_relevel(made_question_order, "first")) %>% 
   group_by(participant) %>%
   filter(row_number() <= 2) %>%
  ungroup()

df.exp2_lexical_adults_order = df.exp2_cause_adults_order %>% 
  filter(question == "lexical") %>% 
  rename(periphrastic_question_order = caused_question_order) %>% 
  select(-participant) %>% 
  bind_rows(df.exp2_made_adults_order %>% 
             filter(question == "lexical") %>% 
  rename(periphrastic_question_order = made_question_order) %>% 
  select(-participant)) %>% 
  mutate(participant = rep(1:n()),
         periphrastic_question_order = as_factor(periphrastic_question_order),
         periphrastic_question_order = fct_relevel(periphrastic_question_order, "first"))

```

#### STATS

##### Bayesian Models
###### Direct

```{r message=FALSE, warning=FALSE}

df.model = df.exp2_cause_adults_order %>% 
  filter(question == "cause")

# Check contrast values
 contrasts(df.model$caused_question_order)


cause_adults_direct_order = brm(formula = direct ~ 1 + caused_question_order + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_adults_direct_order") 

cause_adults_direct_order


df.model = df.exp2_made_adults_order %>% 
  filter(question == "made")

# Check contrast values
 contrasts(df.model$made_question_order)


made_adults_direct_order = brm(formula = direct ~ 1 + made_question_order + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/made_adults_direct_order") 

made_adults_direct_order


df.model = df.exp2_lexical_adults_order

# Check contrast values
 contrasts(df.model$periphrastic_question_order)
 
lexical_adults_direct_order = brm(formula = direct ~ 1 + periphrastic_question_order + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/lexical_adults_direct_order") 

lexical_adults_direct_order



```

###### Absent

```{r message=FALSE, warning=FALSE}

df.model = df.exp2_cause_adults_order %>% 
  filter(question == "cause")

# Check contrast values
 contrasts(df.model$caused_question_order)
 
cause_adults_absent_order = brm(formula = absence ~ 1 + caused_question_order + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_adults_absence_order") 

cause_adults_absent_order




df.model = df.exp2_made_adults_order %>% 
  filter(question == "made")

# Check contrast values
 contrasts(df.model$made_question_order)
 
made_adults_absent_order = brm(formula = absence ~ 1 + made_question_order + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/made_adults_absence_order") 

made_adults_absent_order



df.model = df.exp2_lexical_adults_order

# Check contrast values
 contrasts(df.model$periphrastic_question_order)
 
lexical_adults_absent_order = brm(formula = absence ~ 1 + periphrastic_question_order + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/lexical_adults_absence_order") 

lexical_adults_absent_order



```

### CHILDREN
#### DATA
##### Wrangle

```{r}

df.exp2_cause_children_order = df.exp2_cause_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "lexical"),
         caused_question_order = as_factor(cause_question_order),
         caused_question_order = fct_relevel(caused_question_order, "first")) %>% 
   group_by(participant) %>%
   filter(row_number() <= 2) %>%
  ungroup()



df.exp2_made_children_order = df.exp2_made_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "lexical"),
         made_question_order = str_replace_all(made_question_order, "frst", "first"),
         made_question_order = str_replace_all(made_question_order, "scond", "second"),
         made_question_order = as_factor(made_question_order),
         made_question_order = fct_relevel(made_question_order, "first")) %>% 
   group_by(participant) %>%
   filter(row_number() <= 2) %>%
  ungroup()

df.exp2_lexical_children_order = df.exp2_cause_children_order %>% 
  filter(question == "lexical") %>% 
  rename(periphrastic_question_order = caused_question_order) %>% 
  select(-participant) %>% 
  bind_rows(df.exp2_made_children_order %>% 
             filter(question == "lexical") %>% 
  rename(periphrastic_question_order = made_question_order) %>% 
  select(-participant)) %>% 
  mutate(participant = rep(1:n()),
         periphrastic_question_order = as_factor(periphrastic_question_order),
         periphrastic_question_order = fct_relevel(periphrastic_question_order, "first"))


```

#### STATS

##### Bayesian Models
###### Direct

```{r message=FALSE, warning=FALSE}

df.model = df.exp2_cause_children_order %>% 
  filter(question == "caused")

# Check contrast values
 contrasts(df.model$caused_question_order)


cause_children_direct_order = brm(formula = direct ~ 1 + caused_question_order + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_children_direct_order") 

cause_children_direct_order


df.model = df.exp2_made_children_order %>% 
  filter(question == "made")

# Check contrast values
 contrasts(df.model$made_question_order)


made_children_direct_order = brm(formula = direct ~ 1 + made_question_order + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/made_children_direct_order") 

made_children_direct_order


df.model = df.exp2_lexical_children_order

# Check contrast values
 contrasts(df.model$periphrastic_question_order)
 
lexical_children_direct_order = brm(formula = direct ~ 1 + periphrastic_question_order + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/lexical_children_direct_order") 

lexical_children_direct_order



```
###### Absent

```{r message=FALSE, warning=FALSE}

df.model = df.exp2_cause_children_order %>% 
  filter(question == "caused")

# Check contrast values
 contrasts(df.model$caused_question_order)


cause_children_absent_order = brm(formula = absence ~ 1 + caused_question_order + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_children_absent_order") 

cause_children_absent_order


df.model = df.exp2_made_children_order %>% 
  filter(question == "made")

# Check contrast values
 contrasts(df.model$made_question_order)


made_children_absent_order = brm(formula = absence ~ 1 + made_question_order + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/made_children_absent_order") 

made_children_absent_order


df.model = df.exp2_lexical_children_order

# Check contrast values
 contrasts(df.model$periphrastic_question_order)
 
lexical_children_absent_order = brm(formula = absence ~ 1 + periphrastic_question_order + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/lexical_children_absent_order") 

lexical_children_absent_order



```

## PLOTS
### Response Plots
#### Cause
```{r message=FALSE, warning=FALSE}

df.model = df.exp2_cause_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "caused"))

# removed random intercepts for scenario to avoid divergent transition errors
fit.brm.present.cause.age2 = brm(formula = direct ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 6000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999,
                                    max_treedepth = 15),
                     file = "cache/fit.brm.present.cause.age2") 



fit.brm.absence.cause.age2 = brm(formula = absence ~ 1 + question*age + (1 | participant) + (1 | scenario),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 6000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999,
                                     max_treedepth = 15),
                      file = "cache/fit.brm.absence.cause.age2") 



df.data = expand_grid(age = seq(4, 9, 0.1),
                      question = c("caused", "lexical"))

df.prediction = fit.brm.present.cause.age2 %>% 
  fitted(newdata = df.data,
         re_formula = NA,
          probs = c(0.1, 0.9)) %>% 
  as_tibble() %>% 
  bind_cols(df.data) %>% 
  mutate(type = "presence") %>% 
  bind_rows(fit.brm.absence.cause.age2 %>% 
              fitted(newdata = df.data,
                     re_formula = NA,
                     probs = c(0.1, 0.9)) %>% 
              as_tibble() %>% 
              bind_cols(df.data) %>% 
              mutate(type = "absence")) %>% 
  clean_names()

df.adults = df.exp2_cause_adults %>% 
  select(-response) %>% 
  mutate(age_whole = rep(10)) %>% 
  pivot_longer(cols = (direct:absence),
    names_to = "type",
    values_to = "response")



df.children = df.exp2_cause_children%>%
  select(-response) %>% 
 pivot_longer(cols = (direct:absence),
               names_to = "type",
               values_to = "response")

df.means = df.children %>% 
  bind_rows(df.adults) %>% 
  mutate(age_whole = factor(age_whole, 
                            levels = c(4, 5, 6, 7, 8, 9, 10), 
                            labels = c("4", "5", "6", "7", "8", "9", "adults")),
         question = recode(question, "cause" = "caused"),
         type = recode(type, "direct" = "presence")) %>% 
  group_by(age_whole, question, type) %>% 
  summarize(
    response = Hmisc::smean.cl.boot(response)) %>%
    mutate(index = c("response", "low", "high")) %>%
    ungroup() %>% 
    pivot_wider(names_from = index,
                values_from = response) %>% 
  mutate(age_whole = fct_recode(age_whole, "10" = "adults"),
         age_whole = as.numeric(as.character(age_whole)))



custom_labels = as_labeller(c("absence" = "Absent Cause", "presence" = "Direct Cause"))

p7 = ggplot(mapping = aes(x = age, 
                     y = response,
                     color = question)) + 
  geom_hline(yintercept=0.50, linetype="dashed", color = "black") +
  geom_smooth(data = df.prediction,
              mapping = aes(y = estimate,
                            ymin = q10,
                            ymax = q90,
                            color = question,
                            fill = question),
              stat = "identity",
              alpha = 0.2,
              show.legend = F) +
  geom_pointrange(data = df.means,
                  mapping = aes(x = age_whole,
                                y = response,
                                ymin = low,
                                ymax = high,
                                fill = question,
                                shape = question),
                  color = "black",
                  size = 0.5,
                  show.legend = TRUE,
                  alpha = 0.8,
                  position = position_dodge(width = 0.5)) +
    facet_wrap(~type,
             labeller = custom_labels) + 
  scale_fill_brewer(palette = "Set1") + 
  scale_color_brewer(palette = "Set1") +
  scale_shape_manual(values = c(21, 23)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                      labels = str_c(seq(0, 1, 0.25) * 100, "%")) +
  scale_x_continuous(breaks = 4:10,
                     labels = c("4", "5", "6", "7", "8", "9", "Adults")) +
  labs(y = "Probability of selecting \n causal candidate") +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        text = element_text(size = 18)) +
  guides(color = guide_legend(reverse = TRUE),
         fill = guide_legend(reverse = TRUE),
         shape = guide_legend(reverse = TRUE))

  
```

#### Made

```{r message=FALSE, warning=FALSE}

df.model = df.exp2_made_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "made"))


fit.brm.present.made.age2 = brm(formula = direct ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 8000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999,
                                    max_treedepth = 15),
                     file = "cache/fit.brm.present.made.age2") 



fit.brm.absence.made.age2 = brm(formula = absence ~ 1 + question*age + (1 | participant) + (1 | scenario),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 6000,
                      control = list(adapt_delta = .999999,
                                     max_treedepth = 15),
                      file = "cache/fit.brm.absence.made.age2") 



df.data = expand_grid(age = seq(4, 9, 0.1),
                      question = c("made", "lexical"))

df.prediction = fit.brm.present.made.age2 %>% 
  fitted(newdata = df.data,
         re_formula = NA,
          probs = c(0.1, 0.9)) %>% 
  as_tibble() %>% 
  bind_cols(df.data) %>% 
  mutate(type = "presence") %>% 
  bind_rows(fit.brm.absence.made.age2 %>% 
              fitted(newdata = df.data,
                     re_formula = NA,
                     probs = c(0.1, 0.9)) %>% 
              as_tibble() %>% 
              bind_cols(df.data) %>% 
              mutate(type = "absence")) %>% 
  clean_names()

df.adults = df.exp2_made_adults %>% 
  select(-response) %>% 
  mutate(age_whole = rep(10)) %>% 
  pivot_longer(cols = (direct:absence),
    names_to = "type",
    values_to = "response")


df.children = df.exp2_made_children %>%
  select(-response) %>% 
  pivot_longer(cols = (direct:absence),
               names_to = "type",
               values_to = "response")

df.means = df.children %>% 
  mutate(age_whole = as.integer(age)) %>%
  bind_rows(df.adults) %>% 
  mutate(age_whole = factor(age_whole, 
                            levels = c(4, 5, 6, 7, 8, 9, 10), 
                            labels = c("4", "5", "6", "7", "8", "9", "adults")),
         type = recode(type, "direct" = "presence")) %>% 
  group_by(age_whole, question, type) %>% 
  summarize(
    response = Hmisc::smean.cl.boot(response)) %>%
    mutate(index = c("response", "low", "high")) %>%
    ungroup() %>% 
    pivot_wider(names_from = index,
                values_from = response) %>% 
  mutate(age_whole = fct_recode(age_whole, "10" = "adults"),
         age_whole = as.numeric(as.character(age_whole)),
         question = factor(question, levels = c("made", "lexical")))


custom_labels = as_labeller(c("absence" = "Absent Cause", "presence" = "Direct Cause"))


p8 = ggplot(mapping = aes(x = age, 
                     y = response,
                     color = question)) + 
  geom_hline(yintercept=0.50, linetype="dashed", color = "black") +
  geom_smooth(data = df.prediction,
              mapping = aes(y = estimate,
                            ymin = q10,
                            ymax = q90,
                            color = question,
                            fill = question),
              stat = "identity",
              alpha = 0.2,
              show.legend = F) +
  geom_pointrange(data = df.means,
                  mapping = aes(x = age_whole,
                                y = response,
                                ymin = low,
                                ymax = high,
                                fill = question,
                                shape = question),
                  color = "black",
                  size = 0.5,
                  show.legend = TRUE,
                  alpha = 0.8,
                  position = position_dodge(width = 0.4)) +
  facet_wrap(~type,
             labeller = custom_labels) + 
  scale_fill_manual(values = c("made" = "#4DAF4A", "lexical" = "#377EB8"), breaks=c("made", "lexical")) +
  scale_color_manual(values = c("made" = "#4DAF4A", "lexical" = "#377EB8"), breaks=c("made", "lexical")) +
  scale_shape_manual(values = c(21, 23), breaks=c("made", "lexical")) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = str_c(seq(0, 1, 0.25) * 100, "%"),
                     limits = c(0, 1)) +
  scale_x_continuous(breaks = 4:10,
                     labels = c("4", "5", "6", "7", "8", "9", "Adults")) +
  labs(y = "Probability of selecting \n causal candidate") +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        text = element_text(size = 18)) 


```

#### Combine Cause and Made Plots

```{r fig.height=5, fig.width=18, message=FALSE, warning=FALSE}

plot = p7 + p8 + 
plot_layout(nrow = 1) &
plot_annotation(tag_levels = "A") &
theme(plot.tag = element_text(face = "bold"))

ggsave(plot, filename = "../../figures/experiment2/absence_all.pdf", height = 5, width = 18)

plot


```

### Order Effects
#### First Scenario

```{r fig.height=4, fig.width=9.5, message=FALSE, warning=FALSE}

df.plot = df.exp2_cause_children_order %>% 
  rename(periphrastic_question_order = caused_question_order) %>% 
  select(question, direct, absence, periphrastic_question_order) %>% 
  mutate(age = rep("children")) %>% 
  bind_rows(df.exp2_made_children_order %>% 
              rename(periphrastic_question_order = made_question_order) %>% 
              select(question, direct, absence, periphrastic_question_order) %>% 
  mutate(age = rep("children")),
            df.exp2_cause_adults_order %>% 
              rename(periphrastic_question_order = caused_question_order) %>% 
              select(question, direct, absence, periphrastic_question_order) %>% 
  mutate(age = rep("adults")),
            df.exp2_made_adults_order %>% 
              rename(periphrastic_question_order = made_question_order) %>% 
    select(question, direct, absence, periphrastic_question_order) %>% 
  mutate(age = rep("adults"))) %>% 
  pivot_longer(cols = direct:absence,
               names_to = "type",
               values_to = "response") %>% 
  mutate(question = str_replace_all(question, "\\bcause\\b", "caused"),
          age = factor(age, levels = c("children", "adults")))

custom_labels = as_labeller(c("direct" = "Direct Cause", "absence" = "Absent Cause"))

ggplot(data = df.plot,
       mapping = aes(x = factor(question, levels = c("caused", "made", "lexical")),
                     y = response,
                     group = interaction(periphrastic_question_order, age),
                     color = periphrastic_question_order,
                     fill = periphrastic_question_order,
                     shape = age)) + 
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  stat_summary(fun.data = "mean_cl_boot",
               position = position_dodge(width = 0.8),
               size = .9,
               color = "black") +  
  scale_fill_brewer(palette = "Set3") +
  scale_color_brewer(palette = "Set3") +
 scale_y_continuous(breaks = seq(0, 1, 0.25),
                      labels = str_c(seq(0, 1, 0.25) * 100, "%"),
                      limits = c(0, 1)) +
  ylab("Probability of selecting \n causal candidate") + 
 scale_shape_manual(values = c(21, 23)) +
  guides(fill = guide_legend(order = 1, override.aes = list(shape = 22, color = NA)),
         color = guide_legend(order = 1, override.aes = list(shape = 22, color = NA)),
         shape = guide_legend(order = 2, override.aes = list(color = "black"))) +
  ylab("Probability of selecting \n causal candidate") +
  theme(legend.position = "bottom",
        legend.box = "vertical",
        axis.title.x = element_blank(),
        text = element_text(size = 18)) +  
  labs(color = "  periphrastic \n\ question order", 
       fill = "   periphrastic \n\ question order",
       shape = "age") +
   facet_wrap(~type,
             labeller = custom_labels) 

ggsave("../../figures/experiment2/absent_order_effect_first_scenario.pdf", height = 4, width = 9.5)


```

#### Second Scenario

```{r fig.height=4, fig.width=9.5, message=FALSE, warning=FALSE}

df.exp2_cause_children_order_second = df.exp2_cause_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "lexical"),
         caused_question_order = as_factor(cause_question_order),
         caused_question_order = fct_relevel(caused_question_order, "first")) %>% 
   group_by(participant) %>%
   filter(row_number() %in% 3:4) %>%
  ungroup()



df.exp2_made_children_order_second = df.exp2_made_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "lexical"),
         made_question_order = str_replace_all(made_question_order, "frst", "first"),
         made_question_order = str_replace_all(made_question_order, "scond", "second"),
         made_question_order = as_factor(made_question_order),
         made_question_order = fct_relevel(made_question_order, "first")) %>% 
   group_by(participant) %>%
   filter(row_number() %in% 3:4) %>%
  ungroup()

# code order
df.tmp = df.exp2_cause_adults %>% 
  group_by(participant) %>% 
  filter(row_number() == 1) %>% 
  mutate(scenario_order = str_c(scenario, "_first"),
         question_order = str_c(question, "_first")) %>% 
  select(participant,
         contains("order"))

df.exp2_cause_adults_order_second = df.exp2_cause_adults %>% 
  left_join(df.tmp,
            by = "participant") %>% 
  relocate(contains("order"), .after = question) %>% 
  mutate(caused_question_order = case_when(question_order == "lexical_first" ~ "second",
                                          question_order == "cause_first" ~ "first"),
         question = as_factor(question),
         question = fct_relevel(question, "lexical"),
         caused_question_order = as_factor(caused_question_order),
         caused_question_order = fct_relevel(caused_question_order, "first")) %>% 
   group_by(participant) %>%
   filter(row_number() %in% 3:4) %>%
  ungroup()


# code order
df.tmp = df.exp2_made_adults %>% 
  group_by(participant) %>% 
  filter(row_number() == 1) %>% 
  mutate(scenario_order = str_c(scenario, "_first"),
         question_order = str_c(question, "_first")) %>% 
  select(participant,
         contains("order"))

df.exp2_made_adults_order_second = df.exp2_made_adults %>% 
  left_join(df.tmp,
            by = "participant") %>% 
  relocate(contains("order"), .after = question) %>% 
  mutate(made_question_order = case_when(question_order == "lexical_first" ~ "second",
                                          question_order == "made_first" ~ "first"),
         question = as_factor(question),
         question = fct_relevel(question, "lexical"),
         made_question_order = as_factor(made_question_order),
         made_question_order = fct_relevel(made_question_order, "first")) %>% 
   group_by(participant) %>%
   filter(row_number() %in% 3:4) %>%
  ungroup()



df.plot = df.exp2_cause_children_order_second %>% 
  rename(periphrastic_question_order = caused_question_order) %>% 
  select(question, direct, absence, periphrastic_question_order) %>% 
  mutate(age = rep("children")) %>% 
  bind_rows(df.exp2_made_children_order_second %>% 
              rename(periphrastic_question_order = made_question_order) %>% 
              select(question, direct, absence, periphrastic_question_order) %>% 
  mutate(age = rep("children")),
            df.exp2_cause_adults_order_second %>% 
              rename(periphrastic_question_order = caused_question_order) %>% 
              select(question, direct, absence, periphrastic_question_order) %>% 
  mutate(age = rep("adults")),
            df.exp2_made_adults_order_second %>% 
              rename(periphrastic_question_order = made_question_order) %>% 
    select(question, direct, absence, periphrastic_question_order) %>% 
  mutate(age = rep("adults"))) %>% 
  pivot_longer(cols = direct:absence,
               names_to = "type",
               values_to = "response") %>% 
  mutate(question = str_replace_all(question, "\\bcause\\b", "caused"),
         age = factor(age, levels = c("children", "adults")))
  

custom_labels = as_labeller(c("direct" = "Direct Cause", "absence" = "Absent Cause"))

ggplot(data = df.plot,
       mapping = aes(x = factor(question, levels = c("caused", "made", "lexical")),
                     y = response,
                     group = interaction(periphrastic_question_order, age),
                     color = periphrastic_question_order,
                     fill = periphrastic_question_order,
                     shape = age)) + 
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  stat_summary(fun.data = "mean_cl_boot",
               position = position_dodge(width = 0.8),
               size = .9,
               color = "black") +  
  scale_fill_brewer(palette = "Set3") +
  scale_color_brewer(palette = "Set3") +
 scale_y_continuous(breaks = seq(0, 1, 0.25),
                      labels = str_c(seq(0, 1, 0.25) * 100, "%"),
                      limits = c(0, 1)) +
  ylab("Probability of selecting \n causal candidate") + 
 scale_shape_manual(values = c(21, 23)) +
  guides(fill = guide_legend(order = 1, override.aes = list(shape = 22, color = NA)),
         color = guide_legend(order = 1, override.aes = list(shape = 22, color = NA)),
         shape = guide_legend(order = 2, override.aes = list(color = "black"))) +
  ylab("Probability of selecting \n causal candidate") +
  theme(legend.position = "bottom",
        legend.box = "vertical",
        axis.title.x = element_blank(),
        text = element_text(size = 18)) +  
  labs(color = "  periphrastic \n\ question order", 
       fill = "   periphrastic \n\ question order",
       shape = "age") +
   facet_wrap(~type,
             labeller = custom_labels) 

ggsave("../../figures/experiment2/absent_order_effect_second_scenario.pdf", height = 4, width = 9.5)


```


# SESSION INFO
```{r}

sessionInfo()

```
