---
title: "Cause and Burn in Development"
author: "David Rose, Siying Zhang, Shaun Nichols, Ellen Markman & Tobias Gerstenberg"
date: "`r Sys.Date()`"
output:
  bookdown::html_document2:
    toc: true
    toc_depth: 6
    theme: cosmo
    highlight: tango
---

# Load packages
```{r eval=TRUE, include=FALSE, message=FALSE, warning=FALSE}

library("janitor")         # for cleaning variable names
library("emmeans")         # for comparing means
library("brms")            # for Bayesian data analysis
library("patchwork")       # for combining figures
library("knitr")           # for knitting 
library("marginaleffects") # for marginal effects
library("ggtext")          # for adding text to figures
library("tidyverse")       # for everything else

```

# Settings

```{r message=FALSE, warning=FALSE}

# set theme 
theme_set(theme_classic())

# sum coding
options(contrasts = c("contr.sum","contr.poly"))

# suppress grouping warning 
options(dplyr.summarise.inform = F)
```

# EXPERIMENT 1: CHAINS
## CAUSE V LEXICAL (BREAK & CRACK)
### ADULTS
#### DATA
##### Read in data
```{r message=FALSE, warning=FALSE}

df.exp1_cause_adults = read_csv("../../data/experiment1/cause/adults/exp1_cause_adults.csv")

```

##### Wrangle 

```{r message=FALSE, warning=FALSE}

df.exp1_cause_adults = df.exp1_cause_adults %>% 
  mutate(participant = 1:n()) %>% 
  select(participant, break_cause_processed, break_simple_processed, crack_cause_processed, crack_simple_processed, counterbalance) %>% 
  pivot_longer(-c(participant,counterbalance),
               names_to = "tmp_name",
               values_to = "response") %>% 
  separate(.,
           col = tmp_name,
           into = c("verb", "question", "tmp"),
           sep = "_") %>% 
  select(-tmp) %>% 
  mutate(distal = ifelse(counterbalance == "order_1" & str_detect(response,
                                                                  "Andy|Sophia"), 1, 0),
         distal = ifelse(counterbalance == "order_2" & str_detect(response,
                                                                  "Suzy|Bobby"), 1, distal),
         proximal = ifelse(counterbalance == "order_1" & str_detect(response,
                                                                    "Suzy|Bobby"), 1, 0),
         proximal = ifelse(counterbalance == "order_2" & str_detect(response,
                                                                    "Andy|Sophia"), 1, proximal), 
         question = str_replace_all(question, "simple", "lexical"),
         question = str_replace_all(question, "cause", "caused")) %>% 
  rename(scenario = verb)

```

##### Demographics

```{r message=FALSE, warning=FALSE}

df.exp1_cause_adults_demo = read_csv("../../data/experiment1/cause/adults/exp1_cause_adults_demo.csv")

df.exp1_cause_adults_demo  %>% 
  summarise(age_mean = mean(as.numeric(age), na.rm = TRUE))

df.exp1_cause_adults_demo  %>% 
  summarise(age_sd = sd(as.numeric(age), na.rm = TRUE))

df.exp1_cause_adults_demo  %>% 
  group_by(gender) %>% 
  count() 

df.exp1_cause_adults_demo  %>% 
  group_by(race) %>% 
  count() 

```


#### STATS

##### Bayesian Model

```{r message=FALSE, warning=FALSE}

df.cause_adults_different = df.exp1_cause_adults %>%
  mutate(response_pattern = case_when(
    distal == 1 & proximal == 1 ~ "both",
    distal == 0 & proximal == 0 ~ "neither",
    TRUE ~ "different"
  )) %>%
  filter(response_pattern == "different") %>%
  mutate(difference = distal - proximal,
        difference = recode(difference, `-1` = 0))

df.cause_adults_both = df.exp1_cause_adults %>%
  mutate(response_pattern = case_when(
    distal == 1 & proximal == 1 ~ "both",
    distal == 0 & proximal == 0 ~ "neither",
    TRUE ~ "different"
  )) %>%
  filter(response_pattern == "both")
  
  
df.cause_adults_both = df.cause_adults_both %>% 
  mutate(difference = 1) %>%
  bind_rows(df.cause_adults_both %>% 
              mutate(difference = 0)) 

df.chain_cause_adults = df.cause_adults_different %>% 
  bind_rows(df.cause_adults_both)


df.model = df.chain_cause_adults %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "caused"))

# Check contrast values
 contrasts(df.model$question)


fit.brm.chain.cause.adults = brm(formula = difference ~ 1 + question + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     file = "cache/chain_cause_adult_difference") 

fit.brm.chain.cause.adults
```

##### Follow-up analysis 

```{r}
fit.brm.chain.cause.adults %>% 
  emmeans(spec = pairwise ~ question, 
          type = "response")

```



### CHILDREN

#### DATA

##### Read in data

```{r message=FALSE, warning=FALSE}
df.exp1_cause_children = read_csv("../../data/experiment1/cause/children/exp1_cause_children.csv")
```

##### Wrangle
```{r message=FALSE, warning=FALSE}
#clean data
df.exp1_cause_children = df.exp1_cause_children %>% 
  clean_names() %>% 
  rename(question = question_type) %>% 
  mutate(response = str_remove_all(string = response,
                                   pattern = "\""),
         response = str_remove_all(string = response,
                                   pattern = ":"),
         response = str_remove_all(string = response,
                                   pattern = "\\}"),
         response = str_remove_all(string = response,
                                   pattern = "\\."),
         response = str_remove_all(string = response,
                                   pattern = "\\,"),
         response = str_remove_all(string = response,
                                   pattern = "\\\\n"),
         response = str_to_lower(response)) %>% 
  select(-(response_id : age_range), -notes, -full_response) 


# code responses
df.exp1_cause_children = df.exp1_cause_children %>% 
  mutate(distal = ifelse(counterbalance == "andy" & str_detect(response, "andy"), 1, 0),
         distal = ifelse(counterbalance == "suzy" & str_detect(response, "suzy"), 1, distal),
         distal = ifelse(counterbalance == "bobby" & str_detect(response, "bobby"), 1, distal),
         distal = ifelse(counterbalance == "sophia" & str_detect(response, "sophia"), 1, distal),
         proximal = ifelse(counterbalance == "andy" & str_detect(response, "suzy"), 1, 0),
         proximal = ifelse(counterbalance == "suzy" & str_detect(response, "andy"), 1, proximal),
         proximal = ifelse(counterbalance == "bobby" & str_detect(response, "sophia"), 1, proximal),
         proximal = ifelse(counterbalance == "sophia" & str_detect(response, "bobby"), 1, proximal),
         age = round(rounded_age / 365, digits = 2),
         question = str_replace_all(question, "break|crack", "simple")) 

# compute age and replace simple with lexical
df.exp1_cause_children = df.exp1_cause_children %>% 
  mutate(age_whole = as.integer(age)) %>%
  mutate(age_character = as.character(age_whole)) %>%
  mutate(age_character = recode(age_character, "7" = "7-9", "8" = "7-9", "9" = "7-9"),
         question = str_replace_all(question, "simple", "lexical")) %>%
  rename(participant = participant_number) 

```

##### Demographics

```{r message=FALSE, warning=FALSE}
# gender
df.exp1_cause_children %>%
  group_by(gender) %>%
  summarise(n = n_distinct(participant)) %>%
  print()

# language spoken
df.exp1_cause_children %>%
    mutate(en_occurrence = ifelse(str_detect(lan_spoken, "en"), "en", "non-en")) %>%
    group_by(en_occurrence) %>%
    summarise(n = n_distinct(participant)) %>%
    print()
```

#### STATS

##### Bayesian Model
```{r message=FALSE, warning=FALSE}
df.cause_children_different = df.exp1_cause_children %>%
  mutate(response_pattern = case_when(
    distal == 1 & proximal == 1 ~ "both",
    distal == 0 & proximal == 0 ~ "neither",
    TRUE ~ "different"
  )) %>%
  filter(response_pattern == "different") %>%
  mutate(difference = distal - proximal,
        difference = recode(difference, `-1` = 0))

df.cause_children_both = df.exp1_cause_children %>%
  mutate(response_pattern = case_when(
    distal == 1 & proximal == 1 ~ "both",
    distal == 0 & proximal == 0 ~ "neither",
    TRUE ~ "different"
  )) %>%
  filter(response_pattern == "both") 


 df.cause_children_both = df.cause_children_both %>% 
  mutate(difference = 1) %>%
  bind_rows(df.cause_children_both %>% 
              mutate(difference = 0)) 

df.chain_cause_children = df.cause_children_different %>% 
  bind_rows(df.cause_children_both) 
  
df.model = df.chain_cause_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "caused"))

fit.brm.chain.cause.children = brm(formula = difference ~ 1 + question * age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     file = "cache/chain_cause_children_difference") 

fit.brm.chain.cause.children 
```

##### Follow-up analysis 

```{r}
# effect of question 
fit.brm.chain.cause.children %>% 
  emmeans(spec = pairwise ~ question, 
          type = "response")

# effect of age 
fit.brm.chain.cause.children %>% 
  avg_slopes(variable = "age",
             type = "link")
  
# interaction effect 
fit.brm.chain.cause.children %>% 
  emtrends(specs = pairwise ~ question,
           var = "age")
```


## MADE v LEXICAL (BREAK & CRACK)
### ADULTS
#### DATA
##### Read in data

```{r message=FALSE, warning=FALSE}

df.exp1_made_adults = read_csv("../../data/experiment1/made/adults/exp1_made_adults.csv")

```

##### Wrangle

```{r message=FALSE, warning=FALSE}

df.exp1_made_adults = df.exp1_made_adults %>% 
  mutate(participant = 1:n()) %>% 
  select(participant, break_cause_processed, break_simple_processed, crack_cause_processed, crack_simple_processed, counterbalance) %>% 
  pivot_longer(-c(participant,counterbalance),
               names_to = "tmp_name",
               values_to = "response") %>% 
  separate(.,
           col = tmp_name,
           into = c("verb", "question", "tmp"),
           sep = "_") %>% 
  select(-tmp) %>% 
  mutate(distal = ifelse(counterbalance == "order_1" & str_detect(response,
                                    "Andy|Sophia"), 1, 0),
         distal = ifelse(counterbalance == "order_2" & str_detect(response,
                                    "Suzy|Bobby"), 1, distal),
         proximal = ifelse(counterbalance == "order_1" & str_detect(response,
                                    "Suzy|Bobby"), 1, 0),
         proximal = ifelse(counterbalance == "order_2" & str_detect(response,
                                    "Andy|Sophia"), 1, proximal),
         question = str_replace_all(question, "cause", "made"),
         question = str_replace_all(question, "simple", "lexical")) %>% 
  rename(scenario = verb)

```

##### Demographics

```{r message=FALSE, warning=FALSE}

df.exp1_made_adults_demo = read_csv("../../data/experiment1/made/adults/exp1_made_adults_demo.csv")

df.exp1_made_adults_demo %>% 
  summarise(age_mean = mean(as.numeric(age), na.rm = TRUE))

df.exp1_made_adults_demo %>% 
  summarise(age_sd = sd(as.numeric(age), na.rm = TRUE))

df.exp1_made_adults_demo %>% 
  group_by(gender) %>% 
  count() 

df.exp1_made_adults_demo %>% 
  group_by(race) %>% 
  count() 

```

#### STATS



##### Bayesian Model

```{r message=FALSE, warning=FALSE}


df.made_adults_different = df.exp1_made_adults %>%
  mutate(response_pattern = case_when(
    distal == 1 & proximal == 1 ~ "both",
    distal == 0 & proximal == 0 ~ "neither",
    TRUE ~ "different"
  )) %>%
  filter(response_pattern == "different") %>%
  mutate(difference = distal - proximal,
        difference = recode(difference, `-1` = 0))

df.made_adults_both = df.exp1_made_adults %>%
  mutate(response_pattern = case_when(
    distal == 1 & proximal == 1 ~ "both",
    distal == 0 & proximal == 0 ~ "neither",
    TRUE ~ "different"
  )) %>%
  filter(response_pattern == "both")


df.made_adults_both = df.made_adults_both %>% 
  mutate(difference = 1) %>%
  bind_rows(df.made_adults_both %>% 
              mutate(difference = 0)) 

df.chain_made_adults = df.made_adults_different %>% 
  bind_rows(df.made_adults_both) 

df.model = df.chain_made_adults %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "made"))

# Check contrast values
 contrasts(df.model$question)


fit.brm.chain.made.adults = brm(formula = difference ~ 1 + question + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     file = "cache/chain_made_adult_difference") 

fit.brm.chain.made.adults


```

##### Follow-up analysis 

```{r}
fit.brm.chain.made.adults %>% 
  emmeans(spec = pairwise ~ question, 
          type = "response")

```

### CHILDREN
#### DATA
##### Read in data

```{r message=FALSE, warning=FALSE}

df.exp1_made_children = read_csv("../../data/experiment1/made/children/exp1_made_children.csv")

```

##### Wrangle

```{r message=FALSE, warning=FALSE}

#clean data
df.exp1_made_children = df.exp1_made_children %>% 
  clean_names() %>% 
  rename(
         question = question_type) %>% 
  mutate(response = str_to_lower(response),
         counterbalance = str_to_lower(counterbalance)) %>% 
  select(-(response_id : age_range), -notes, -full_response) 

#code responses
df.exp1_made_children = df.exp1_made_children %>% 
  mutate(distal = ifelse(counterbalance == "andy" & str_detect(response, "andy"), 1, 0),
         distal = ifelse(counterbalance == "suzy" & str_detect(response, "suzy"), 1, distal),
         distal = ifelse(counterbalance == "bobby" & str_detect(response, "bobby"), 1, distal),
         distal = ifelse(counterbalance == "sophia" & str_detect(response, "sophia"), 1, distal),
         proximal = ifelse(counterbalance == "andy" & str_detect(response, "suzy"), 1, 0),
         proximal = ifelse(counterbalance == "suzy" & str_detect(response, "andy"), 1, proximal),
         proximal = ifelse(counterbalance == "bobby" & str_detect(response, "sophia"), 1, proximal),
         proximal = ifelse(counterbalance == "sophia" & str_detect(response, "bobby"), 1, proximal),
         age = round(rounded_age / 365, digits = 2),
         question = str_replace_all(question, "break|crack", "simple")) 

# compute age and recode question
df.exp1_made_children = df.exp1_made_children %>% 
  mutate(age_whole =as.integer(age)) %>%
  mutate(age_character = as.character(age_whole)) %>%
  mutate(age_character = recode(age_character, "7" = "7-9", "8" = "7-9", "9" = "7-9"),
         question = str_replace_all(question, "simple", "lexical"),
         scenario = str_replace_all(scenario, "mirror_break", "mirror_crack")) %>%
  rename(participant = participant_number) 


```

##### Demographics
```{r message=FALSE, warning=FALSE}

 # gender
df.exp1_made_children %>%
  group_by(gender) %>%
  summarise(n = n_distinct(participant)) %>%
  print()
  
  
  # language spoken
df.exp1_made_children %>%
    mutate(en_occurrence = ifelse(str_detect(lan_spoken, "en"), "en", "non-en")) %>%
    group_by(en_occurrence) %>%
    summarise(n = n_distinct(participant)) %>%
    print()

```

#### STATS

##### Bayesian Model
```{r message=FALSE, warning=FALSE}


df.made_children_different = df.exp1_made_children %>%
  mutate(response_pattern = case_when(
    distal == 1 & proximal == 1 ~ "both",
    distal == 0 & proximal == 0 ~ "neither",
    TRUE ~ "different"
  )) %>%
  filter(response_pattern == "different") %>%
  mutate(difference = distal - proximal,
        difference = recode(difference, `-1` = 0))

df.made_children_both = df.exp1_made_children %>%
  mutate(response_pattern = case_when(
    distal == 1 & proximal == 1 ~ "both",
    distal == 0 & proximal == 0 ~ "neither",
    TRUE ~ "different"
  )) %>%
  filter(response_pattern == "both")

df.made_children_both = df.made_children_both %>% 
  mutate(difference = 1) %>%
  bind_rows(df.made_children_both %>% 
              mutate(difference = 0)) 

df.chain_made_children = df.made_children_different %>% 
  bind_rows(df.made_children_both) 
  
df.model = df.chain_made_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "made"))


# Check contrast values
 contrasts(df.model$question)
 


fit.brm.chain.made.children = brm(formula = difference ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     file = "cache/chain_made_children_difference") 

fit.brm.chain.made.children


```

##### Follow-up analysis 

```{r}

# effect of question 
fit.brm.chain.made.children %>% 
  emmeans(spec = pairwise ~ question, 
          type = "response")

# effect of age 
fit.brm.chain.made.children %>% 
  avg_slopes(variable = "age",
             type = "link")
  
# interaction effect 
fit.brm.chain.made.children %>% 
  emtrends(specs = pairwise ~ question,
           var = "age")
```

## PLOTS
### Responses Plots
#### Cause v Lexical
```{r message=FALSE, warning=FALSE}


df.data = expand_grid(age = seq(4, 9, 0.1),
                      question = c("caused", "lexical"))

df.prediction = fit.brm.chain.cause.children %>%
  fitted(newdata = df.data,
         re_formula = NA,
          probs = c(0.1, 0.9)) %>%
  as_tibble() %>%
  bind_cols(df.data) %>%
  clean_names()


df.means = df.chain_cause_adults %>% 
  mutate(age_whole = rep(10)) %>% 
  bind_rows(df.chain_cause_children) %>% 
  mutate(age_whole = factor(age_whole,
                            levels = c(4, 5, 6, 7, 8, 9, 10),
                            labels = c("4", "5", "6", "7", "8", "9", "adults"))) %>%
  group_by(age_whole, question) %>%
  summarize(
    response = Hmisc::smean.cl.boot(difference)) %>%
    mutate(index = c("response", "low", "high")) %>%
    ungroup() %>%
    pivot_wider(names_from = index,
                values_from = response) %>%
  mutate(age_whole = fct_recode(age_whole, "10" = "adults"),
         age_whole = as.numeric(as.character(age_whole)))


gradient_segments = data.frame(
  x = rep(min(df.means$age_whole), 100),
  xend = rep(max(df.means$age_whole), 100),
  y = seq(0, 1, length.out = 100),
  yend = seq(0, 1, length.out = 100),
  color = scales::gradient_n_pal(c("#377EB8", "#E41A1C"))(seq(0, 1, length.out = 100))
)

# custom_labels = function(breaks) {
#   counts = df.chain_cause_adults %>% 
#   mutate(age_whole = rep(10)) %>% 
#   bind_rows(df.chain_cause_children) %>% 
#   mutate(age_whole = factor(age_whole,
#                             levels = c(4, 5, 6, 7, 8, 9, 10),
#                             labels = c("4", "5", "6", "7", "8", "9", "Adults"))) %>%
#   group_by(age_whole) %>%
#   summarize(count = n_distinct(participant)) %>%
#     pull(count)
#   labels = c("4", "5", "6", "7", "8", "9", "Adults")
#   paste0(labels, "<br><span style='font-size:10px;'>n=", counts, "</span>")
# }


# custom_labels = function(breaks) {
#   counts = df.chain_cause_adults %>% 
#     mutate(age_whole = rep(10)) %>% 
#     bind_rows(df.chain_cause_children) %>% 
#     mutate(age_whole = factor(age_whole,
#                               levels = c(4, 5, 6, 7, 8, 9, 10),
#                               labels = c("4", "5", "6", "7", "8", "9", "Adults"))) %>%
#     group_by(age_whole) %>%
#     summarize(count = n_distinct(participant)) %>%
#     pull(count)
#   
#   labels = c(paste0("(n=", counts[1], ")<br><span style='font-size:10px;'>n=", counts[1], "</span>"),
#              paste0("(", counts[-1], ")<br><span style='font-size:10px;'>", counts[-1], "</span>"))
#   return(labels)
# }

# custom_labels = function(breaks) {
#   counts = df.chain_cause_adults %>% 
#     mutate(age_whole = rep(10)) %>% 
#     bind_rows(df.chain_cause_children) %>% 
#     mutate(age_whole = factor(age_whole,
#                               levels = c(4, 5, 6, 7, 8, 9, 10),
#                               labels = c("4", "5", "6", "7", "8", "9", "Adults"))) %>%
#     group_by(age_whole) %>%
#     summarize(count = n_distinct(participant)) %>%
#     pull(count)
#   
#   labels = c(paste0("(n=", counts[1], ")<br><span style='font-size:10px;'>n=", counts[1], "</span>"),
#              paste0("<span style='font-size:10px;'>(", counts[-1], ")</span>"))
#   return(labels)
# }

custom_labels = function(breaks) {
  counts = df.chain_cause_adults %>% 
    mutate(age_whole = rep(10)) %>% 
    bind_rows(df.chain_cause_children) %>% 
    mutate(age_whole = factor(age_whole,
                              levels = c(4, 5, 6, 7, 8, 9, 10),
                              labels = c("4", "5", "6", "7", "8", "9", "Adults"))) %>%
    group_by(age_whole) %>%
    summarize(count = n_distinct(participant)) %>%
    pull(count)
  labels = c(paste0("<span style='font-size:10px;'>(n=", counts[1], ")</span>"),
             paste0("<span style='font-size:10px;'>(", counts[-1], ")</span>"))
  return(labels)
}





p1 = ggplot(mapping = aes(x = age,
                     y = difference,
                     color = question)) +
    geom_segment(data = gradient_segments,
               aes(x = 3.8, 
                   xend = 10.2, 
                   y = y, 
                   yend = yend, 
                   color = I(color)),
               size = 1.1,
               alpha = .9) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  geom_smooth(data = df.prediction,
              mapping = aes(y = estimate,
                            ymin = q10,
                            ymax = q90,
                            color = question,
                            fill = question),
              stat = "identity",
              alpha = 0.2,
              show.legend = F) +
  geom_pointrange(data = df.means,
                  mapping = aes(x = age_whole,
                                y = response,
                                ymin = low,
                                ymax = high,
                                shape = question),
                  color = "black",
                  fill = "white",
                  size = 0.5,
                  show.legend = TRUE,
                  alpha = 0.8,
                  position = position_dodge(width = 0.3)) +
  scale_fill_manual(values = c("caused" = "black",
                               "lexical" = "black")) +
  scale_color_manual(values = c("caused" = "black",
                                "lexical" = "black")) +
  scale_shape_manual(values = c("caused" = 21,
                               "lexical" = 23)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = c("100% \n proximal", "75%", "50%", "75%", "100% \n distal"),
                      limits = c(0, 1)) +
 scale_x_continuous(breaks = 4:10,
                    labels = custom_labels(labels),
                    limits = c(3.8, 10.2)) +
  labs(y = "Probability of selecting \n proximal or distal cause") +
  theme(legend.position = "none",
        legend.title = element_blank(),
        text = element_text(size = 18),
        axis.text.x = element_markdown(),
        axis.title.x = element_blank()) +
  facet_wrap(~factor(question,
             levels = c("lexical", "caused"))) 

p1

lexcial = "#4DAF4A", caused = "#FF7F00", made = "#FFFF33"
 

```


#### Made v Lexical
```{r message=FALSE, warning=FALSE}

df.data = expand_grid(age = seq(4, 9, 0.1),
                      question = c("made", "lexical"))

df.prediction = fit.brm.chain.made.children %>%
  fitted(newdata = df.data,
         re_formula = NA,
          probs = c(0.1, 0.9)) %>%
  as_tibble() %>%
  bind_cols(df.data) %>%
  clean_names()


df.means = df.chain_made_adults %>% 
  mutate(age_whole = rep(10)) %>% 
  bind_rows(df.chain_made_children) %>% 
  mutate(age_whole = factor(age_whole,
                            levels = c(4, 5, 6, 7, 8, 9, 10),
                            labels = c("4", "5", "6", "7", "8", "9", "adults"))) %>%
  group_by(age_whole, question) %>%
  summarize(
    response = Hmisc::smean.cl.boot(difference)) %>%
    mutate(index = c("response", "low", "high")) %>%
    ungroup() %>%
    pivot_wider(names_from = index,
                values_from = response) %>%
  mutate(age_whole = fct_recode(age_whole, "10" = "adults"),
         age_whole = as.numeric(as.character(age_whole)))


gradient_segments = data.frame(
  x = rep(min(df.means$age_whole), 100),
  xend = rep(max(df.means$age_whole), 100),
  y = seq(0, 1, length.out = 100),
  yend = seq(0, 1, length.out = 100),
  color = scales::gradient_n_pal(c("#377EB8", "#E41A1C"))(seq(0, 1, length.out = 100))
)

# custom_labels = function(breaks) {
#   counts = df.chain_made_adults %>% 
#   mutate(age_whole = rep(10)) %>% 
#   bind_rows(df.chain_made_children) %>% 
#   mutate(age_whole = factor(age_whole,
#                             levels = c(4, 5, 6, 7, 8, 9, 10),
#                             labels = c("4", "5", "6", "7", "8", "9", "Adults"))) %>%
#   group_by(age_whole) %>%
#   summarize(count = n_distinct(participant)) %>%
#     pull(count)
#   labels = c("4", "5", "6", "7", "8", "9", "Adults")
#   paste0(labels, "<br><span style='font-size:10px;'>n=", counts, "</span>")
# }


custom_labels = function(breaks) {
  counts = df.chain_made_adults %>% 
    mutate(age_whole = rep(10)) %>% 
    bind_rows(df.chain_made_children) %>% 
    mutate(age_whole = factor(age_whole,
                              levels = c(4, 5, 6, 7, 8, 9, 10),
                              labels = c("4", "5", "6", "7", "8", "9", "Adults"))) %>%
    group_by(age_whole) %>%
    summarize(count = n_distinct(participant)) %>%
    pull(count)
  labels = c(paste0("<span style='font-size:10px;'>(n=", counts[1], ")</span>"),
             paste0("<span style='font-size:10px;'>(", counts[-1], ")</span>"))
  return(labels)
}




p2 = ggplot(mapping = aes(x = age,
                     y = difference,
                     color = question)) +
    geom_segment(data = gradient_segments,
               aes(x = 3.8, 
                   xend = 10.2, 
                   y = y, 
                   yend = yend, 
                   color = I(color)),
               size = 1.1,
               alpha = .9) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  geom_smooth(data = df.prediction,
              mapping = aes(y = estimate,
                            ymin = q10,
                            ymax = q90,
                            color = question,
                            fill = question),
              stat = "identity",
              alpha = 0.2,
              show.legend = F) +
  geom_pointrange(data = df.means,
                  mapping = aes(x = age_whole,
                                y = response,
                                ymin = low,
                                ymax = high,
                                shape = question),
                  color = "black",
                  fill = "white",
                  size = 0.5,
                  show.legend = TRUE,
                  alpha = 0.8,
                  position = position_dodge(width = 0.3)) +
  scale_fill_manual(values = c("made" = "black",
                               "lexical" = "black")) +
  scale_color_manual(values = c("made" = "black",
                                "lexical" = "black")) +
  scale_shape_manual(values = c("made" = 21,
                               "lexical" = 23)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = c("100% \n proximal", "75%", "50%", "75%", "100% \n distal"),
                      limits = c(0, 1)) +
 scale_x_continuous(breaks = 4:10,
                    labels = custom_labels(labels),
                    limits = c(3.8, 10.2)) +
  labs(y = "Probability of selecting \n proximal or distal cause") +
  theme(legend.position = "none",
        legend.title = element_blank(),
        text = element_text(size = 18),
        axis.text.x = element_markdown(),
        axis.title.x = element_blank()) +
  facet_wrap(~factor(question,
             levels = c("lexical", "made"))) 

p2 


question == "lexical" = "#4DAF4A",  "made" ~ "#FFFF33"
                                                         

display.brewer.pal(n = 8, name = 'Set1')
 
brewer.pal(n = 8, name = 'Set1')

lexcial = "#4DAF4A", caused = "#FF7F00", made = "#FFFF33"

```

### Responses Patterns by Age
##### Cause v Lexical
```{r}

df.plot = df.exp1_cause_adults %>% 
  mutate(age_whole = 10) %>% 
  bind_rows(df.exp1_cause_children) %>% 
  mutate(response_pattern = case_when(
    distal == 1 & proximal == 1 ~ "both",
    distal == 0 & proximal == 0 ~ "neither",
    distal == 1 & proximal == 0  ~ "distal only",
    distal == 0 & proximal == 1  ~ "proximal only",
  ),
  question = recode(question, "cause" = "caused"),
  age_whole = as.factor(age_whole)) %>% 
  group_by(age_whole, question, response_pattern) %>% 
  summarize(n = n()) %>% 
  ungroup() %>%
  group_by(age_whole, question) %>%
  mutate(percentage = n / sum(n) * 100) %>%
  ungroup() %>% 
  mutate(question = factor(question, levels = c("lexical", "caused")),
         response_pattern = factor(response_pattern, levels = c("distal only", "proximal only", "both", "neither")))

# custom_labels = function(breaks) {
#   counts = df.exp1_cause_adults %>%
#   mutate(age_whole = rep(10)) %>%
#   bind_rows(df.exp1_cause_children) %>%
#   mutate(age_whole = factor(age_whole,
#                             levels = c(4, 5, 6, 7, 8, 9, 10),
#                             labels = c("4", "5", "6", "7", "8", "9", "Adults"))) %>%
#   group_by(age_whole) %>%
#   summarize(count = n_distinct(participant)) %>%
#     pull(count)
#   labels = c("4", "5", "6", "7", "8", "9", "Adults")
#   paste0(labels, "<br><span style='font-size:10px;'>n=", counts, "</span>")
# }




custom_labels = function(breaks) {
  counts = df.exp1_cause_adults %>%
    mutate(age_whole = 10) %>%
    bind_rows(df.exp1_cause_children) %>%
    mutate(age_whole = factor(age_whole,
                              levels = c(4, 5, 6, 7, 8, 9, 10),
                              labels = c("4", "5", "6", "7", "8", "9", "Adults"))) %>%
    group_by(age_whole) %>%
    summarize(count = n_distinct(participant)) %>%
    pull(count)
  
  labels = c("4", "5", "6", "7", "8", "9", "Adults")
  counts_label1 = paste0("<span style='font-size:10px;'>(n=", counts[1], ")</span>")
  counts_label2 = paste0("<span style='font-size:10px;'>(", counts[-1], ")</span>")
  
  combined_labels = c(paste0(labels[1], "<br>", counts_label1), 
                       paste0(labels[-1], "<br>", counts_label2))
  return(combined_labels)
}




p3 = ggplot(data = df.plot,
       mapping = aes(x = age_whole,
                     y = percentage,
                     group = response_pattern,
                     color = response_pattern,
                     fill = response_pattern)) +
  geom_col(color = "black") +
 scale_fill_manual(values = c("distal only" = "#E41A1C",
                               "proximal only" = "#377EB8",
                               "both" = "#984EA3",
                               "neither" = "#999999")) +
  scale_color_manual(values = c("distal only" = "#E41A1C",
                                "proximal only" = "#377EB8",
                                "both" = "#984EA3",
                                "neither" = "#999999")) +
  scale_shape_manual(values = c(21, 23)) +
  scale_y_continuous(breaks = seq(0, 100, 25),
                     labels = str_c(seq(0, 100, 25), "%")) +
  scale_x_discrete(breaks = 4:10,
                  labels = custom_labels(labels)) +
  labs(y = "Response pattern \n\ probability") +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        text = element_text(size = 18),
        axis.text.x = element_markdown(),
        axis.title.x = element_blank(),
        strip.background = element_blank(),
        strip.text = element_blank()) +
  facet_wrap(~question)

p3

```

##### Made v Lexical
```{r}

df.plot = df.exp1_made_adults %>% 
  mutate(age_whole = 10) %>% 
  bind_rows(df.exp1_made_children) %>% 
  mutate(response_pattern = case_when(
    distal == 1 & proximal == 1 ~ "both",
    distal == 0 & proximal == 0 ~ "neither",
    distal == 1 & proximal == 0  ~ "distal only",
    distal == 0 & proximal == 1  ~ "proximal only",
  ),
  age_whole = as.factor(age_whole)) %>% 
  group_by(age_whole, question, response_pattern) %>% 
  summarize(n = n()) %>% 
  ungroup() %>%
  group_by(age_whole, question) %>%
  mutate(percentage = n / sum(n) * 100) %>%
  ungroup() %>% 
  mutate(question = factor(question, levels = c("lexical", "made")),
         response_pattern = factor(response_pattern, levels = c("distal only", "proximal only", "both", "neither")))

# custom_labels = function(breaks) {
#   counts = df.exp1_made_adults %>% 
#   mutate(age_whole = rep(10)) %>% 
#   bind_rows(df.exp1_made_children) %>% 
#   mutate(age_whole = factor(age_whole,
#                             levels = c(4, 5, 6, 7, 8, 9, 10),
#                             labels = c("4", "5", "6", "7", "8", "9", "Adults"))) %>%
#   group_by(age_whole) %>%
#   summarize(count = n_distinct(participant)) %>%
#     pull(count)
#   labels = c("4", "5", "6", "7", "8", "9", "Adults")
#   paste0(labels, "<br><span style='font-size:10px;'>n=", counts, "</span>")
# }

custom_labels = function(breaks) {
  counts = df.exp1_made_adults %>%
    mutate(age_whole = 10) %>%
    bind_rows(df.exp1_made_children) %>%
    mutate(age_whole = factor(age_whole,
                              levels = c(4, 5, 6, 7, 8, 9, 10),
                              labels = c("4", "5", "6", "7", "8", "9", "Adults"))) %>%
    group_by(age_whole) %>%
    summarize(count = n_distinct(participant)) %>%
    pull(count)
  
  labels = c("4", "5", "6", "7", "8", "9", "Adults")
  counts_label1 = paste0("<span style='font-size:10px;'>(n=", counts[1], ")</span>")
  counts_label2 = paste0("<span style='font-size:10px;'>(", counts[-1], ")</span>")
  
  combined_labels = c(paste0(labels[1], "<br>", counts_label1), 
                       paste0(labels[-1], "<br>", counts_label2))
  return(combined_labels)
}


p4 = ggplot(data = df.plot,
       mapping = aes(x = age_whole,
                     y = percentage,
                     group = response_pattern,
                     color = response_pattern,
                     fill = response_pattern)) +
  geom_col(color = "black") +
  scale_fill_manual(values = c("distal only" = "#E41A1C",
                               "proximal only" = "#377EB8",
                               "both" = "#984EA3",
                               "neither" = "#999999")) +
  scale_color_manual(values = c("distal only" = "#E41A1C",
                                "proximal only" = "#377EB8",
                                "both" = "#984EA3",
                                "neither" = "#999999")) +
  scale_shape_manual(values = c(21, 23)) +
  scale_y_continuous(breaks = seq(0, 100, 25),
                     labels = str_c(seq(0, 100, 25), "%")) +
  scale_x_discrete(breaks = 4:10,
                    labels = custom_labels(labels)) +
  labs(y = "Response pattern \n\ probability") +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        text = element_text(size = 18),
        axis.text.x = element_markdown(),
        axis.title.x = element_blank(),
        strip.background = element_blank(),
        strip.text = element_blank()) +
  facet_wrap(~question)

p4


```
### Combine Cause and Made Plots
```{r fig.height=5, fig.width=18, message=FALSE, warning=FALSE}

plot = p1 + p2 + p3 + p4 +
plot_layout(nrow = 2) &
plot_annotation(tag_levels = "A") &
theme(plot.tag = element_text(face = "bold"))

ggsave(plot, filename = "../../figures/experiment1/chain_response_patterns_age.pdf", height = 8, width = 16)

plot


```



# EXPERIMENT 2: ABSENCES
## CAUSE V LEXICAL (BURN & FLOOD)
### ADULTS
#### DATA
##### Read in data

```{r message=FALSE, warning=FALSE}

df.exp2_cause_adults = read_csv("../../data/experiment2/cause/adults/exp2_cause_adults.csv")

```

##### Wrangle
```{r message=FALSE, warning=FALSE}

# clean data
df.exp2_cause_adults = df.exp2_cause_adults %>% 
  mutate(condition = str_extract(string = responses,
                                 pattern = "sunburn_simple_response|sunburn_cause_response|flood_simple_response|flood_cause_response"),
         response = str_extract(string = responses, 
                                pattern = ":(.*)"),
         response = str_remove_all(string = response,
                                   pattern = "\""),
         response = str_remove_all(string = response,
                                   pattern = ":"),
         response = str_remove_all(string = response,
                                   pattern = "\\}"),
         response = str_remove_all(string = response,
                                   pattern = "\\."),
         response = str_remove_all(string = response,
                                   pattern = "\\,"),
         response = str_remove_all(string = response,
                                   pattern = "\\\\n"),
         response = str_to_lower(response)) %>% 
  separate(condition, c("scenario", "question", "extra"), "_") %>% 
  rename(participant = workerid) %>% 
  select(participant, scenario, question, response)

# code responses
df.exp2_cause_adults = df.exp2_cause_adults %>%
  mutate(direct = ifelse(str_detect(response,
                                    "^sun$|sun | sun$"), 1, 0),
         direct = ifelse(str_detect(response,
                                    "^water$|water | water$"), 1, direct),
         direct = ifelse(str_detect(response,
                                    "^rain$|rain | rain$"), 1, direct),
         absence = ifelse(str_detect(response,
                                     "^sunscreen$|sunscreen | sunscreen$"), 1, 0),
         absence = ifelse(str_detect(response,
                                     "^window$|window | window$"), 1, absence),
         absence = ifelse(str_detect(response,
                                     "^latch$|latch | latch$"), 1, absence))

## replace simple with lexical
df.exp2_cause_adults = df.exp2_cause_adults %>% 
  mutate(question = str_replace_all(question, "simple", "lexical"),
         question = str_replace_all(question, "cause", "caused"))


```

##### Demographics

```{r message=FALSE, warning=FALSE}

df.exp2_cause_adults_demo = read_csv("../../data/experiment2/cause/adults/exp2_cause_adults_demo.csv")

df.exp2_cause_adults_demo %>% 
  summarise(age_mean = mean(as.numeric(age), na.rm = TRUE))

df.exp2_cause_adults_demo %>% 
  summarise(age_sd = sd(as.numeric(age), na.rm = TRUE))

df.exp2_cause_adults_demo %>% 
  group_by(gender) %>% 
  count() 

df.exp2_cause_adults_demo %>% 
  group_by(race) %>% 
  count() 

df.exp2_cause_adults_demo %>% 
  group_by(ethnicity) %>% 
  count() 

```

#### STATS
##### Bayesian Model

```{r message=FALSE, warning=FALSE}

df.cause_adults_different = df.exp2_cause_adults %>%
  mutate(response_pattern = case_when(
    direct == 1 & absence == 1 ~ "both",
    direct == 0 & absence == 0 ~ "neither",
    TRUE ~ "different"
  )) %>%
  filter(response_pattern == "different") %>%
  mutate(difference = absence - direct,
        difference = recode(difference, `-1` = 0))

df.cause_adults_both = df.exp2_cause_adults %>%
  mutate(response_pattern = case_when(
    direct == 1 & absence == 1 ~ "both",
    direct == 0 & absence == 0 ~ "neither",
    TRUE ~ "different"
  )) %>%
  filter(response_pattern == "both")
  
  
df.cause_adults_both = df.cause_adults_both %>% 
  mutate(difference = 1) %>%
  bind_rows(df.cause_adults_both %>% 
              mutate(difference = 0)) 

df.absence_cause_adults = df.cause_adults_different %>% 
  bind_rows(df.cause_adults_both)


df.model = df.absence_cause_adults %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "caused"))

# Check contrast values
 contrasts(df.model$question)


fit.brm.absence.cause.adults = brm(formula = difference ~ 1 + question + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     file = "cache/absence_cause_adult_difference") 

fit.brm.absence.cause.adults
```

##### Follow-up analysis 

```{r}
fit.brm.absence.cause.adults %>% 
  emmeans(spec = pairwise ~ question, 
          type = "response")

```



### CHILDREN
#### DATA
##### Read in data

```{r message=FALSE, warning=FALSE}

df.exp2_cause_children = read_csv("../../data/experiment2/cause/children/exp2_cause_children.csv")

```

##### Wrangle
```{r message=FALSE, warning=FALSE}

# clean responses
df.exp2_cause_children = df.exp2_cause_children %>% 
  rename(response = full_response,
         question = question_type) %>% 
  mutate(response = str_remove_all(string = response,
                                   pattern = "\""),
         response = str_remove_all(string = response,
                                   pattern = ":"),
         response = str_remove_all(string = response,
                                   pattern = "\\}"),
         response = str_remove_all(string = response,
                                   pattern = "\\."),
         response = str_remove_all(string = response,
                                   pattern = "\\,"),
         response = str_remove_all(string = response,
                                   pattern = "\\\\n"),
         response = str_to_lower(response))


# code responses
df.exp2_cause_children = df.exp2_cause_children %>%
  mutate(direct = ifelse(str_detect(response,
                                    "^sun$|sun | sun$"), 1, 0),
         direct = ifelse(str_detect(response,
                                    "^water$|water | water$"), 1, direct),
         direct = ifelse(str_detect(response,
                                    "^rain$|rain | rain$"), 1, direct),
         absence = ifelse(str_detect(response,
                                     "^sunscreen$|sunscreen | sunscreen$"), 1, 0),
         absence = ifelse(str_detect(response,
                                     "^window$|window | window$"), 1, absence),
         absence = ifelse(str_detect(response,
                                     "^latch$|latch | latch$"), 1, absence)) 


# compute age and replace simple with lexical
df.exp2_cause_children = df.exp2_cause_children %>%
  mutate(age = round(rounded_age / 365, digits = 2),
         age_whole =as.integer(age),
         question = str_replace_all(question, "simple", "lexical"))


```

##### Demographics

```{r message=FALSE, warning=FALSE}

 # gender
df.exp2_cause_children %>%
  group_by(gender) %>%
  summarise(n = n_distinct(participant)) %>%
  print()
  
  
  # language spoken
df.exp2_cause_children %>%
    mutate(en_occurrence = ifelse(str_detect(lan_spoken, "en"), "en", "non-en")) %>%
    group_by(en_occurrence) %>%
    summarise(n = n_distinct(participant)) %>%
    print()

```

#### STATS
##### Bayesian Model
```{r message=FALSE, warning=FALSE}
df.cause_children_different = df.exp2_cause_children %>%
  mutate(response_pattern = case_when(
   direct == 1 & absence == 1 ~ "both",
    direct == 0 & absence == 0 ~ "neither",
    TRUE ~ "different"
  )) %>%
  filter(response_pattern == "different") %>%
  mutate(difference = absence - direct,
        difference = recode(difference, `-1` = 0))

df.cause_children_both = df.exp2_cause_children %>%
  mutate(response_pattern = case_when(
    direct == 1 & absence == 1 ~ "both",
    direct == 0 & absence == 0 ~ "neither",
    TRUE ~ "different"
  )) %>%
  filter(response_pattern == "both") 


 df.cause_children_both = df.cause_children_both %>% 
  mutate(difference = 1) %>%
  bind_rows(df.cause_children_both %>% 
              mutate(difference = 0)) 

df.absence_cause_children = df.cause_children_different %>% 
  bind_rows(df.cause_children_both) 
  
df.model = df.absence_cause_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "caused"))

fit.brm.absence.cause.children = brm(formula = difference ~ 1 + question * age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     file = "cache/absence_cause_children_difference") 

fit.brm.absence.cause.children 
```

##### Follow-up analysis 

```{r}
# effect of question 
fit.brm.absence.cause.children %>% 
  emmeans(spec = pairwise ~ question, 
          type = "response")

# effect of age 
fit.brm.absence.cause.children %>% 
  avg_slopes(variable = "age",
             type = "link")
  
# interaction effect 
fit.brm.absence.cause.children %>% 
  emtrends(specs = pairwise ~ question,
           var = "age")
```

## MADE V LEXICAL (BURN & FLOOD)
### ADULTS
#### DATA
##### Read in data

```{r message=FALSE, warning=FALSE}

df.exp2_made_adults = read_csv("../../data/experiment2/made/adults/exp2_made_adults.csv")

```

##### Wrangle

```{r message=FALSE, warning=FALSE}

# clean responses
df.exp2_made_adults = df.exp2_made_adults %>% 
  mutate(condition = str_extract(string = responses,
                                 pattern = "sunburn_simple_response|sunburn_made_response|flood_simple_response|flood_made_response"),
         response = str_extract(string = responses, 
                                pattern = ":(.*)"),
         response = str_remove_all(string = response,
                                   pattern = "\""),
         response = str_remove_all(string = response,
                                   pattern = ":"),
         response = str_remove_all(string = response,
                                   pattern = "\\}"),
         response = str_remove_all(string = response,
                                   pattern = "\\."),
         response = str_remove_all(string = response,
                                   pattern = "\\,"),
         response = str_remove_all(string = response,
                                   pattern = "\\\\n"),
         response = str_to_lower(response)) %>% 
  separate(condition, c("scenario", "question", "extra"), "_") %>% 
  rename(participant = workerid) %>% 
  select(participant, scenario, question, response)

# code responses
df.exp2_made_adults = df.exp2_made_adults %>%
  mutate(direct = ifelse(str_detect(response,
                                    "^sun$|sun | sun$"), 1, 0),
         direct = ifelse(str_detect(response,
                                    "^water$|water | water$"), 1, direct),
         direct = ifelse(str_detect(response,
                                    "^rain$|rain | rain$"), 1, direct),
         absence = ifelse(str_detect(response,
                                     "^sunscreen$|sunscreen | sunscreen$"), 1, 0),
         absence = ifelse(str_detect(response,
                                     "^window$|window | window$"), 1, absence),
         absence = ifelse(str_detect(response,
                                     "^latch$|latch | latch$"), 1, absence))


## replace simple with lexical
df.exp2_made_adults = df.exp2_made_adults %>% 
  mutate(question = str_replace_all(question, "simple", "lexical"))


```

##### Demographics

```{r message=FALSE, warning=FALSE}

df.exp2_made_adults_demo = read_csv("../../data/experiment2/made/adults/exp2_made_adults_demo.csv")

df.exp2_made_adults_demo %>% 
  summarise(age_mean = mean(as.numeric(age), na.rm = TRUE))

df.exp2_made_adults_demo %>% 
  summarise(age_sd = sd(as.numeric(age), na.rm = TRUE))

df.exp2_made_adults_demo %>% 
  group_by(gender) %>% 
  count() 

df.exp2_made_adults_demo %>% 
  group_by(race) %>% 
  count() 

df.exp2_made_adults_demo %>% 
  group_by(ethnicity) %>% 
  count() 

```

#### STATS
##### Bayesian Model

```{r message=FALSE, warning=FALSE}

df.made_adults_different = df.exp2_made_adults %>%
  mutate(response_pattern = case_when(
    direct == 1 & absence == 1 ~ "both",
    direct == 0 & absence == 0 ~ "neither",
    TRUE ~ "different"
  )) %>%
  filter(response_pattern == "different") %>%
  mutate(difference = absence - direct,
        difference = recode(difference, `-1` = 0))

df.made_adults_both = df.exp2_made_adults %>%
  mutate(response_pattern = case_when(
    direct == 1 & absence == 1 ~ "both",
    direct == 0 & absence == 0 ~ "neither",
    TRUE ~ "different"
  )) %>%
  filter(response_pattern == "both")
  
  
df.made_adults_both = df.made_adults_both %>% 
  mutate(difference = 1) %>%
  bind_rows(df.made_adults_both %>% 
              mutate(difference = 0)) 

df.absence_made_adults = df.made_adults_different %>% 
  bind_rows(df.made_adults_both)


df.model = df.absence_made_adults %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "caused"))

# Check contrast values
 contrasts(df.model$question)


fit.brm.absence.made.adults = brm(formula = difference ~ 1 + question + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     file = "cache/absence_made_adult_difference") 

fit.brm.absence.made.adults
```

##### Follow-up analysis 

```{r}
fit.brm.absence.made.adults %>% 
  emmeans(spec = pairwise ~ question, 
          type = "response")

```

### CHILDREN
#### DATA
##### Read in data

```{r message=FALSE, warning=FALSE}

df.exp2_made_children = read_csv("../../data/experiment2/made/children/exp2_made_children.csv")

```

##### Wrangle
```{r message=FALSE, warning=FALSE}

# clean responses
df.exp2_made_children = df.exp2_made_children %>% 
  rename(response = full_response,
         question = question_type) %>% 
  mutate(response = str_remove_all(string = response,
                                   pattern = "\""),
         response = str_remove_all(string = response,
                                   pattern = ":"),
         response = str_remove_all(string = response,
                                   pattern = "\\}"),
         response = str_remove_all(string = response,
                                   pattern = "\\."),
         response = str_remove_all(string = response,
                                   pattern = "\\,"),
         response = str_remove_all(string = response,
                                   pattern = "\\\\n"),
         response = str_to_lower(response))

# code responses
df.exp2_made_children = df.exp2_made_children %>%
  mutate(direct = ifelse(str_detect(response,
                                    "^sun$|sun | sun$"), 1, 0),
         direct = ifelse(str_detect(response,
                                    "^water$|water | water$"), 1, direct),
         direct = ifelse(str_detect(response,
                                    "^rain$|rain | rain$"), 1, direct),
         absence = ifelse(str_detect(response,
                                     "^sunscreen$|sunscreen | sunscreen$"), 1, 0),
         # note the first response in the data is 'windows' but this doesn't capture that
         absence = ifelse(str_detect(response,
                                     "^window$|window | window$"), 1, absence),
         absence = ifelse(str_detect(response,
                                     "^latch$|latch | latch$"), 1, absence)) 


# compute age and replace simple with lexical
df.exp2_made_children = df.exp2_made_children %>%
  mutate(age = round(rounded_age / 365, digits = 2),
         age_whole = as.integer(age),
         question = str_replace_all(question, "simple", "lexical")) %>% 
  rename(participant = `participant _number`)


```

##### Demographics

```{r message=FALSE, warning=FALSE}

 # gender
df.exp2_made_children %>%
  group_by(gender) %>%
  summarise(n = n_distinct(participant)) %>%
  print()
  
  
  # language spoken
df.exp2_made_children %>%
    mutate(en_occurrence = ifelse(str_detect(lan_spoken, "en"), "en", "non-en")) %>%
    group_by(en_occurrence) %>%
    summarise(n = n_distinct(participant)) %>%
    print()

```

#### STATS
##### Bayesian Model
```{r message=FALSE, warning=FALSE}


df.made_children_different = df.exp2_made_children %>%
  mutate(response_pattern = case_when(
     direct == 1 & absence == 1 ~ "both",
    direct == 0 & absence == 0 ~ "neither",
    TRUE ~ "different"
  )) %>%
  filter(response_pattern == "different") %>%
  mutate(difference = absence - direct,
        difference = recode(difference, `-1` = 0))

df.made_children_both = df.exp2_made_children %>%
  mutate(response_pattern = case_when(
    direct == 1 & absence == 1 ~ "both",
    direct == 0 & absence == 0 ~ "neither",
    TRUE ~ "different"
  )) %>%
  filter(response_pattern == "both")

df.made_children_both = df.made_children_both %>% 
  mutate(difference = 1) %>%
  bind_rows(df.made_children_both %>% 
              mutate(difference = 0)) 

df.absence_made_children = df.made_children_different %>% 
  bind_rows(df.made_children_both) 
  
df.model = df.absence_made_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "made"))


# Check contrast values
 contrasts(df.model$question)
 


fit.brm.absence.made.children = brm(formula = difference ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     file = "cache/absence_made_children_difference") 

fit.brm.absence.made.children


```

##### Follow-up analysis 

```{r}

# effect of question 
fit.brm.absence.made.children %>% 
  emmeans(spec = pairwise ~ question, 
          type = "response")

# effect of age 
fit.brm.absence.made.children %>% 
  avg_slopes(variable = "age",
             type = "link")
  
# interaction effect 
fit.brm.absence.made.children %>% 
  emtrends(specs = pairwise ~ question,
           var = "age")
```


## PLOTS

### Responses Plots
#### Cause v Lexical
```{r message=FALSE, warning=FALSE}


df.data = expand_grid(age = seq(4, 9, 0.1),
                      question = c("caused", "lexical"))

df.prediction = fit.brm.absence.cause.children %>%
  fitted(newdata = df.data,
         re_formula = NA,
          probs = c(0.1, 0.9)) %>%
  as_tibble() %>%
  bind_cols(df.data) %>%
  clean_names()


df.means = df.absence_cause_adults %>% 
  mutate(age_whole = rep(10)) %>% 
  bind_rows(df.absence_cause_children) %>% 
  mutate(age_whole = factor(age_whole,
                            levels = c(4, 5, 6, 7, 8, 9, 10),
                            labels = c("4", "5", "6", "7", "8", "9", "adults"))) %>%
  group_by(age_whole, question) %>%
  summarize(
    response = Hmisc::smean.cl.boot(difference)) %>%
    mutate(index = c("response", "low", "high")) %>%
    ungroup() %>%
    pivot_wider(names_from = index,
                values_from = response) %>%
  mutate(age_whole = fct_recode(age_whole, "10" = "adults"),
         age_whole = as.numeric(as.character(age_whole)))


gradient_segments = data.frame(
  x = rep(min(df.means$age_whole), 100),
  xend = rep(max(df.means$age_whole), 100),
  y = seq(0, 1, length.out = 100),
  yend = seq(0, 1, length.out = 100),
  color = scales::gradient_n_pal(c("#377EB8", "#E41A1C"))(seq(0, 1, length.out = 100))
)

custom_labels = function(breaks) {
  counts = df.absence_cause_adults %>% 
  mutate(age_whole = rep(10)) %>% 
  bind_rows(df.absence_cause_children) %>% 
  mutate(age_whole = factor(age_whole,
                            levels = c(4, 5, 6, 7, 8, 9, 10),
                            labels = c("4", "5", "6", "7", "8", "9", "Adults"))) %>%
  group_by(age_whole) %>%
  summarize(count = n_distinct(participant)) %>%
    pull(count)
  labels = c("4", "5", "6", "7", "8", "9", "Adults")
  paste0(labels, "<br><span style='font-size:10px;'>n=", counts, "</span>")
}


p5 = ggplot(mapping = aes(x = age,
                     y = difference,
                     color = question)) +
    geom_segment(data = gradient_segments,
               aes(x = 3.9, 
                   xend = 10.1, 
                   y = y, 
                   yend = yend, 
                   color = I(color)),
               size = 1.1) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  geom_smooth(data = df.prediction,
              mapping = aes(y = estimate,
                            ymin = q10,
                            ymax = q90,
                            color = question,
                            fill = question),
              stat = "identity",
              alpha = 0.2,
              show.legend = F) +
  geom_pointrange(data = df.means,
                  mapping = aes(x = age_whole,
                                y = response,
                                ymin = low,
                                ymax = high,
                                shape = question),
                  color = "black",
                  fill = "white",
                  size = 0.5,
                  show.legend = TRUE,
                  alpha = 0.8,
                  position = position_dodge(width = 0.3)) +
  scale_fill_manual(values = c("caused" = "black",
                               "lexical" = "black")) +
  scale_color_manual(values = c("caused" = "black",
                                "lexical" = "black")) +
  scale_shape_manual(values = c("caused" = 21,
                               "lexical" = 23)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = c("100% \n direct", "75%", "50%", "75%", "100% \n absent"),
                      limits = c(0, 1)) +
 scale_x_continuous(breaks = 4:10,
                    labels = custom_labels(labels),
                    limits = c(3.9, 10.1)) +
  labs(y = "Probability of selecting \n direct or absent cause") +
  theme(legend.position = "none",
        legend.title = element_blank(),
        text = element_text(size = 18),
        axis.text.x = element_markdown(),
        axis.title.x = element_blank()) +
  facet_wrap(~factor(question,
             levels = c("lexical", "caused"))) 
 

```


#### Made v Lexical
```{r message=FALSE, warning=FALSE}

df.data = expand_grid(age = seq(4, 9, 0.1),
                      question = c("made", "lexical"))

df.prediction = fit.brm.absence.made.children %>%
  fitted(newdata = df.data,
         re_formula = NA,
          probs = c(0.1, 0.9)) %>%
  as_tibble() %>%
  bind_cols(df.data) %>%
  clean_names()


df.means = df.absence_made_adults %>% 
  mutate(age_whole = rep(10)) %>% 
  bind_rows(df.absence_made_children) %>% 
  mutate(age_whole = factor(age_whole,
                            levels = c(4, 5, 6, 7, 8, 9, 10),
                            labels = c("4", "5", "6", "7", "8", "9", "adults"))) %>%
  group_by(age_whole, question) %>%
  summarize(
    response = Hmisc::smean.cl.boot(difference)) %>%
    mutate(index = c("response", "low", "high")) %>%
    ungroup() %>%
    pivot_wider(names_from = index,
                values_from = response) %>%
  mutate(age_whole = fct_recode(age_whole, "10" = "adults"),
         age_whole = as.numeric(as.character(age_whole)))


gradient_segments = data.frame(
  x = rep(min(df.means$age_whole), 100),
  xend = rep(max(df.means$age_whole), 100),
  y = seq(0, 1, length.out = 100),
  yend = seq(0, 1, length.out = 100),
  color = scales::gradient_n_pal(c("#377EB8", "#E41A1C"))(seq(0, 1, length.out = 100))
)

custom_labels = function(breaks) {
  counts = df.absence_made_adults %>% 
  mutate(age_whole = rep(10)) %>% 
  bind_rows(df.absence_made_children) %>% 
  mutate(age_whole = factor(age_whole,
                            levels = c(4, 5, 6, 7, 8, 9, 10),
                            labels = c("4", "5", "6", "7", "8", "9", "Adults"))) %>%
  group_by(age_whole) %>%
  summarize(count = n_distinct(participant)) %>%
    pull(count)
  labels = c("4", "5", "6", "7", "8", "9", "Adults")
  paste0(labels, "<br><span style='font-size:10px;'>n=", counts, "</span>")
}


p6 = ggplot(mapping = aes(x = age,
                     y = difference,
                     color = question)) +
    geom_segment(data = gradient_segments,
               aes(x = 3.9, 
                   xend = 10.1, 
                   y = y, 
                   yend = yend, 
                   color = I(color)),
               size = 1.1) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  geom_smooth(data = df.prediction,
              mapping = aes(y = estimate,
                            ymin = q10,
                            ymax = q90,
                            color = question,
                            fill = question),
              stat = "identity",
              alpha = 0.2,
              show.legend = F) +
  geom_pointrange(data = df.means,
                  mapping = aes(x = age_whole,
                                y = response,
                                ymin = low,
                                ymax = high,
                                shape = question),
                  color = "black",
                  fill = "white",
                  size = 0.5,
                  show.legend = TRUE,
                  alpha = 0.8,
                  position = position_dodge(width = 0.3)) +
  scale_fill_manual(values = c("made" = "black",
                               "lexical" = "black")) +
  scale_color_manual(values = c("made" = "black",
                                "lexical" = "black")) +
  scale_shape_manual(values = c("made" = 21,
                               "lexical" = 23)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = c("100% \n direct", "75%", "50%", "75%", "100% \n absent"),
                      limits = c(0, 1)) +
 scale_x_continuous(breaks = 4:10,
                    labels = custom_labels(labels),
                    limits = c(3.9, 10.1)) +
  labs(y = "Probability of selecting \n direct or absent cause") +
  theme(legend.position = "none",
        legend.title = element_blank(),
        text = element_text(size = 18),
        axis.text.x = element_markdown(),
        axis.title.x = element_blank()) +
  facet_wrap(~factor(question,
             levels = c("lexical", "made"))) 
 

```

### Responses Patterns by Age
##### Cause v Lexical
```{r}

df.plot = df.exp2_cause_adults %>% 
  mutate(age_whole = 10) %>% 
  bind_rows(df.exp2_cause_children) %>% 
  mutate(response_pattern = case_when(
    direct == 1 & absence == 1 ~ "both",
    direct == 0 & absence == 0 ~ "neither",
    direct == 1 & absence == 0  ~ "direct only",
    direct == 0 & absence == 1  ~ "absence only",
  ),
  question = recode(question, "cause" = "caused"),
  age_whole = as.factor(age_whole)) %>% 
  group_by(age_whole, question, response_pattern) %>% 
  summarize(n = n()) %>% 
  ungroup() %>%
  group_by(age_whole, question) %>%
  mutate(percentage = n / sum(n) * 100) %>%
  ungroup() %>% 
  mutate(question = factor(question, levels = c("lexical", "caused")),
         response_pattern = factor(response_pattern, levels = c("absence only", "direct only", "both", "neither")))

custom_labels = function(breaks) {
  counts = df.exp2_cause_adults %>% 
  mutate(age_whole = rep(10)) %>% 
  bind_rows(df.exp2_cause_children) %>% 
  mutate(age_whole = factor(age_whole,
                            levels = c(4, 5, 6, 7, 8, 9, 10),
                            labels = c("4", "5", "6", "7", "8", "9", "Adults"))) %>%
  group_by(age_whole) %>%
  summarize(count = n_distinct(participant)) %>%
    pull(count)
  labels = c("4", "5", "6", "7", "8", "9", "Adults")
  paste0(labels, "<br><span style='font-size:10px;'>n=", counts, "</span>")
}


p7 = ggplot(data = df.plot,
       mapping = aes(x = age_whole,
                     y = percentage,
                     group = response_pattern,
                     color = response_pattern,
                     fill = response_pattern)) +
  geom_col(color = "black") +
 scale_fill_manual(values = c("absence only" = "#E41A1C",
                               "direct only" = "#377EB8",
                               "both" = "#984EA3",
                               "neither" = "#999999")) +
  scale_color_manual(values = c("absence only" = "#E41A1C",
                                "direct only" = "#377EB8",
                                "both" = "#984EA3",
                                "neither" = "#999999")) +
  scale_shape_manual(values = c(21, 23)) +
  scale_y_continuous(breaks = seq(0, 100, 25),
                     labels = str_c(seq(0, 100, 25), "%")) +
  scale_x_discrete(breaks = 4:10,
                  labels = custom_labels(labels)) +
  labs(y = "Response pattern \n\ probability") +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        text = element_text(size = 18),
        axis.text.x = element_markdown(),
        axis.title.x = element_blank()) +
  facet_wrap(~question)

```

##### Made v Lexical
```{r}

df.plot = df.exp2_made_adults %>% 
  mutate(age_whole = 10) %>% 
  bind_rows(df.exp2_made_children) %>% 
  mutate(response_pattern = case_when(
    direct == 1 & absence == 1 ~ "both",
    direct == 0 & absence == 0 ~ "neither",
    direct == 1 & absence == 0  ~ "direct only",
    direct == 0 & absence == 1  ~ "absence only",
  ),
  age_whole = as.factor(age_whole)) %>% 
  group_by(age_whole, question, response_pattern) %>% 
  summarize(n = n()) %>% 
  ungroup() %>%
  group_by(age_whole, question) %>%
  mutate(percentage = n / sum(n) * 100) %>%
  ungroup() %>% 
  mutate(question = factor(question, levels = c("lexical", "made")),
         response_pattern = factor(response_pattern, levels = c("absence only", "direct only", "both", "neither")))

custom_labels = function(breaks) {
  counts = df.exp2_made_adults %>% 
  mutate(age_whole = rep(10)) %>% 
  bind_rows(df.exp2_made_children) %>% 
  mutate(age_whole = factor(age_whole,
                            levels = c(4, 5, 6, 7, 8, 9, 10),
                            labels = c("4", "5", "6", "7", "8", "9", "Adults"))) %>%
  group_by(age_whole) %>%
  summarize(count = n_distinct(participant)) %>%
    pull(count)
  labels = c("4", "5", "6", "7", "8", "9", "Adults")
  paste0(labels, "<br><span style='font-size:10px;'>n=", counts, "</span>")
}


p8 = ggplot(data = df.plot,
       mapping = aes(x = age_whole,
                     y = percentage,
                     group = response_pattern,
                     color = response_pattern,
                     fill = response_pattern)) +
  geom_col(color = "black") +
  scale_fill_manual(values = c("absence only" = "#E41A1C",
                               "direct only" = "#377EB8",
                               "both" = "#984EA3",
                               "neither" = "#999999")) +
  scale_color_manual(values = c("absence only" = "#E41A1C",
                                "direct only" = "#377EB8",
                                "both" = "#984EA3",
                                "neither" = "#999999")) +
  scale_shape_manual(values = c(21, 23)) +
  scale_y_continuous(breaks = seq(0, 100, 25),
                     labels = str_c(seq(0, 100, 25), "%")) +
  scale_x_discrete(breaks = 4:10,
                    labels = custom_labels(labels)) +
  labs(y = "Response pattern \n\ probability") +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        text = element_text(size = 18),
        axis.text.x = element_markdown(),
        axis.title.x = element_blank()) +
  facet_wrap(~question)


```
### Combine Cause and Made Plots
```{r fig.height=5, fig.width=18, message=FALSE, warning=FALSE}

plot = p5 + p6 + p7 + p8 +
plot_layout(nrow = 2) &
plot_annotation(tag_levels = "A") &
theme(plot.tag = element_text(face = "bold"))

ggsave(plot, filename = "../../figures/experiment2/absence_response_patterns_age.pdf", height = 8, width = 16)

plot


```


# EXPERIMENT 3: ABSENCES 
## EXPLANATION
### ADULTS
#### DATA
##### Read in data

```{r message=FALSE, warning=FALSE}

df.exp3_adults = read_csv("../../data/experiment3/adults/exp3_adults.csv")

```

##### Wrangle

```{r message=FALSE, warning=FALSE}

# clean responses
df.exp3_adults = df.exp3_adults %>% 
  mutate(condition = str_extract(string = responses,
                                 pattern = "sunburn_simple_response|sunburn_made_response|flood_simple_response|flood_made_response"),
         response = str_extract(string = responses, 
                                pattern = ":(.*)"),
         response = str_remove_all(string = response,
                                   pattern = "\""),
         response = str_remove_all(string = response,
                                   pattern = ":"),
         response = str_remove_all(string = response,
                                   pattern = "\\}"),
         response = str_remove_all(string = response,
                                   pattern = "\\."),
         response = str_remove_all(string = response,
                                   pattern = "\\,"),
         response = str_remove_all(string = response,
                                   pattern = "\\\\n"),
         response = str_to_lower(response)) %>% 
  separate(condition, c("scenario", "question", "extra"), "_") %>% 
  rename(participant = workerid) %>% 
  select(participant, scenario, question, response)

# code responses
df.exp3_adults = df.exp3_adults %>%
  mutate(direct = ifelse(str_detect(response,
                                    "^sun$|sun | sun$"), 1, 0),
         direct = ifelse(str_detect(response,
                                    "^water$|water | water$"), 1, direct),
         direct = ifelse(str_detect(response,
                                    "^rain$|rain | rain$"), 1, direct),
         absence = ifelse(str_detect(response,
                                     "^sunscreen$|sunscreen | sunscreen$"), 1, 0),
         absence = ifelse(str_detect(response,
                                     "^window$|window | window$"), 1, absence),
         absence = ifelse(str_detect(response,
                                     "^latch$|latch | latch$"), 1, absence))




```

##### Demographics

```{r message=FALSE, warning=FALSE}

df.exp3_adults_demo = read_csv("../../data/experiment3/adults/exp3_adults_demo.csv")

df.exp3_adults_demo %>% 
  summarise(age_mean = mean(as.numeric(age), na.rm = TRUE))

df.exp3_adults_demo %>% 
  summarise(age_sd = sd(as.numeric(age), na.rm = TRUE))

df.exp3_adults_demo %>% 
  group_by(gender) %>% 
  count() 

df.exp3_adults_demo %>% 
  group_by(race) %>% 
  count() 

df.exp3_adults_demo %>% 
  group_by(ethnicity) %>% 
  count() 


```

#### STATS
##### Bayesian Model

```{r}

df.model = df.exp3_adults %>% 
  select(-response) %>% 
  pivot_longer(cols = direct:absence,
               names_to = "causal_candidate",
               values_to = "response") %>% 
  mutate(causal_candidate = factor(causal_candidate, levels = c("direct", "absence")), 
         causal_candidate= fct_relevel(causal_candidate, "absence"))

# check levels of causal_candidate
contrasts(df.model$causal_candidate)

fit.brm.exp.adults = brm(formula = response ~ 1 + causal_candidate + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/explanation_adult") 
fit.brm.exp.adults

```

##### Follow-up analysis 

```{r}
fit.brm.exp.adults %>% 
  emmeans(spec = pairwise ~ causal_candidate, 
          type = "response")

```

### CHILDREN
#### DATA
##### Read in Data

```{r message=FALSE, warning=FALSE}

df.exp3_children = read_csv("../../data/experiment3/children/exp3_children.csv")

```

##### Wrangle

```{r message=FALSE, warning=FALSE}

# clean data
df.exp3_children = df.exp3_children %>% 
  clean_names() %>% 
  rename(response_1 = full_response_11,
         response_2 = full_response_13) %>% 
  select(participant_number, rounded_age, scenario_1, scenario_2, response_1, response_2, gender, lan_spoken) %>%
  pivot_longer(
    cols = c(-participant_number, -rounded_age, -gender, -lan_spoken),
    names_to = c(".value"),
    names_pattern = "(^scenario|^response)"
  ) %>% 
  mutate(response = str_remove_all(string = response,
                                   pattern = "\""),
         response = str_remove_all(string = response,
                                   pattern = ":"),
         response = str_remove_all(string = response,
                                   pattern = "\\("),
         response = str_remove_all(string = response,
                                   pattern = "\\)"),
         response = str_remove_all(string = response,
                                   pattern = "\\}"),
         response = str_remove_all(string = response,
                                   pattern = "\\."),
         response = str_remove_all(string = response,
                                   pattern = "\\,"),
         response = str_remove_all(string = response,
                                   pattern = "\\\\n"),
         response = str_to_lower(response))

# code responses
df.exp3_children = df.exp3_children %>%
  mutate(direct = ifelse(str_detect(response,
                                    "^sun$|sun | sun$"), 1, 0),
         direct = ifelse(str_detect(response,
                                    "^water$|water | water$"), 1, direct),
         direct = ifelse(str_detect(response,
                                    "^rain$|rain | rain$"), 1, direct),
         absence = ifelse(str_detect(response,
                                     "^sunscreen$|sunscreen | sunscreen$"), 1, 0),
         absence = ifelse(str_detect(response,
                                     "^window$|window | window$"), 1, absence),
         absence = ifelse(str_detect(response,
                                     "^windows$|windows | windows$"), 1, absence),
         absence = ifelse(str_detect(response,
                                     "^latch$|latch | latch$"), 1, absence),
         age = round(rounded_age / 365, digits = 2)) %>% 
  rename(participant = participant_number)


df.exp3_children %>% 
  summarise(n_distinct(participant))
```

##### Demographics

```{r message=FALSE, warning=FALSE}

 # gender
df.exp3_children %>%
  group_by(gender) %>%
  summarise(n = n_distinct(participant)) %>%
  print()
  
  
  # language spoken
df.exp3_children %>%
    mutate(en_occurrence = ifelse(str_detect(lan_spoken, "en"), "en", "non-en")) %>%
    group_by(en_occurrence) %>%
    summarise(n = n_distinct(participant)) %>%
    print()

```

#### STATS

##### Bayesian Model

```{r message=FALSE, warning=FALSE}

df.model = df.exp3_children %>% 
  select(-response) %>% 
  pivot_longer(cols = direct:absence,
               names_to = "causal_candidate",
               values_to = "response") %>% 
  mutate(causal_candidate = factor(causal_candidate, levels = c("direct", "absence")),
         causal_candidate= fct_relevel(causal_candidate, "absence"))


# check levels of causal_candidate
contrasts(df.model$causal_candidate)

# removed random intercepts for scenario to avoid divergent transition errors
fit.brm.exp.children = brm(formula = response ~ 1 + causal_candidate + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/explanation_children") 

fit.brm.exp.children

```

##### Follow-up analysis 

```{r}
fit.brm.exp.children %>% 
  emmeans(spec = pairwise ~ causal_candidate, 
          type = "response")

```

### PLOTS
#### Responses Patterns by Age
```{r}

df.plot = df.exp3_adults %>% 
  mutate(age_whole = 7) %>% 
  bind_rows(df.exp3_children %>% 
               mutate(age_whole = as.integer(age))) %>% 
  mutate(response_pattern = case_when(
    direct == 1 & absence == 1 ~ "both",
    direct == 0 & absence == 0 ~ "neither",
    direct == 1 & absence == 0  ~ "direct only",
    direct == 0 & absence == 1  ~ "absence only",
  ),
  question = recode(question, "cause" = "caused"),
  age_whole = as.factor(age_whole)) %>% 
  group_by(age_whole, response_pattern) %>% 
  summarize(n = n()) %>% 
  ungroup() %>%
  group_by(age_whole) %>%
  mutate(percentage = n / sum(n) * 100) %>%
  ungroup() %>% 
  mutate(response_pattern = factor(response_pattern, levels = c("absence only", "direct only", "both", "neither"))) %>% 
  filter(!is.na(age_whole))

custom_labels = function(breaks) {
  counts = df.exp3_adults %>% 
    mutate(age_whole = rep(7)) %>% 
    bind_rows(df.exp3_children %>% 
                mutate(age_whole = as.integer(age))) %>% 
    mutate(age_whole = factor(age_whole,
                              levels = c(4, 5, 6, 7),
                              labels = c("4", "5", "6", "Adults"))) %>%
    filter(!is.na(age_whole)) %>% 
    group_by(age_whole) %>%
    summarize(count = n_distinct(participant)) %>%
    pull(count)
  labels = c("4", "5", "6", "Adults")
  paste0(labels, "<br><span style='font-size:10px;'>n=", counts, "</span>")
}


ggplot(data = df.plot,
       mapping = aes(x = age_whole,
                     y = percentage,
                     group = response_pattern,
                     color = response_pattern,
                     fill = response_pattern)) +
  geom_col(color = "black") +
    scale_fill_manual(values = c("absence only" = "#E41A1C",
                               "direct only" = "#377EB8",
                               "both" = "#984EA3",
                               "neither" = "#999999")) +
  scale_color_manual(values = c("absence only" = "#E41A1C",
                                "direct only" = "#377EB8",
                                "both" = "#984EA3",
                                "neither" = "#999999")) +
  scale_shape_manual(values = c(21, 23)) +
  scale_y_continuous(breaks = seq(0, 100, 25),
                     labels = str_c(seq(0, 100, 25), "%")) +
  scale_x_discrete(breaks = 4:7,
                   labels = custom_labels(labels)) +
  labs(y = "Response pattern \n\ probability") +
 theme(legend.position = "bottom",
        legend.title = element_blank(),
        text = element_text(size = 18),
        axis.text.x = element_markdown(),
        axis.title.x = element_blank())


ggsave("../../figures/experiment3/explanation_response_patterns_age.pdf", height = 4, width = 6)

```


# APPENDIX
# EXPERIMENT 1: CHAINS
## CAUSE V LEXICAL (BREAK & CRACK)
### ADULTS
#### STATS
##### Bayesian Models
###### Distal

```{r message=FALSE, warning=FALSE}


df.model = df.exp1_cause_adults %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "cause"))

# Check contrast values
 contrasts(df.model$question)

# removed random intercepts for scenario to avoid divergent transition errors
fit.brm.cause.adult.distal = brm(formula = distal ~ 1 + question + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_adult_distal") 
fit.brm.cause.adult.distal


```

###### Proximal

```{r}

fit.brm.cause.adult.proximal = brm(formula = proximal ~ 1 + question + (1 | participant) + (1 | scenario),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/cause_adult_proximal") 

fit.brm.cause.adult.proximal

```

### CHILDREN
#### STATS
##### Bayesian Models
###### Distal

```{r message=FALSE, warning=FALSE}

df.model = df.exp1_cause_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "caused"),
         age = age - mean(age))

# Check contrast values
 contrasts(df.model$question)


fit.brm.cause.children.distal = brm(formula = distal ~ 1 + question + (1 | participant) + (1 | scenario),
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_children_distal") 

fit.brm.cause.children.distal


fit.brm.cause.children.distal.age = brm(formula = distal ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_children_distal_age") 

fit.brm.cause.children.distal.age 

```

###### Proximal
```{r message=FALSE, warning=FALSE}

# removed random intercepts for scenario to avoid divergent transition errors
fit.brm.cause.children.proximal = brm(formula = proximal ~ 1 + question + (1 | participant),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/cause_children_proximal") 

fit.brm.cause.children.proximal


fit.brm.cause.children.proximal.age = brm(formula = proximal ~ 1 + question*age + (1 | participant) + (1 | scenario),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/cause_children_proximal_age") 

fit.brm.cause.children.proximal.age


```

## MADE v LEXICAL (BREAK & CRACK)
### ADULTS
#### STATS
##### Bayesian Models
###### Distal

```{r message=FALSE, warning=FALSE}

df.model = df.exp1_made_adults %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "made"))

# Check contrast values
 contrasts(df.model$question)


fit.brm.made.adult.distal = brm(formula = distal ~ 1 + question + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/made_adult_distal") 

fit.brm.made.adult.distal




```

###### Proximal

```{r message=FALSE, warning=FALSE}

fit.brm.made.adult.proximal = brm(formula = proximal ~ 1 + question + (1 | participant) + (1 | scenario),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/made_adult_proximal") 

fit.brm.made.adult.proximal


```

### CHILDREN
#### STATS
##### Bayesian Models
###### Distal
```{r message=FALSE, warning=FALSE}

df.model = df.exp1_made_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "made"),
         age = age - mean(age))

# Check contrast values
 contrasts(df.model$question)


fit.brm.made.children.distal = brm(formula = distal ~ 1 + question + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/made_children_distal") 

fit.brm.made.children.distal


fit.brm.made.children.distal.age = brm(formula = distal ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/made_children_distal_age") 

fit.brm.made.children.distal.age

```

###### Proximal

```{r message=FALSE, warning=FALSE}

fit.brm.proximal = brm(formula = proximal ~ 1 + question + (1 | participant) + (1 | scenario),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/made_children_proximal") 

fit.brm.proximal


fit.brm.proximal.age = brm(formula = proximal ~ 1 + question*age + (1 | participant) + (1 | scenario),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/made_children_proximal_age") 

fit.brm.proximal.age



```

## CAUSE v MADE
### ADULTS
#### DATA
##### Wrangle

```{r message=FALSE, warning=FALSE}

df.exp1_cause_made_adults = df.exp1_cause_adults %>% 
  filter(question == "caused") %>% 
  select(-participant) %>% 
  bind_rows(df.exp1_made_adults %>% 
  filter(question == "made") %>% 
  select(-participant)) %>% 
  mutate(participant = rep(1:(n()/2), each = 2))


```

#### STATS

##### Bayesian Models
###### Distal

```{r message=FALSE, warning=FALSE}

df.model = df.exp1_cause_made_adults %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "made"))

# Check contrast values
 contrasts(df.model$question)


fit.brm.cause.made.adult.distal = brm(formula = distal ~ 1 + question + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_made_adult_distal") 

fit.brm.cause.made.adult.distal



```

###### Proximal

```{r message=FALSE, warning=FALSE}

fit.brm.cause.made.adult.proximal = brm(formula = proximal ~ 1 + question + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_made_adult_proximal") 

fit.brm.cause.made.adult.proximal

```

### CHILDREN
#### DATA
##### Wrangle

```{r message=FALSE, warning=FALSE}

df.exp1_cause_made_children = df.exp1_cause_children %>% 
  filter(question == "caused") %>% 
  select(-caused_question_order, participant) %>% 
  bind_rows(df.exp1_made_children %>% 
  filter(question == "made") %>% 
  select(-made_question_order, participant)) %>% 
  mutate(participant = rep(1:(n()/2), each = 2))


```

#### STATS

##### Bayesian Models
###### Distal

```{r message=FALSE, warning=FALSE}

df.model = df.exp1_cause_made_children %>% 
  mutate(question = fct_relevel(question, "made"),
         age = age - mean(age))

# Check contrast values
 contrasts(df.model$question)



fit.brm.cause.made.children.distal = brm(formula = distal ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_made_children_distal.rds") 

fit.brm.cause.made.children.distal


```

###### Proximal

```{r message=FALSE, warning=FALSE}

fit.brm.cause.made.children.proximal = brm(formula = proximal ~ 1 + question*age + (1 | participant) + (1 | scenario),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/cause_made_children_proximal") 

fit.brm.cause.made.children.proximal



```


## ORDER EFFECTS
### CHILDREN
#### DATA
##### Wrangle

```{r}

df.exp1_cause_children_order = df.exp1_cause_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "lexical"),
         order = as_factor(caused_question_order),
         order = fct_relevel(order, "second")) %>% 
  group_by(participant) %>%
  filter(row_number() <= 2) %>%
  ungroup() %>% 
  filter(question == "caused") %>% 
  mutate(difference = distal - proximal,
         difference = recode(difference, `-1` = 0))

df.exp1_cause_lexical_children_order = df.exp1_cause_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "lexical"),
         order = as_factor(caused_question_order),
         order = fct_relevel(order, "second"),
         order = str_replace_all(order, "first", "temp_placeholder"),
         order = str_replace_all(order, "second", "first"),
         order = str_replace_all(order, "temp_placeholder", "second"),
         order = as_factor(order),
         order = fct_relevel(order, "second")) %>% 
  group_by(participant) %>%
  filter(row_number() <= 2) %>%
  ungroup() %>% 
  filter(question == "lexical") %>% 
  mutate(difference = distal - proximal,
         difference = recode(difference, `-1` = 0))


df.exp1_made_children_order = df.exp1_made_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "lexical"),
         order = as_factor(made_question_order),
         order = fct_relevel(order, "second")) %>% 
  group_by(participant) %>%
  filter(row_number() <= 2) %>%
  ungroup() %>% 
  filter(question == "made") %>% 
  mutate(difference = distal - proximal,
         difference = recode(difference, `-1` = 0))

df.exp1_made_lexical_children_order = df.exp1_made_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "lexical"),
         order = as_factor(made_question_order),
         order = fct_relevel(order, "second"),
         order = str_replace_all(order, "first", "temp_placeholder"),
         order = str_replace_all(order, "second", "first"),
         order = str_replace_all(order, "temp_placeholder", "second"),
         order = as_factor(order),
         order = fct_relevel(order, "second")) %>% 
  group_by(participant) %>%
  filter(row_number() <= 2) %>%
  ungroup() %>% 
  filter(question == "lexical") %>% 
mutate(difference = distal - proximal,
       difference = recode(difference, `-1` = 0))




```

#### STATS

##### Bayesian Models

```{r message=FALSE, warning=FALSE}



# Check contrast values
contrasts(df.exp1_cause_children_order$order)

fit.brm.df.exp1.cause.children.order = brm(formula = difference ~ 1 + order + (1 | participant) + (1 | scenario), 
                     data = df.exp1_cause_children_order,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     file = "cache/exp1_cause_children_order") 

fit.brm.df.exp1.cause.children.order



# Check contrast values
contrasts(df.exp1_cause_lexical_children_order$order)


fit.brm.df.exp1.cause.lexical.children.order = brm(formula = difference ~ 1 + order + (1 | participant) + (1 | scenario), 
                     data = df.exp1_cause_lexical_children_order,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     file = "cache/exp1_cause_lexical_children_order") 

fit.brm.df.exp1.cause.lexical.children.order



# Check contrast values
contrasts(df.exp1_made_children_order$order)

fit.brm.df.exp1.made.children.order = brm(formula = difference ~ 1 + order + (1 | participant) + (1 | scenario), 
                     data = df.exp1_made_children_order,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     file = "cache/exp1_made_children_order") 

fit.brm.df.exp1.made.children.order



# Check contrast values
contrasts(df.exp1_made_lexical_children_order$order)

fit.brm.df.exp1.made.lexical.children.order = brm(formula = difference ~ 1 + order + (1 | participant) + (1 | scenario), 
                     data = df.exp1_made_lexical_children_order,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     file = "cache/exp1_made_lexical_children_order") 

fit.brm.df.exp1.made.lexical.children.order

```

##### Follow-up analysis 

```{r}

fit.brm.df.exp1.cause.children.order %>% 
  emmeans(spec = pairwise ~ order, 
          type = "response")

fit.brm.df.exp1.cause.lexical.children.order %>% 
  emmeans(spec = pairwise ~ order, 
          type = "response")

fit.brm.df.exp1.made.children.order %>% 
  emmeans(spec = pairwise ~ order, 
          type = "response")

fit.brm.df.exp1.made.lexical.children.order %>% 
  emmeans(spec = pairwise ~ order, 
          type = "response")

```





## PLOTS
### Response Plots
#### Cause
```{r message=FALSE, warning=FALSE}

df.model = df.exp1_cause_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "caused"))

fit.brm.distal.cause.age2 = brm(formula = distal ~ 1 + question*age + (1 | participant) + (1 | scenario),
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .9999),
                     file = "cache/fit.brm.distal.cause.age2")


fit.brm.proximal.cause.age2 = brm(formula = proximal ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 6000,
                     warmup = 1000,
                     control = list(adapt_delta = .9999),
                     file = "cache/fit.brm.proximal.cause.age2")

df.data = expand_grid(age = seq(4, 9, 0.1),
                      question = c("caused", "lexical"))

df.prediction = fit.brm.distal.cause.age2 %>% 
  fitted(newdata = df.data,
         re_formula = NA,
          probs = c(0.1, 0.9)) %>% 
  as_tibble() %>% 
  bind_cols(df.data) %>% 
  mutate(type = "distal") %>% 
  bind_rows(fit.brm.proximal.cause.age2 %>% 
              fitted(newdata = df.data,
                     re_formula = NA,
                     probs = c(0.1, 0.9)) %>% 
              as_tibble() %>% 
              bind_cols(df.data) %>% 
              mutate(type = "proximal")) %>% 
  clean_names()

df.adults = df.exp1_cause_adults %>% 
  select(-response) %>% 
  mutate(age_whole = rep(10)) %>% 
  pivot_longer(cols = (proximal:distal),
               names_to = "type",
               values_to = "response")

df.children = df.exp1_cause_children %>% 
  select(-response) %>% 
  pivot_longer(cols = distal:proximal,
               names_to = "type",
               values_to = "response")

df.means = df.children %>% 
  bind_rows(df.adults) %>% 
  mutate(age_whole = factor(age_whole, 
                            levels = c(4, 5, 6, 7, 8, 9, 10), 
                            labels = c("4", "5", "6", "7", "8", "9", "adults")),
         question = recode(question, "cause" = "caused")) %>% 
  group_by(age_whole, question, type) %>% 
  summarize(
    response = Hmisc::smean.cl.boot(response)) %>%
    mutate(index = c("response", "low", "high")) %>%
    ungroup() %>% 
    pivot_wider(names_from = index,
                values_from = response) %>% 
  mutate(age_whole = fct_recode(age_whole, "10" = "adults"),
         age_whole = as.numeric(as.character(age_whole)))


custom_labels = as_labeller(c("distal" = "Distal Cause", "proximal" = "Proximal Cause"))

p3 = ggplot(mapping = aes(x = age, 
                     y = response,
                     color = question)) + 
  geom_hline(yintercept=0.50, linetype="dashed", color = "black") +
  geom_smooth(data = df.prediction,
              mapping = aes(y = estimate,
                            ymin = q10,
                            ymax = q90,
                            color = question,
                            fill = question),
              stat = "identity",
              alpha = 0.2,
              show.legend = F) +
  geom_pointrange(data = df.means,
                  mapping = aes(x = age_whole,
                                y = response,
                                ymin = low,
                                ymax = high,
                                fill = question,
                                shape = question),
                  color = "black",
                  size = 0.5,
                  show.legend = TRUE,
                  alpha = 0.8,
                  position = position_dodge(width = 0.1)) +
    facet_wrap(~type,
             labeller = custom_labels) + 
  scale_fill_brewer(palette = "Set1") + 
  scale_color_brewer(palette = "Set1") +
  scale_shape_manual(values = c(21, 23)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                      labels = str_c(seq(0, 1, 0.25) * 100, "%")) +
  scale_x_continuous(breaks = 4:10,
                     labels = c("4", "5", "6", "7", "8", "9", "Adults")) +
  labs(y = "Probability of selecting \n causal candidate") +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        text = element_text(size = 18)) +
  guides(color = guide_legend(reverse = TRUE),
         fill = guide_legend(reverse = TRUE),
         shape = guide_legend(reverse = TRUE))




```

#### Made
```{r message=FALSE, warning=FALSE}


df.model = df.exp1_made_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "made"))


fit.brm.distal.age2.made = brm(formula = distal ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .9999),
                     file = "cache/fit.brm.distal.age2.made")


fit.brm.proximal.age2.made = brm(formula = proximal ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .9999),
                     file = "cache/fit.brm.proximal.age2.made")

df.data = expand_grid(age = seq(4, 9, 0.1),
                      question = c("made", "lexical"))

df.prediction = fit.brm.distal.age2.made %>% 
  fitted(newdata = df.data,
         re_formula = NA,
          probs = c(0.1, 0.9)) %>% 
  as_tibble() %>% 
  bind_cols(df.data) %>% 
  mutate(type = "distal") %>% 
  bind_rows(fit.brm.proximal.age2.made %>% 
              fitted(newdata = df.data,
                     re_formula = NA,
                     probs = c(0.1, 0.9)) %>% 
              as_tibble() %>% 
              bind_cols(df.data) %>% 
              mutate(type = "proximal")) %>% 
  clean_names()

df.adults = df.exp1_made_adults %>% 
  select(-response) %>% 
  mutate(age_whole = rep(10)) %>% 
  pivot_longer(cols = (proximal:distal),
               names_to = "type",
               values_to = "response")

df.children = df.exp1_made_children %>% 
  select(-response) %>% 
  pivot_longer(cols = distal:proximal,
               names_to = "type",
               values_to = "response")

df.means = df.children %>% 
  bind_rows(df.adults) %>% 
  mutate(age_whole = factor(age_whole, 
                            levels = c(4, 5, 6, 7, 8, 9, 10), 
                            labels = c("4", "5", "6", "7", "8", "9", "adults"))) %>% 
  group_by(age_whole, question, type) %>% 
  summarize(
    response = Hmisc::smean.cl.boot(response)) %>%
    mutate(index = c("response", "low", "high")) %>%
    ungroup() %>% 
    pivot_wider(names_from = index,
                values_from = response) %>% 
  mutate(age_whole = fct_recode(age_whole, "10" = "adults"),
         age_whole = as.numeric(as.character(age_whole)))

custom_labels = as_labeller(c("distal" = "Distal Cause", "proximal" = "Proximal Cause"))

df.means = df.means %>%
  mutate(question = factor(question, levels = c("made", "lexical")))

p4 = ggplot(mapping = aes(x = age, 
                     y = response,
                     color = question)) + 
  geom_hline(yintercept=0.50, linetype="dashed", color = "black") +
  geom_smooth(data = df.prediction,
              mapping = aes(y = estimate,
                            ymin = q10,
                            ymax = q90,
                            color = question,
                            fill = question),
              stat = "identity",
              alpha = 0.2,
              show.legend = F) +
  geom_pointrange(data = df.means,
                  mapping = aes(x = age_whole,
                                y = response,
                                ymin = low,
                                ymax = high,
                                fill = question,
                                shape = question),
                  color = "black",
                  size = 0.5,
                  show.legend = TRUE,
                  alpha = 0.8,
                  position = position_dodge(width = 0.3)) +
  facet_wrap(~type,
             labeller = custom_labels) + 
  scale_fill_manual(values = c("made" = "#4DAF4A", "lexical" = "#377EB8"), breaks=c("made", "lexical")) +
  scale_color_manual(values = c("made" = "#4DAF4A", "lexical" = "#377EB8"), breaks=c("made", "lexical")) +
  scale_shape_manual(values = c(21, 23), breaks=c("made", "lexical")) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = str_c(seq(0, 1, 0.25) * 100, "%"),
                     limits = c(0, 1)) +
  scale_x_continuous(breaks = 4:10,
                     labels = c("4", "5", "6", "7", "8", "9", "Adults")) +
  labs(y = "Probability of selecting \n causal candidate") + 
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        text = element_text(size = 18)) 

  
```

#### Combine Cause and Made Plots
```{r fig.height=5, fig.width=18, message=FALSE, warning=FALSE}

plot = p3 + p4 + 
plot_layout(nrow = 1) &
plot_annotation(tag_levels = "A") &
theme(plot.tag = element_text(face = "bold"))

ggsave(plot, filename = "../../figures/experiment1/chain_all.pdf", height = 5, width = 18)

plot


```

### Order Effects 
#### Cause v Lexical

```{r fig.height=4, fig.width=6, message=FALSE, warning=FALSE}

df.plot = df.exp1_cause_children_order %>% 
  bind_rows(df.exp1_cause_lexical_children_order) %>% 
  mutate(order = factor(order, levels = c("first", "second")))



p3 = ggplot(data = df.plot,
       mapping = aes(x = factor(question, levels = c("lexical", "caused")),
                     y = difference,
                     color = order,
                     fill = order)) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
   stat_summary(fun.data = "mean_cl_boot",
               position = position_dodge(width = 0.5),
               shape = 21,
               color = "black",
               size = 1) +
  scale_fill_brewer(palette = "Set3") +
  scale_color_brewer(palette = "Set3") +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = c("100% \n proximal", "75%", "50%", "75%", "100% \n distal"),
                      limits = c(0, 1)) +
  ylab("Probability of selecting \n proximal or distal cause") +
  theme(legend.position = "bottom",
        legend.box = "vertical",
        axis.title.x = element_blank(),
        text = element_text(size = 18)) 



```

#### Made v Lexical

```{r fig.height=4, fig.width=8, message=FALSE, warning=FALSE}

df.plot = df.exp1_made_children_order %>% 
  bind_rows(df.exp1_made_lexical_children_order) %>% 
  mutate(order = factor(order, levels = c("first", "second")))



p4 = ggplot(data = df.plot,
       mapping = aes(x = factor(question, levels = c("lexical", "made")),
                     y = difference,
                     color = order,
                     fill = order)) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
   stat_summary(fun.data = "mean_cl_boot",
               position = position_dodge(width = 0.5),
               shape = 21,
               color = "black",
               size = 1) +
  scale_fill_brewer(palette = "Set3") +
  scale_color_brewer(palette = "Set3") +
   scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = c("100% \n proximal", "75%", "50%", "75%", "100% \n distal"),
                      limits = c(0, 1)) +
  ylab("Probability of selecting \n proximal or distal cause") +
  theme(legend.position = "bottom",
        legend.box = "vertical",
        axis.title.x = element_blank(),
        text = element_text(size = 18)) 


```

#### Combine Cause and Made Plots
```{r fig.height=5, fig.width=12, message=FALSE, warning=FALSE}

plot = p3 + p4 + 
plot_layout(nrow = 1) &
plot_annotation(tag_levels = "A") &
theme(plot.tag = element_text(face = "bold"))

ggsave(plot, filename = "../../figures/experiment1/chain_order_effect.pdf", height = 5, width = 12)

plot


```


# EXPERIMENT 2: ABSENCES
## CAUSE V LEXICAL (BURN & FLOOD)
### ADULTS
#### STATS
##### Bayesian Models
###### Direct

```{r message=FALSE, warning=FALSE}

df.model = df.exp2_cause_adults  %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "cause"))

# Check contrast values
 contrasts(df.model$question)

fit.brm.direct = brm(formula = direct ~ 1 + question + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_adult_direct") 
fit.brm.direct

```

###### Absent
```{r}

fit.brm.absent = brm(formula = absence ~ 1 + question + (1 | participant) + (1 | scenario),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/cause_adult_absent") 

fit.brm.absent

```

### CHILDREN
#### STATS

##### Bayesian Models
###### Direct
```{r message=FALSE, warning=FALSE}

df.model = df.exp2_cause_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "caused"),
         age = age - mean(age))

# Check contrast values
 contrasts(df.model$question)

fit.brm.direct = brm(formula = direct ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_children_direct") 
fit.brm.direct

```

###### Absent
```{r message=FALSE, warning=FALSE}

# removed random intercepts for scenario to avoid divergent transition errors
fit.brm.absent = brm(formula = absence ~ 1 + question*age + (1 | participant),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/cause_children_absent") 


fit.brm.absent

```

## MADE V LEXICAL (BURN & FLOOD)
### ADULTS
##### Bayesian Models
###### Direct

```{r}

df.model = df.exp2_made_adults %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "made"))

# Check contrast values
 contrasts(df.model$question)

fit.brm.direct = brm(formula = direct ~ 1 + question + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/made_adult_direct") 
fit.brm.direct

```

###### Absent

```{r}

fit.brm.absent = brm(formula = absence ~ 1 + question + (1 | participant) + (1 | scenario),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/made_adult_absent") 

fit.brm.absent

```

### CHILDREN
#### STATS
##### Bayesian Models
###### Direct

```{r message=FALSE, warning=FALSE}

df.model = df.exp2_made_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "made"),
         age = age - mean(age)) 

# Check contrast values
 contrasts(df.model$question)

fit.brm.direct = brm(formula = direct ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/made_children_direct") 
fit.brm.direct

```

###### Absent
```{r message=FALSE, warning=FALSE}

# removed random intercepts for scenario to avoid divergent transition errors
fit.brm.absent = brm(formula = absence ~ 1 + question*age + (1 | participant),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/made_children_absent") 


fit.brm.absent

```

## CAUSE v MADE
### ADULTS
#### DATA
##### Wrangle

```{r message=FALSE, warning=FALSE}

df.exp2_cause_made_adults = df.exp2_cause_adults %>% 
  filter(question == "caused") %>% 
  select(-participant) %>% 
  bind_rows(df.exp2_made_adults %>% 
  filter(question == "made") %>% 
  select(-participant)) %>% 
  mutate(participant = rep(1:(n()/2), each = 2))


```

#### STATS

##### Bayesian Models
###### Direct

```{r message=FALSE, warning=FALSE}

df.model = df.exp2_cause_made_adults %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "made"))

# Check contrast values
 contrasts(df.model$question)


fit.brm.cause.made.adult.direct = brm(formula = direct ~ 1 + question + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_made_adult_direct") 

fit.brm.cause.made.adult.direct



```

###### Absent

```{r message=FALSE, warning=FALSE}

fit.brm.cause.made.adult.absent = brm(formula = absence ~ 1 + question + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_made_adult_absence") 

fit.brm.cause.made.adult.absent

```

### CHILDREN
#### DATA
##### Wrangle

```{r message=FALSE, warning=FALSE}

df.exp2_cause_made_children = df.exp2_cause_children %>% 
  filter(question == "caused") %>% 
  select(-cause_question_order, participant) %>% 
  bind_rows(df.exp2_made_children %>% 
  filter(question == "made") %>% 
  select(-made_question_order, participant)) %>% 
  mutate(participant = rep(1:(n()/2), each = 2))


```

#### STATS

##### Bayesian Models
###### Direct

```{r message=FALSE, warning=FALSE}

df.model = df.exp2_cause_made_children %>% 
  mutate(question = fct_relevel(question, "made"),
         age = age - mean(age))

# Check contrast values
 contrasts(df.model$question)



fit.brm.cause.made.children.direct = brm(formula = direct ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_made_children_direct.rds") 

fit.brm.cause.made.children.direct


```

###### Absent

```{r message=FALSE, warning=FALSE}


fit.brm.cause.made.children.absent = brm(formula = absence ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_made_children_absence.rds") 

fit.brm.cause.made.children.absent


```
## ORDER EFFECTS
### ADULTS
#### DATA
##### Wrangle

```{r}

# code order
df.tmp = df.exp2_cause_adults %>% 
  group_by(participant) %>% 
  filter(row_number() == 1) %>% 
  mutate(scenario_order = str_c(scenario, "_first"),
         question_order = str_c(question, "_first")) %>% 
  select(participant,
         contains("order"))

df.exp2_cause_adults_order = df.exp2_cause_adults %>% 
  left_join(df.tmp,
            by = "participant") %>% 
  relocate(contains("order"), .after = question) %>% 
  mutate(caused_question_order = case_when(question_order == "lexical_first" ~ "second",
                                          question_order == "caused_first" ~ "first"),
         question = as_factor(question),
         question = fct_relevel(question, "lexical"),
         caused_question_order = as_factor(caused_question_order),
         caused_question_order = fct_relevel(caused_question_order, "first")) %>% 
   group_by(participant) %>%
   filter(row_number() <= 2) %>%
  ungroup()

df.tmp = df.exp2_cause_adults_order %>% 
  filter(question == "caused") %>% 
  mutate(order = caused_question_order)

df.tmp2 = df.exp2_cause_adults_order %>% 
  filter(question == "lexical") %>% 
  mutate(order = case_when(caused_question_order == "second" ~ "first",
                           caused_question_order == "first" ~ "second"))

df.exp2_cause_adults_order = df.tmp %>% 
  bind_rows(df.tmp2) %>% 
  mutate(order = as_factor(order),
         order = fct_relevel(order, "second"),
         difference = absence - direct,
         difference = recode(difference, `-1` = 0))


# code order
df.tmp = df.exp2_made_adults %>% 
  group_by(participant) %>% 
  filter(row_number() == 1) %>% 
  mutate(scenario_order = str_c(scenario, "_first"),
         question_order = str_c(question, "_first")) %>% 
  select(participant,
         contains("order"))

df.exp2_made_adults_order = df.exp2_made_adults %>% 
  left_join(df.tmp,
            by = "participant") %>% 
  relocate(contains("order"), .after = question) %>% 
  mutate(made_question_order = case_when(question_order == "lexical_first" ~ "second",
                                          question_order == "made_first" ~ "first"),
         question = as_factor(question),
         question = fct_relevel(question, "lexical"),
         made_question_order = as_factor(made_question_order),
         made_question_order = fct_relevel(made_question_order, "first")) %>% 
   group_by(participant) %>%
   filter(row_number() <= 2) %>%
  ungroup()

df.tmp = df.exp2_made_adults_order %>% 
  filter(question == "made") %>% 
  mutate(order = made_question_order)

df.tmp2 = df.exp2_made_adults_order %>% 
  filter(question == "lexical") %>% 
  mutate(order = case_when(made_question_order == "second" ~ "first",
                           made_question_order == "first" ~ "second"))

df.exp2_made_adults_order = df.tmp %>% 
  bind_rows(df.tmp2) %>% 
  mutate(order = as_factor(order),
         order = fct_relevel(order, "second"),
         difference = absence - direct,
         difference = recode(difference, `-1` = 0))

```

#### STATS

##### Bayesian Models

```{r message=FALSE, warning=FALSE}



# Check contrast values
contrasts(df.exp2_cause_adults_order$order)

fit.brm.df.exp2.cause.adults.order = brm(formula = difference ~ 1 + question*order + (1 | participant) + (1 | scenario), 
                     data = df.exp2_cause_adults_order,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     file = "cache/exp2_cause_adults_order") 

fit.brm.df.exp2.cause.adults.order



# Check contrast values
contrasts(df.exp2_made_adults_order$order)


fit.brm.df.exp2.made.adults.order = brm(formula = difference ~ 1 + question*order + (1 | participant) + (1 | scenario), 
                     data = df.exp2_made_adults_order,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     file = "cache/exp2_made_adults_order") 

fit.brm.df.exp2.made.adults.order


```

##### Follow-up analysis 

```{r}

fit.brm.df.exp2.cause.adults.order%>% 
  emmeans(spec = pairwise ~ order | question, 
          type = "response")

fit.brm.df.exp2.made.adults.order%>% 
  emmeans(spec = pairwise ~ order | question, 
          type = "response")
```

### CHILDREN
#### DATA
##### Wrangle

```{r}

df.tmp = df.exp2_cause_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "lexical"),
         order = as_factor(cause_question_order),
         order = fct_relevel(order, "second")) %>% 
   group_by(participant) %>%
   filter(row_number() <= 2) %>%
  ungroup()  %>% 
  filter(question == "caused") %>% 
  mutate(difference = absence - direct,
         difference = recode(difference, `-1` = 0))

df.tmp2 = df.exp2_cause_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "lexical"),
         order = as_factor(cause_question_order),
         order = fct_relevel(order, "second"),
         order = str_replace_all(order, "first", "temp_placeholder"),
         order = str_replace_all(order, "second", "first"),
         order = str_replace_all(order, "temp_placeholder", "second"),
         order = as_factor(order),
         order = fct_relevel(order, "second")) %>% 
  group_by(participant) %>%
  filter(row_number() <= 2) %>%
  ungroup() %>% 
  filter(question == "lexical") %>% 
  mutate(difference = absence - direct,
         difference = recode(difference, `-1` = 0))

df.exp2_cause_children_order = df.tmp %>% 
  bind_rows(df.tmp2)



df.tmp = df.exp2_made_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "lexical"),
         order = as_factor(made_question_order),
         order = fct_relevel(order, "second")) %>% 
   group_by(participant) %>%
   filter(row_number() <= 2) %>%
  ungroup()  %>% 
  filter(question == "made") %>% 
  mutate(difference = absence - direct,
         difference = recode(difference, `-1` = 0))

df.tmp2 = df.exp2_made_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "lexical"),
         order = as_factor(made_question_order),
         order = fct_relevel(order, "second"),
         order = str_replace_all(order, "first", "temp_placeholder"),
         order = str_replace_all(order, "second", "first"),
         order = str_replace_all(order, "temp_placeholder", "second"),
         order = as_factor(order),
         order = fct_relevel(order, "second")) %>% 
  group_by(participant) %>%
  filter(row_number() <= 2) %>%
  ungroup() %>% 
  filter(question == "lexical") %>% 
  mutate(difference = absence - direct,
         difference = recode(difference, `-1` = 0))

df.exp2_made_children_order = df.tmp %>% 
  bind_rows(df.tmp2) %>% 
  mutate(order = str_replace_all(order, "frst", "first"),
         order = str_replace_all(order, "scond", "second"),
         order = as_factor(order),
         order = fct_relevel(order, "second"))


```

#### STATS

##### Bayesian Models

```{r message=FALSE, warning=FALSE}



# Check contrast values
contrasts(df.exp2_cause_children_order$order)

fit.brm.df.exp2.cause.children.order = brm(formula = difference ~ 1 + question*order + (1 | participant) + (1 | scenario), 
                     data = df.exp2_cause_adults_order,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     file = "cache/exp2_cause_children_order") 

fit.brm.df.exp2.cause.children.order



# Check contrast values
contrasts(df.exp2_made_children_order$order)


fit.brm.df.exp2.made.children.order = brm(formula = difference ~ 1 + question*order + (1 | participant) + (1 | scenario), 
                     data = df.exp2_made_adults_order,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     file = "cache/exp2_made_children_order") 

fit.brm.df.exp2.made.children.order


```

##### Follow-up analysis 

```{r}

fit.brm.df.exp2.cause.children.order %>% 
  emmeans(spec = pairwise ~ order | question, 
          type = "response")

fit.brm.df.exp2.made.children.order %>% 
  emmeans(spec = pairwise ~ order | question, 
          type = "response")
```

## PLOTS
### Response Plots
#### Cause
```{r message=FALSE, warning=FALSE}

df.model = df.exp2_cause_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "caused"))

# removed random intercepts for scenario to avoid divergent transition errors
fit.brm.present.cause.age2 = brm(formula = direct ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 6000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999,
                                    max_treedepth = 15),
                     file = "cache/fit.brm.present.cause.age2") 



fit.brm.absence.cause.age2 = brm(formula = absence ~ 1 + question*age + (1 | participant) + (1 | scenario),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 6000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999,
                                     max_treedepth = 15),
                      file = "cache/fit.brm.absence.cause.age2") 



df.data = expand_grid(age = seq(4, 9, 0.1),
                      question = c("caused", "lexical"))

df.prediction = fit.brm.present.cause.age2 %>% 
  fitted(newdata = df.data,
         re_formula = NA,
          probs = c(0.1, 0.9)) %>% 
  as_tibble() %>% 
  bind_cols(df.data) %>% 
  mutate(type = "presence") %>% 
  bind_rows(fit.brm.absence.cause.age2 %>% 
              fitted(newdata = df.data,
                     re_formula = NA,
                     probs = c(0.1, 0.9)) %>% 
              as_tibble() %>% 
              bind_cols(df.data) %>% 
              mutate(type = "absence")) %>% 
  clean_names()

df.adults = df.exp2_cause_adults %>% 
  select(-response) %>% 
  mutate(age_whole = rep(10)) %>% 
  pivot_longer(cols = (direct:absence),
    names_to = "type",
    values_to = "response")



df.children = df.exp2_cause_children%>%
  select(-response) %>% 
 pivot_longer(cols = (direct:absence),
               names_to = "type",
               values_to = "response")

df.means = df.children %>% 
  bind_rows(df.adults) %>% 
  mutate(age_whole = factor(age_whole, 
                            levels = c(4, 5, 6, 7, 8, 9, 10), 
                            labels = c("4", "5", "6", "7", "8", "9", "adults")),
         question = recode(question, "cause" = "caused"),
         type = recode(type, "direct" = "presence")) %>% 
  group_by(age_whole, question, type) %>% 
  summarize(
    response = Hmisc::smean.cl.boot(response)) %>%
    mutate(index = c("response", "low", "high")) %>%
    ungroup() %>% 
    pivot_wider(names_from = index,
                values_from = response) %>% 
  mutate(age_whole = fct_recode(age_whole, "10" = "adults"),
         age_whole = as.numeric(as.character(age_whole)))



custom_labels = as_labeller(c("absence" = "Absent Cause", "presence" = "Direct Cause"))

p7 = ggplot(mapping = aes(x = age, 
                     y = response,
                     color = question)) + 
  geom_hline(yintercept=0.50, linetype="dashed", color = "black") +
  geom_smooth(data = df.prediction,
              mapping = aes(y = estimate,
                            ymin = q10,
                            ymax = q90,
                            color = question,
                            fill = question),
              stat = "identity",
              alpha = 0.2,
              show.legend = F) +
  geom_pointrange(data = df.means,
                  mapping = aes(x = age_whole,
                                y = response,
                                ymin = low,
                                ymax = high,
                                fill = question,
                                shape = question),
                  color = "black",
                  size = 0.5,
                  show.legend = TRUE,
                  alpha = 0.8,
                  position = position_dodge(width = 0.5)) +
    facet_wrap(~type,
             labeller = custom_labels) + 
  scale_fill_brewer(palette = "Set1") + 
  scale_color_brewer(palette = "Set1") +
  scale_shape_manual(values = c(21, 23)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                      labels = str_c(seq(0, 1, 0.25) * 100, "%")) +
  scale_x_continuous(breaks = 4:10,
                     labels = c("4", "5", "6", "7", "8", "9", "Adults")) +
  labs(y = "Probability of selecting \n causal candidate") +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        text = element_text(size = 18)) +
  guides(color = guide_legend(reverse = TRUE),
         fill = guide_legend(reverse = TRUE),
         shape = guide_legend(reverse = TRUE))

  
```

#### Made

```{r message=FALSE, warning=FALSE}

df.model = df.exp2_made_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "made"))


fit.brm.present.made.age2 = brm(formula = direct ~ 1 + question*age + (1 | participant) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 8000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999,
                                    max_treedepth = 15),
                     file = "cache/fit.brm.present.made.age2") 



fit.brm.absence.made.age2 = brm(formula = absence ~ 1 + question*age + (1 | participant) + (1 | scenario),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 6000,
                      control = list(adapt_delta = .999999,
                                     max_treedepth = 15),
                      file = "cache/fit.brm.absence.made.age2") 



df.data = expand_grid(age = seq(4, 9, 0.1),
                      question = c("made", "lexical"))

df.prediction = fit.brm.present.made.age2 %>% 
  fitted(newdata = df.data,
         re_formula = NA,
          probs = c(0.1, 0.9)) %>% 
  as_tibble() %>% 
  bind_cols(df.data) %>% 
  mutate(type = "presence") %>% 
  bind_rows(fit.brm.absence.made.age2 %>% 
              fitted(newdata = df.data,
                     re_formula = NA,
                     probs = c(0.1, 0.9)) %>% 
              as_tibble() %>% 
              bind_cols(df.data) %>% 
              mutate(type = "absence")) %>% 
  clean_names()

df.adults = df.exp2_made_adults %>% 
  select(-response) %>% 
  mutate(age_whole = rep(10)) %>% 
  pivot_longer(cols = (direct:absence),
    names_to = "type",
    values_to = "response")


df.children = df.exp2_made_children %>%
  select(-response) %>% 
  pivot_longer(cols = (direct:absence),
               names_to = "type",
               values_to = "response")

df.means = df.children %>% 
  mutate(age_whole = as.integer(age)) %>%
  bind_rows(df.adults) %>% 
  mutate(age_whole = factor(age_whole, 
                            levels = c(4, 5, 6, 7, 8, 9, 10), 
                            labels = c("4", "5", "6", "7", "8", "9", "adults")),
         type = recode(type, "direct" = "presence")) %>% 
  group_by(age_whole, question, type) %>% 
  summarize(
    response = Hmisc::smean.cl.boot(response)) %>%
    mutate(index = c("response", "low", "high")) %>%
    ungroup() %>% 
    pivot_wider(names_from = index,
                values_from = response) %>% 
  mutate(age_whole = fct_recode(age_whole, "10" = "adults"),
         age_whole = as.numeric(as.character(age_whole)),
         question = factor(question, levels = c("made", "lexical")))


custom_labels = as_labeller(c("absence" = "Absent Cause", "presence" = "Direct Cause"))


p8 = ggplot(mapping = aes(x = age, 
                     y = response,
                     color = question)) + 
  geom_hline(yintercept=0.50, linetype="dashed", color = "black") +
  geom_smooth(data = df.prediction,
              mapping = aes(y = estimate,
                            ymin = q10,
                            ymax = q90,
                            color = question,
                            fill = question),
              stat = "identity",
              alpha = 0.2,
              show.legend = F) +
  geom_pointrange(data = df.means,
                  mapping = aes(x = age_whole,
                                y = response,
                                ymin = low,
                                ymax = high,
                                fill = question,
                                shape = question),
                  color = "black",
                  size = 0.5,
                  show.legend = TRUE,
                  alpha = 0.8,
                  position = position_dodge(width = 0.4)) +
  facet_wrap(~type,
             labeller = custom_labels) + 
  scale_fill_manual(values = c("made" = "#4DAF4A", "lexical" = "#377EB8"), breaks=c("made", "lexical")) +
  scale_color_manual(values = c("made" = "#4DAF4A", "lexical" = "#377EB8"), breaks=c("made", "lexical")) +
  scale_shape_manual(values = c(21, 23), breaks=c("made", "lexical")) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = str_c(seq(0, 1, 0.25) * 100, "%"),
                     limits = c(0, 1)) +
  scale_x_continuous(breaks = 4:10,
                     labels = c("4", "5", "6", "7", "8", "9", "Adults")) +
  labs(y = "Probability of selecting \n causal candidate") +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        text = element_text(size = 18)) 


```

#### Combine Cause and Made Plots

```{r fig.height=5, fig.width=18, message=FALSE, warning=FALSE}

plot = p7 + p8 + 
plot_layout(nrow = 1) &
plot_annotation(tag_levels = "A") &
theme(plot.tag = element_text(face = "bold"))

ggsave(plot, filename = "../../figures/experiment2/absence_all.pdf", height = 5, width = 18)

plot


```

### Order Effects 
#### Cause v Lexical

```{r fig.height=4, fig.width=6, message=FALSE, warning=FALSE}

df.plot = df.exp2_cause_children_order %>% 
  mutate(age = "children") %>% 
  bind_rows(df.exp2_cause_adults_order %>% 
              mutate(age = "adults")) %>% 
  mutate(order = factor(order, levels = c("first", "second")))



p5 = ggplot(data = df.plot,
       mapping = aes(x = factor(question, levels = c("lexical", "caused")),
                     y = difference,
                     color = order,
                     fill = order)) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
   stat_summary(fun.data = "mean_cl_boot",
               position = position_dodge(width = 0.5),
               shape = 21,
               color = "black",
               size = 1) +
  scale_fill_brewer(palette = "Set3") +
  scale_color_brewer(palette = "Set3") +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = c("100% \n direct", "75%", "50%", "75%", "100% \n absent"),
                      limits = c(0, 1)) +
  ylab("Probability of selecting \n direct or absent cause") +
  theme(legend.position = "bottom",
        legend.box = "vertical",
        axis.title.x = element_blank(),
        text = element_text(size = 18)) +
  facet_wrap(~age)



```

#### Made v Lexical

```{r fig.height=4, fig.width=8, message=FALSE, warning=FALSE}

df.plot = df.exp2_made_children_order %>% 
  mutate(age = "children") %>% 
  bind_rows(df.exp2_made_adults_order %>% 
              mutate(age = "adults")) %>% 
  mutate(order = factor(order, levels = c("first", "second")))



p6 = ggplot(data = df.plot,
       mapping = aes(x = factor(question, levels = c("lexical", "made")),
                     y = difference,
                     color = order,
                     fill = order)) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
   stat_summary(fun.data = "mean_cl_boot",
               position = position_dodge(width = 0.5),
               shape = 21,
               color = "black",
               size = 1) +
  scale_fill_brewer(palette = "Set3") +
  scale_color_brewer(palette = "Set3") +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = c("100% \n direct", "75%", "50%", "75%", "100% \n absent"),
                      limits = c(0, 1)) +
  ylab("Probability of selecting \n direct or absent cause") +
  theme(legend.position = "bottom",
        legend.box = "vertical",
        axis.title.x = element_blank(),
        text = element_text(size = 18)) +
  facet_wrap(~age)


```

#### Combine Cause and Made Plots
```{r fig.height=5, fig.width=12, message=FALSE, warning=FALSE}

plot = p5 + p6 + 
plot_layout(nrow = 1) &
plot_annotation(tag_levels = "A") &
theme(plot.tag = element_text(face = "bold"))

ggsave(plot, filename = "../../figures/experiment2/absence_order_effect.pdf", height = 5, width = 12)

plot


```


# SESSION INFO
```{r}

sessionInfo()

```
