---
title: "RSA model of causal verbs"
author: "David Rose, Siying Zhang, Shaun Nichols, Ellen Markman & Tobias Gerstenberg"
date: "`r Sys.Date()`"
output: html_document
---

# Load Packages

```{r}
library("patchwork")
library("kableExtra")
library("boot")
library("patchwork")
library("rsample")
library("latex2exp")
library("tidyverse")
```

# Helper functions

```{r}
# softmax function
softmax = function(x, beta = 1) {
  return(exp(x * beta) / sum(exp(x * beta)))
}

# set the theme 
theme_set(theme_classic() + 
    theme(text = element_text(size = 24)))

# function for printing out html or latex tables 
print_table = function(data, format = "html", digits = 2){
  if(format == "html"){
    data %>% 
      kable(digits = digits) %>% 
      kable_styling()
  }else if(format == "latex"){
    data %>% 
      xtable(digits = digits,
             caption = "Caption",
             label = "tab:table") %>%
      print(include.rownames = F,
            booktabs = T,
            sanitize.colnames.function = identity,
            caption.placement = "top")
  }
}

# suppress grouping warning 
options(dplyr.summarise.inform = F)
```

# DATA

## Chain

### Caused vs. lexical 

```{r}
df.chain_caused = read.csv("../../data/experiment1/cause/children/chain_cause_different_responses.csv") %>% 
  count(age_whole, question, distal) %>% 
  group_by(age_whole, question) %>%
  mutate(probability = n/sum(n)) %>%
  ungroup() %>% 
  mutate(distal = factor(distal,
                         levels = c(0, 1),
                         labels = c("no", "yes"))) %>% 
  select(-n) %>% 
  relocate(probability, .after = last_col()) %>% 
  arrange(age_whole, question, distal) %>% 
  mutate(version = rep("chain")) %>% 
  rename(age = age_whole) %>% 
  mutate(event = ifelse(distal == "yes", "distal", "proximal"),
         alternative = "caused") %>%
  select(age, question, event, probability, version, -distal, alternative)
```

### Made vs. lexical 

```{r}
df.chain_made = read.csv("../../data/experiment1/made/children/chain_made_different_responses.csv") %>% 
  count(age_whole, question, distal) %>% 
  group_by(age_whole, question) %>%
  mutate(probability = n/sum(n)) %>%
  ungroup() %>% 
  mutate(distal = factor(distal,
                         levels = c(0, 1),
                         labels = c("no", "yes"))) %>% 
  select(-n) %>% 
  relocate(probability, .after = last_col()) %>% 
  arrange(age_whole, question, distal) %>% 
  mutate(version = rep("chain")) %>% 
  rename(age = age_whole) %>% 
  mutate(event = ifelse(distal == "yes", "distal", "proximal"),
         alternative = "made") %>% 
  select(age, question, event, probability, version, -distal, alternative)
```

## Omission

### Caused vs. lexical

```{r}
df.omission_caused = read.csv("../../data/experiment2/cause/children/absence_cause_different_responses.csv") %>% 
  rename(absent = absence) %>% 
  count(age_whole, question, absent) %>% 
  group_by(age_whole, question) %>%
  mutate(probability = n/sum(n)) %>%
  ungroup() %>% 
  mutate(absent = factor(absent,
                         levels = c(0, 1),
                         labels = c("no", "yes"))) %>% 
  select(-n) %>% 
  relocate(probability, .after = last_col()) %>% 
  arrange(age_whole, question, absent) %>% 
  mutate(version = "omission") %>% 
  rename(age = age_whole) %>% 
  mutate(event = ifelse(absent == "yes", "absent", "direct"),
         alternative = "caused") %>% 
  select(age, question, event, probability, version, -absent, alternative)
```

### Made vs. lexical

```{r}
df.omission_made = read.csv("../../data/experiment2/made/children/absence_made_different_responses.csv") %>% 
  rename(absent = absence) %>% 
  mutate(age_whole = as.integer(age)) %>% 
  count(age_whole, question, absent) %>% 
  group_by(age_whole, question) %>%
  mutate(probability = n/sum(n)) %>%
  ungroup() %>% 
  mutate(absent = factor(absent,
                         levels = c(0, 1),
                         labels = c("no", "yes"))) %>% 
  select(-n) %>% 
  relocate(probability, .after = last_col()) %>% 
  arrange(age_whole, question, absent) %>% 
  mutate(version = "omission") %>% 
  rename(age = age_whole) %>% 
  mutate(event = ifelse(absent == "yes", "absent", "direct"),
         alternative = "made") %>% 
  select(age, question, event, probability, version, -absent, alternative)
```

## Bootstrapped confidence intervals 

```{r}
fun_bootstraps = function(df, variable, scenario, alternative, nboots){
  df = df %>% 
    bootstraps(times = nboots,
               strata = age_whole) %>% 
    mutate(probability = map(.x = splits,
                             .f = ~ .x %>%
                               as_tibble() %>%
                               count(age_whole, question, {{variable}}, .drop = FALSE) %>% 
                               group_by(age_whole, question) %>%
                               mutate(probability = n/sum(n)))) %>%
    select(-splits) %>%
    unnest(cols = c(probability)) %>% 
    group_by(age_whole, question, {{variable}}) %>%
    summarize(low = quantile(probability, 0.025),
              high = quantile(probability, 0.975)) %>% 
    ungroup()
  
  if (scenario == "chain"){
    df = df %>% 
      mutate(event = factor({{variable}},
                             levels = c(0, 1),
                             labels = c("proximal", "distal")))
  }
  
  if (scenario == "omission"){
    df = df %>% 
      mutate(event = factor({{variable}},
                             levels = c(0, 1),
                             labels = c("direct", "absent"))) 
  }
  
  df = df %>% 
    select(-{{variable}}) %>% 
      mutate(version = scenario,
             alternative = alternative)

  return(df)
}

nboots = 100

df.boot = bind_rows(
  fun_bootstraps(df = read.csv("../../data/experiment1/cause/children/chain_cause_different_responses.csv"),
                 variable = distal,
                 scenario = "chain",
                 alternative = "caused",
                 nboots = nboots),
  fun_bootstraps(df = read.csv("../../data/experiment1/made/children/chain_made_different_responses.csv"),
                 variable = distal,
                 scenario = "chain",
                 alternative = "made",
                 nboots = nboots),
  fun_bootstraps(df = read.csv("../../data/experiment2/cause/children/absence_cause_different_responses.csv"),
                 variable = absence,
                 scenario = "omission",
                 alternative = "caused",
                 nboots = nboots),
  fun_bootstraps(df = read.csv("../../data/experiment2/made/children/absence_made_different_responses.csv") %>% 
                   mutate(age_whole = as.integer(age)),
                 variable = absence,
                 scenario = "omission",
                 alternative = "made",
                 nboots = nboots)) %>% 
  rename(age = age_whole)
```

## Combined data 

```{r}
df.data = bind_rows(df.chain_caused, 
                    df.chain_made, 
                    df.omission_caused,
                    df.omission_made) %>% 
  left_join(df.boot,
            by = c("age", "question", "event", "version", "alternative")) %>% 
  mutate(alternative = factor(alternative, levels = c("caused", "made")),
         question = factor(question, levels = c("lexical", "caused", "made")),
         event = factor(event, levels = c("proximal", "distal", "direct", "absent")),
         event = ifelse(event %in% c("proximal", "direct"), "prototypical", "nonstandard"),
         event = factor(event, levels = c("prototypical", "nonstandard")),
         version = factor(version, levels = c("chain", "omission"))) %>%
  relocate(probability, .after = alternative) %>% 
  arrange(version, age, question, event, alternative)
```

# MODEL

## Helper functions

### Listener and speaker functions

```{r}
fun.l0 = function(prior){
  l0 = tibble(question = c("lexical", "alternative"),
              prototypical = c(1, 1),
              nonstandard = c(0, 1)) %>% 
    pivot_longer(cols = -question,
                 names_to = "event",
                 values_to = "value") %>% 
    # add prior
    mutate(prior = ifelse(event == "prototypical", prior["prototypical"], prior["nonstandard"]),
           value = value * prior) %>%
    group_by(question) %>%
    mutate(value = value/sum(value)) %>%
    ungroup()
  return(l0)
}

fun.s1 = function(l0, cost, beta){
  s1 = l0 %>% 
    select(-prior) %>%
    group_by(event) %>% 
    mutate(cost = ifelse(question == "lexical", 0, cost),
           value = ifelse(value == 0, 0.001, value),
           value = ifelse(value == 1, 0.999, value),
           value = log(value) - cost,
           value = softmax(value, beta = beta)) %>%
    ungroup()
  return(s1)
}

fun.l1 = function(s1, prior){
  l1 = s1 %>%
    mutate(prior = ifelse(event == "prototypical", prior["prototypical"], prior["nonstandard"]), 
           value = value * prior) %>%
    group_by(question) %>% 
    mutate(value = value/sum(value)) %>% 
    ungroup()
  return(l1)
}

fun.fit = function(par, data, fun_model){
  loss = data %>%
    group_by(age) %>%
    nest() %>%
    mutate(prediction = list(fun_model(par = par,
                                       age = age))) %>%
    unnest(c(data, prediction),
           names_sep = "_") %>%
    ungroup() %>%
    summarize(loss = sum((data_probability - prediction_value)^2)) %>%
    pull(loss)
  return(loss)
}

fun.overall = function(par, data, df_parameters, fun_model){
  tmp = data %>% 
    group_by(version, alternative) %>% 
    nest() %>% 
    left_join(df_parameters,
              by = c("version", "alternative")) %>% 
    mutate(l = map2_dbl(.x = parameters, 
                        .y = data,
                        .f = ~ fun.fit(par = par[.x],
                                       data = .y,
                                       fun_model = fun_model)))
  loss = sum(tmp$l)
  return(loss)
}

fun.overall_grid = function(data, df_parameters, fun_model){
  tmp = data %>% 
    group_by(version, alternative) %>% 
    nest() %>% 
    left_join(df_parameters,
              by = c("version", "alternative")) %>% 
    mutate(l = map2_dbl(.x = parameters, 
                        .y = data,
                        .f = ~ fun.fit(par = .x,
                                       data = .y,
                                       fun_model = fun_model)))
  loss = sum(tmp$l)
  return(loss)
}

```

### Plots 

#### Results

```{r, fig.width=10, fig.height = 7}
fun.plot_results = function(params){
  
  df.model = df.data %>% 
    group_by(alternative, version, age) %>%
    nest() %>% 
    left_join(df.parameters,
              by = c("version", "alternative")) %>% 
    mutate(prediction = map2(.x = parameters, 
                             .y = age,
                             .f = ~ fun.model(par = params[.x],
                                              age = .y))) %>% 
    unnest(c(data, prediction),
           names_sep = "_") %>% 
    ungroup() %>% 
    select(age,
           question = data_question,
           event = data_event,
           probability = data_probability,
           low = data_low,
           high = data_high,
           prediction = prediction_value,
           alternative,
           version)
  
  df.plot = df.model %>% 
    filter(event == "nonstandard")
  
  p = ggplot(data = df.plot,
             mapping = aes(x = age,
                           y = probability,
                           group = question,
                           color = question,
                           fill = question)) +
    geom_hline(yintercept = 0.50,
               linetype = "dashed",
               color = "black") +
    geom_line(mapping = aes(y = prediction),
              linewidth = 1.5,
              alpha = 0.5) +
    geom_linerange(mapping = aes(ymin = low,
                                ymax = high),
                   alpha = 0.75,
                   show.legend = F) + 
    geom_point(size = 2.5,
               show.legend = F) + 
    facet_grid(rows = vars(version),
               cols = vars(alternative)) + 
    scale_color_manual(values = c("lexical" = "#377EB8",
                                  "made" = "#4DAF4A",
                                  "caused" = "#E41A1C"),
                       breaks = c("lexical", "made", "caused"),
                       guide = guide_legend(reverse = T)) +
    scale_y_continuous(breaks = seq(0, 1, 0.25),
                       labels = c("100% PT", "75%", "50%", "75%", "100% NS"),
                       limits = c(0, 1)) + 
    labs(y = "probability of selecting\neach cause") + 
    theme(panel.spacing.y = unit(0.5, "cm"))
  p
  
  return(p)
}
```

#### Parameters 

```{r, fig.width=12, fig.height = 5}
fun.plot_params = function(params, nbeta, nprior, ncost){
  n_params = length(params)
  
  if(nbeta == 1){
    p.beta = ggplot(data = tibble(),
                    mapping = aes(x = x)) + 
      geom_col(mapping = aes(x = 1,
                             y = params[1],
                             fill = "black"),
               show.legend = F)
      labs(y = "softmax")
  }else{
    p.beta = ggplot(data = tibble(x = 4:9),
                    mapping = aes(x = x)) + 
      geom_line(mapping = aes(y = params[1] + params[2] * x),
                color = "black",
                linewidth = 1.5) + 
      scale_y_continuous(breaks = seq(0, 0.5, 0.1),
                         limits = c(0, 0.5)) + 
      labs(x = "age",
           y = TeX(r"(speaker optimality $\alpha$)"))
  }
  
  if(nprior == 2){
    p.prior = ggplot() + 
      geom_col(mapping = aes(x = 1:2,
                             y = c(params[nbeta + 1], params[nbeta + 2]),
                             fill = c("chain", "omission")),
               color = "black", 
               show.legend = F) + 
      scale_x_continuous(breaks = c(1, 2),
                         labels = c("chain", "omission")) +
      scale_fill_manual(values = c("chain" = "orange",
                                   "omission" = "purple")) + 
      scale_y_continuous(breaks = seq(0, 0.5, 0.1),
                         limits = c(0, 0.5)) + 
      labs(x = "scenario",
           y = TeX(r"(prior $\it{P}(\it{r})$)"))
  }else{
    p.prior = ggplot(data = tibble(x = 4:9),
                    mapping = aes(x = x)) + 
      geom_line(mapping = aes(y = params[nbeta + 1] + params[nbeta + 2] * x,
                              color = "caused"),
                linewidth = 1) + 
      geom_line(mapping = aes(y = params[nbeta + 3] + params[nbeta + 4] * x,
                              color = "made"),
                linewidth = 1) + 
      scale_x_continuous(breaks = c(1, 2),
                         labels = c("chain", "omission")) +
      scale_fill_manual(values = c("chain" = "orange",
                                   "omission" = "purple")) + 
      labs(x = "age",
           y = "prior") +
      theme(legend.position = "right",
            legend.direction = "vertical") + 
      guides(color = guide_legend(reverse = T))
  }
  
  if(ncost == 2){
    p.cost = ggplot() + 
      geom_col(mapping = aes(x = 1,
                             y = params[nbeta + nprior + 1],
                             fill = "caused"),
               show.legend = F) + 
      geom_col(mapping = aes(x = 2, 
                             y = params[nbeta + nprior + 2],
                             fill = "made"),
               show.legend = F) + 
      scale_x_continuous(breaks = c(1, 2),
                         labels = c("caused", "made")) +
      scale_fill_manual(values = c("caused" = "#E41A1C",
                                   "made" = "#4DAF4A")) +
      labs(y = "cost") +
      theme(axis.title.x = element_blank())
  }else{
    p.cost = ggplot(data = tibble(x = 4:9),
                    mapping = aes(x = x)) + 
      geom_line(mapping = aes(y = params[nbeta + nprior + 1] + params[nbeta + nprior + 2] * x,
                              color = "caused"),
                linewidth = 1.5) + 
      geom_line(mapping = aes(y = params[nbeta + nprior + 3] + params[nbeta + nprior + 4] * x,
                              color = "made"),
                linewidth = 1.5) + 
      scale_color_manual(values = c("caused" = "#E41A1C",
                                    "made" = "#4DAF4A")) +
      labs(x = "age",
           y = TeX(r"(cost $\it{u}$)"),
           color = "alternative") +
      theme(legend.position = "right",
            legend.direction = "vertical")
  }
  
  p.beta + p.prior + p.cost +  
    plot_annotation(tag_levels = "A")
}
```

## Model fits 

### Optimization 

#### Beta: variable; prior: constant; cost: variable 

```{r, fig.width=10, fig.height=6}
# beta = 1:2
# chain = 3
# omission 4
# caused = 5:6
# made = 7:8
df.parameters = df.data %>% 
  distinct(version, alternative) %>% 
  mutate(parameters = list(c(1:2, 3, 5:6), 
                           c(1:2, 3, 7:8),
                           c(1:2, 4, 5:6),
                           c(1:2, 4, 7:8)))

fun.model = function(par, age){
  beta = par[1] + par[2] * age
  p_nonstandard = par[3] 
  cost = par[4] + par[5] * age
  
  if(p_nonstandard <= 0){
    p_nonstandard = 0.001
  }
  if(p_nonstandard >= 1){
    p_nonstandard = 0.999
  }
  prior = c(prototypical = 1-p_nonstandard,
            nonstandard = p_nonstandard)
  
  l0 = fun.l0(prior = prior)
  s1 = fun.s1(l0,
              cost = cost,
              beta = beta)
  l1 = fun.l1(s1,
              prior = prior)
  return(l1)
}

# # best fitting parameters (converging solution!)
par = c(-0.0971210, 0.0623497, 0.3595724, 0.1530933, -0.1393184,  0.5599144, -1.2883752,  0.3481894)

# optimization
# fit = optim(par = rep(0, max(unlist(df.parameters$parameters))),
#             fn = fun.overall,
#             data = df.data,
#             fun_model = fun.model,
#             df_parameters = df.parameters,
#             method = "Nelder-Mead",
#             control = list(maxit = 2000))

# results 
# fun.plot_results(params = fit$par)
fun.plot_results(params = par)
# ggsave("../../figures/plots/model_fits.pdf",
#        width = 10,
#        height = 7)

# # parameters
# # fun.plot_params(params = fit$par,
fun.plot_params(params = par,
                 nbeta = 2,
                 nprior = 2,
                 ncost = 4)

# ggsave("../../figures/rsa/model_parameters.pdf",
#        width = 12,
#        height = 5)
```

#### Alternative models 

##### Beta: constant; prior: constant; cost: constant 

```{r, fig.width=10, fig.height=6}
# beta = 1
# chain = 2
# omission 3
# caused = 4
# made = 5
df.parameters = df.data %>% 
  distinct(version, alternative) %>% 
  mutate(parameters = list(c(1, 2, 4), 
                           c(1, 2, 5),
                           c(1, 3, 4),
                           c(1, 3, 5)))

fun.model = function(par, age){
  beta = par[1] 
  p_nonstandard = par[2] 
  cost = par[3]
  
  if(p_nonstandard <= 0){
    p_nonstandard = 0.001
  }
  if(p_nonstandard >= 1){
    p_nonstandard = 0.999
  }
  prior = c(prototypical = 1-p_nonstandard,
            nonstandard = p_nonstandard)
  
  l0 = fun.l0(prior = prior)
  s1 = fun.s1(l0,
              cost = cost,
              beta = beta)
  l1 = fun.l1(s1,
              prior = prior)
  return(l1)
}

par = c(0.5, 0.1, 0.5)

# optimization
fit = optim(par = rep(0, 5),
            fn = fun.overall,
            data = df.data,
            fun_model = fun.model,
            df_parameters = df.parameters,
            method = "Nelder-Mead")

# results 
fun.plot_results(params = fit$par)

# parameters
fun.plot_params(params = fit$par,
                nbeta = 1,
                nprior = 2,
                ncost = 2)
```

##### Beta: variable; prior: constant; cost: constant 

```{r, fig.width=10, fig.height=6}
# beta = 1:2
# chain = 3
# omission 4
# caused = 5
# made = 6
df.parameters = df.data %>% 
  distinct(version, alternative) %>% 
  mutate(parameters = list(c(1:2, 3, 5), 
                           c(1:2, 3, 6),
                           c(1:2, 4, 5),
                           c(1:2, 4, 6)))

fun.model = function(par, age){
  beta = par[1] + par[2] * age
  p_nonstandard = par[3] 
  cost = par[4]
  
  if(p_nonstandard <= 0){
    p_nonstandard = 0.001
  }
  if(p_nonstandard >= 1){
    p_nonstandard = 0.999
  }
  prior = c(prototypical = 1-p_nonstandard,
            nonstandard = p_nonstandard)
  
  l0 = fun.l0(prior = prior)
  s1 = fun.s1(l0,
              cost = cost,
              beta = beta)
  l1 = fun.l1(s1,
              prior = prior)
  return(l1)
}

# optimization
fit = optim(par = rep(0, 6),
            fn = fun.overall,
            data = df.data,
            fun_model = fun.model,
            df_parameters = df.parameters,
            method = "Nelder-Mead")

# results 
fun.plot_results(params = fit$par)

# parameters
fun.plot_params(params = fit$par,
                nbeta = 2,
                nprior = 2,
                ncost = 2)
```

##### Beta: constant; prior: constant; cost: variable 

```{r, fig.width=10, fig.height=6}
# beta = 1
# chain = 2
# omission 3
# caused = 4:5
# made = 6:7
df.parameters = df.data %>% 
  distinct(version, alternative) %>% 
  mutate(parameters = list(c(1, 2, 4, 5), 
                           c(1, 2, 6, 7),
                           c(1, 3, 4, 5), 
                           c(1, 3, 6, 7)))

fun.model = function(par, age){
  beta = par[1]
  p_nonstandard = par[2] 
  cost = par[3] + par[4] * age
  
  if(p_nonstandard <= 0){
    p_nonstandard = 0.001
  }
  if(p_nonstandard >= 1){
    p_nonstandard = 0.999
  }
  prior = c(prototypical = 1-p_nonstandard,
            nonstandard = p_nonstandard)
  
  l0 = fun.l0(prior = prior)
  s1 = fun.s1(l0,
              cost = cost,
              beta = beta)
  l1 = fun.l1(s1,
              prior = prior)
  return(l1)
}

# best fitting parameters
# par = c(0.37389834,
#         0.24199678,
#         0.10174182,
#         -0.07839857,
#         1.16558207,
#         -3.41787156,
#         1.18943229)

# optimization
fit = optim(par = rep(0, max(unlist(df.parameters$parameters))),
            fn = fun.overall,
            data = df.data,
            fun_model = fun.model,
            df_parameters = df.parameters,
            method = "Nelder-Mead",
            control = list(maxit = 1000))

# results 
fun.plot_results(params = fit$par)

# parameters
fun.plot_params(params = fit$par,
                nbeta = 1,
                nprior = 2,
                ncost = 4)
```

### Grid search 

#### Beta: constant; prior: constant; cost: constant 

```{r, fig.width=10, fig.height=6}
# beta = 1
# chain = 2
# omission 3
# caused = 4
# made = 5

variables = c("beta",
              "chain",
              "omission",
              "caused",
              "made")

df.parameters = df.data %>% 
  distinct(version, alternative) %>% 
  mutate(parameters = list(c(1, 2, 4), 
                           c(1, 2, 5),
                           c(1, 3, 4),
                           c(1, 3, 5)))

df.parameter_values = expand_grid(beta = seq(0.5, 2, 0.5),
                                  chain = seq(0.1, 0.9, 0.2),
                                  omission = seq(0.1, 0.9, 0.2),
                                  caused = seq(0.5, 2, 0.5),
                                  made = seq(0.5, 2, 0.5))

# df.parameter_values = df.parameter_values %>% 
#   filter(row_number() %in% c(1, 100, 200))

fun.model = function(par, age){
  beta = par[1] 
  p_nonstandard = par[2] 
  cost = par[3]
  
  prior = c(prototypical = 1-p_nonstandard,
            nonstandard = p_nonstandard)
  
  l0 = fun.l0(prior = prior)
  s1 = fun.s1(l0,
              cost = cost,
              beta = beta)
  l1 = fun.l1(s1,
              prior = prior)
  return(l1)
}

df.loss = df.parameters %>% 
  unnest(parameters) %>% 
  mutate(parameters = variables[parameters]) %>% 
  expand_grid(index = 1:nrow(df.parameter_values)) %>% 
  arrange(index) %>% 
  left_join(df.parameter_values %>% 
              mutate(index = 1:n()) %>% 
              pivot_longer(cols = -index), 
            by = c("index", "parameters" = "name")) %>% 
  group_by(index, version, alternative) %>% 
  mutate(parameters = list(value)) %>% 
  distinct(index, version, alternative, parameters) %>% 
  ungroup() %>% 
  nest(data = -index) %>% 
  mutate(loss = map_dbl(.x = data,
                        .f = ~ fun.overall_grid(data = df.data,
                                                df_parameters = .x,
                                                fun_model = fun.model)))


# fun.overall_grid(df.data,
#                  df_parameters,
#                  fun.model)

# save(df.loss, file = "loss.RData")

df.best_fit = df.loss %>% 
  ungroup() %>% 
  filter(loss == min(loss)) %>% 
  unnest(data) %>% 
  select(version, alternative, parameters) %>% 
  unnest(parameters) %>% 
  bind_cols(df.parameters %>% 
              unnest(parameters) %>% 
              select(index = parameters)) %>% 
  distinct(index, parameters) %>% 
  arrange(index)

# results 
fun.plot_results(params = df.best_fit$parameters)

# parameters
fun.plot_params(params = df.best_fit$parameters,
                nbeta = 1,
                nprior = 2,
                ncost = 2)
```

#### Beta: variable; prior: constant; cost: variable 

```{r, fig.width=10, fig.height=6}
# beta = 1:2
# chain = 3
# omission 4
# caused = 5:6
# made = 7:8
df.parameters = df.data %>% 
  distinct(version, alternative) %>% 
  mutate(parameters = list(c(1:2, 3, 5:6), 
                           c(1:2, 3, 7:8),
                           c(1:2, 4, 5:6),
                           c(1:2, 4, 7:8)))

variables = c("beta_intercept",
              "beta_slope",
              "chain",
              "omission",
              "caused_intercept",
              "caused_slope",
              "made_intercept",
              "made_slope")

# best fitting parameters from optim 
params = c(-0.10348257,
           0.06281879,
           0.35939409,
           0.15519388,
           -0.14396582,
           0.56518446,
           -1.28347795,
           0.34417906)

delta = seq(-0.1, 0.1, 0.1)

df.parameter_values = expand_grid(beta_intercept = params[1] + delta,
                                  beta_slope = params[2] + delta,
                                  chain = params[3] + delta,
                                  omission = params[4] + delta,
                                  caused_intercept = params[5] + delta,
                                  caused_slope = params[6] + delta,
                                  made_intercept = params[7] + delta,
                                  made_slope = params[8] + delta)

fun.model = function(par, age){
  beta = par[1] + par[2] * age
  p_nonstandard = par[3] 
  cost = par[4] + par[5] * age
  prior = c(prototypical = 1-p_nonstandard,
            nonstandard = p_nonstandard)
  
  l0 = fun.l0(prior = prior)
  s1 = fun.s1(l0,
              cost = cost,
              beta = beta)
  l1 = fun.l1(s1,
              prior = prior)
  return(l1)
}

df.loss = df.parameters %>% 
  unnest(parameters) %>% 
  mutate(parameters = variables[parameters]) %>% 
  expand_grid(index = 1:nrow(df.parameter_values)) %>% 
  arrange(index) %>% 
  left_join(df.parameter_values %>% 
              mutate(index = 1:n()) %>% 
              pivot_longer(cols = -index), 
            by = c("index", "parameters" = "name")) %>% 
  group_by(index, version, alternative) %>% 
  mutate(parameters = list(value)) %>% 
  distinct(index, version, alternative, parameters) %>% 
  ungroup() %>% 
  nest(data = -index) %>% 
  mutate(loss = map_dbl(.x = data,
                        .f = ~ fun.overall_grid(data = df.data,
                                                df_parameters = .x,
                                                fun_model = fun.model)))

# save(df.loss, file = "loss.RData")

df.best_fit = df.loss %>% 
  ungroup() %>% 
  filter(loss == min(loss)) %>% 
  unnest(data) %>% 
  select(version, alternative, parameters) %>% 
  unnest(parameters) %>% 
  bind_cols(df.parameters %>% 
              unnest(parameters) %>% 
              select(index = parameters)) %>% 
  distinct(index, parameters) %>% 
  arrange(index)

# results 
fun.plot_results(params = df.best_fit$parameters)

# parameters
fun.plot_params(params = df.best_fit$parameters,
                nbeta = 2,
                nprior = 2,
                ncost = 4)
```

## Scatter plot 

```{r, fig.width=9, fig.height=6}
df.plot = df.data %>% 
  group_by(alternative, version, age) %>%
  nest() %>% 
  left_join(df.parameters,
            by = c("version", "alternative")) %>% 
  mutate(prediction = map2(.x = parameters, 
                           .y = age,
                           .f = ~ fun.model(par = par[.x],
                                            age = .y))) %>% 
  unnest(c(data, prediction),
         names_sep = "_") %>% 
  ungroup() %>% 
  select(age,
         question = data_question,
         event = data_event,
         probability = data_probability,
         low = data_low,
         high = data_high,
         prediction = prediction_value,
         alternative,
         version) %>% 
  filter(event == "nonstandard")

df.text = df.plot %>% 
  summarize(r = cor(probability, prediction),
            rmse = sqrt(mean((probability - prediction)^2))*100)


ggplot(data = df.plot,
       mapping = aes(x = prediction,
                     y = probability)) + 
  # geom_hline(yintercept = 0.5,
  #            linetype = "dashed",
  #            color = "grey") +
  # geom_vline(xintercept = 0.5,
  #            linetype = "dashed",
  #            color = "grey") +
  geom_smooth(method = "lm",
              formula = y ~ x, 
              fill = "lightblue",
              color = "black") +
  geom_linerange(mapping = aes(ymin = low,
                               ymax = high),
                 alpha = 0.2) +
  geom_point(mapping = aes(fill = question,
                           shape = version),
             size = 2) + 
  annotate(geom = "text",
           x = 0,
           y = c(1, 0.9),
           label = c(str_c("r = ", round(df.text$r, 2)),
                      str_c("RMSE = ", round(df.text$rmse, 2))),
           hjust = 0,
           vjust = 1,
           size = 8) + 
  labs(x = "model prediction",
       y = "probability of selecting\neach cause",
       shape = "scenario",
       fill = "utterance") + 
  scale_shape_manual(values = c("chain" = 21,
                                "omission" = 22)) +
  scale_fill_manual(values = c("lexical" = "#377EB8",
                                  "made" = "#4DAF4A",
                                  "caused" = "#E41A1C"),
                       breaks = c("lexical", "made", "caused"),
                       guide = guide_legend(reverse = T)) + 
  scale_x_continuous(breaks = seq(0, 1, 0.25),
                       labels = c("100% PT", "75%", "50%", "75%", "100% NS"),
                     limits = c(0, 1)) + 
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                       labels = c("100% PT", "75%", "50%", "75%", "100% NS"),
                     limits = c(0, 1)) +
  guides(fill = guide_legend(override.aes = list(shape = 21, size = 3)),
         shape = guide_legend(override.aes = list(size = 3)))

ggsave("../../figures/rsa/scatterplot.pdf",
       width = 9,
       height = 6)
```




