---
title: 'Supplemental Information: Order Effects'
author: "David Rose, Siying Zhang, Shaun Nichols, Ellen Markman & Tobias Gerstenberg"
date: "`r Sys.Date()`"
output: pdf_document
---
# Load packages
```{r eval=TRUE, include=FALSE, message=FALSE, warning=FALSE}

library("janitor")        # for cleaning variable nqmes
library("emmeans")        # for comparing means
library("brms")           # for Bayesian data analysis
library("patchwork")      # for combining figures
library("knitr")          # for knitting 
library("tidyverse")      # for everything else

```

# Settings

```{r message=FALSE, warning=FALSE}

# set theme 
theme_set(theme_classic())

```

# EXPERIMENT 1: CHAINS
## CAUSE V LEXICAL (BREAK & CRACK)
### ADULTS
#### DATA
##### Read in data
##### Wrangle

### CHILDREN
#### DATA
##### Read in data

```{r message=FALSE, warning=FALSE}

df.exp1_cause_children = read_csv("../../data/experiment1/cause/children/exp1_cause_children.csv")

```

##### Wrangle
```{r message=FALSE, warning=FALSE}

#clean data
df.exp1_cause_children = df.exp1_cause_children %>% 
  clean_names() %>% 
  rename(
         question = question_type) %>% 
  mutate(response = str_remove_all(string = response,
                                   pattern = "\""),
         response = str_remove_all(string = response,
                                   pattern = ":"),
         response = str_remove_all(string = response,
                                   pattern = "\\}"),
         response = str_remove_all(string = response,
                                   pattern = "\\."),
         response = str_remove_all(string = response,
                                   pattern = "\\,"),
         response = str_remove_all(string = response,
                                   pattern = "\\\\n"),
         response = str_to_lower(response)) %>% 
  select(-(response_id : age_range), -notes, -full_response, -gender) 


# code responses
df.exp1_cause_children = df.exp1_cause_children %>% 
  mutate(distal = ifelse(counterbalance == "andy" & str_detect(response, "andy"), 1, 0),
         distal = ifelse(counterbalance == "suzy" & str_detect(response, "suzy"), 1, distal),
         distal = ifelse(counterbalance == "bobby" & str_detect(response, "bobby"), 1, distal),
         distal = ifelse(counterbalance == "sophia" & str_detect(response, "sophia"), 1, distal),
         proximal = ifelse(counterbalance == "andy" & str_detect(response, "suzy"), 1, 0),
         proximal = ifelse(counterbalance == "suzy" & str_detect(response, "andy"), 1, proximal),
         proximal = ifelse(counterbalance == "bobby" & str_detect(response, "sophia"), 1, proximal),
         proximal = ifelse(counterbalance == "sophia" & str_detect(response, "bobby"), 1, proximal),
         age = round(rounded_age / 365, digits = 2),
         question = str_replace_all(question, "break|crack", "simple")) %>% 
  na.omit()

# compute age and recode question
df.exp1_cause_children = df.exp1_cause_children %>% 
  mutate(age_whole = as.integer(age)) %>%
  mutate(age_character = as.character(age_whole)) %>%
  mutate(age_character = recode(age_character, "7" = "7-9", "8" = "7-9", "9" = "7-9"),
         question = str_replace_all(question, "simple", "lexical")) %>%
  rename(participant = participant_number)
 
```

#### STATS
##### Distal

```{r}


df.model = df.exp1_cause_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "lexical"),
         caused_question_order = as_factor(caused_question_order),
         caused_question_order = fct_relevel(caused_question_order, "first")) %>% 
   group_by(participant) %>%
   filter(row_number() <= 2) %>%
  ungroup()

# Check contrast values
 contrasts(df.model$question)
 contrasts(df.model$caused_question_order)


fit.brm.distal = brm(formula = distal ~ 1 + question*caused_question_order + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_children_distal_order") 
fit.brm.distal


```
##### Proximal

```{r}

fit.brm.proximal = brm(formula = proximal ~ 1 + question*caused_question_order + (1 | participant),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/cause_children_proximal_order") 

fit.brm.proximal


```
## MADE V LEXICAL (BREAK & CRACK)
### ADULTS
#### DATA
##### Read in data
##### Wrangle

### CHILDREN
#### DATA
##### Read in data

```{r message=FALSE, warning=FALSE}

df.exp1_made_children = read_csv("../../data/experiment1/made/children/exp1_made_children.csv")

```

##### Wrangle

```{r message=FALSE, warning=FALSE}

#clean data
df.exp1_made_children = df.exp1_made_children %>% 
  clean_names() %>% 
  rename(
         question = question_type) %>% 
  mutate(response = str_to_lower(response),
         counterbalance = str_to_lower(counterbalance)) %>% 
  select(-(response_id : age_range), -notes, -full_response, -gender) 

#code responses
df.exp1_made_children = df.exp1_made_children %>% 
  mutate(distal = ifelse(counterbalance == "andy" & str_detect(response, "andy"), 1, 0),
         distal = ifelse(counterbalance == "suzy" & str_detect(response, "suzy"), 1, distal),
          distal = ifelse(counterbalance == "bobby" & str_detect(response, "bobby"), 1, distal),
          distal = ifelse(counterbalance == "sophia" & str_detect(response, "sophia"), 1, distal),
         proximal = ifelse(counterbalance == "andy" & str_detect(response, "suzy"), 1, 0),
         proximal = ifelse(counterbalance == "suzy" & str_detect(response, "andy"), 1, proximal),
          proximal = ifelse(counterbalance == "bobby" & str_detect(response, "sophia"), 1, proximal),
          proximal = ifelse(counterbalance == "sophia" & str_detect(response, "bobby"), 1, proximal),
         age = round(rounded_age / 365, digits = 2),
         question = str_replace_all(question, "break|crack", "simple")) %>% 
  na.omit()

# compute age and recode question
df.exp1_made_children = df.exp1_made_children %>% 
   mutate(age_whole =as.integer(age)) %>%
  mutate(age_character = as.character(age_whole)) %>%
  mutate(age_character = recode(age_character, "7" = "7-9", "8" = "7-9", "9" = "7-9"),
         question = str_replace_all(question, "simple", "lexical")) %>%
  rename(participant = participant_number) 

```

#### STATS
##### Distal

```{r}


df.model = df.exp1_made_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "lexical"),
         made_question_order = as_factor(made_question_order),
         made_question_order = fct_relevel(made_question_order, "first")) %>% 
   group_by(participant) %>%
   filter(row_number() <= 2) %>%
  ungroup()

# Check contrast values
 contrasts(df.model$question)
 contrasts(df.model$made_question_order)


fit.brm.distal = brm(formula = distal ~ 1 + question*made_question_order + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/made_children_distal_order") 
fit.brm.distal


```

##### Proximal

```{r}

fit.brm.proximal = brm(formula = proximal ~ 1 + question*made_question_order + (1 | participant),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/made_children_proximal_order") 

fit.brm.proximal


```

## PLOTS
### Data
#### Different Responses

```{r fig.height=4, fig.width=6, message=FALSE, warning=FALSE}

df.exp1_cause_children_difference = df.exp1_cause_children %>% 
  rename(periphrastic_question_order = caused_question_order) %>% 
  select(question, distal, proximal, periphrastic_question_order) %>% 
  mutate(age = rep("children"))

df.exp1_made_children_difference = df.exp1_made_children %>% 
  rename(periphrastic_question_order = made_question_order) %>% 
  select(question, distal, proximal, periphrastic_question_order) %>% 
  mutate(age = rep("children"))

df.plot = df.exp1_cause_children_difference %>% 
  bind_rows(df.exp1_made_children_difference) %>% 
   mutate(response_pattern = case_when(
    distal == 1 & proximal == 1 ~ "both",
    distal == 0 & proximal == 0 ~ "neither",
    TRUE ~ "different"
  )) %>% 
  filter(response_pattern == "different") %>% 
  mutate(difference = distal - proximal,
        difference = recode(difference, `-1` = 0),
        question = str_replace_all(question, "caused", "cause"))


ggplot(data = df.plot,
       mapping = aes(x = factor(question, levels = c("cause", "made", "lexical")),
                     y = difference,
                     color = periphrastic_question_order,
                     fill = periphrastic_question_order)) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
   stat_summary(fun.data = "mean_cl_boot",
               position = position_dodge(width = 0.5),
               shape = 21,
               color = "black",
               size = 1) +
  scale_fill_brewer(palette = "Set3") +
  scale_color_brewer(palette = "Set3") +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = c("100% \n proximal", "75%", "50%", "75%", "100% \n distal"),
                     limits = c(0, 1)) +
  ylab("Probability of selecting \n distal or proximal cause") +
  theme(legend.position = "bottom",
        legend.box = "vertical",
        axis.title.x = element_blank(),
        text = element_text(size = 18)) +
  labs(color = "  periphrastic \n\ question order",
       fill = "   periphrastic \n\ question order") +
  guides(color = guide_legend(override.aes = list(fill = NA)))

ggsave("../../figures/experiment1/chain_order_effect.pdf", height = 5, width = 6)



```

# EXPERIMENT 2: ABSENCES
## CAUSE V LEXICAL (BURN & FLOOD)
### ADULTS
#### DATA
##### Read in data

```{r message=FALSE, warning=FALSE}

df.exp2_cause_adults = read_csv("../../data/experiment2/cause/adults/exp2_cause_adults.csv")

```

##### Wrangle
```{r message=FALSE, warning=FALSE}

# clean data
df.exp2_cause_adults = df.exp2_cause_adults %>% 
  mutate(condition = str_extract(string = responses,
                                 pattern = "sunburn_simple_response|sunburn_cause_response|flood_simple_response|flood_cause_response"),
         response = str_extract(string = responses, 
                                pattern = ":(.*)"),
         response = str_remove_all(string = response,
                                   pattern = "\""),
         response = str_remove_all(string = response,
                                   pattern = ":"),
         response = str_remove_all(string = response,
                                   pattern = "\\}"),
         response = str_remove_all(string = response,
                                   pattern = "\\."),
         response = str_remove_all(string = response,
                                   pattern = "\\,"),
         response = str_remove_all(string = response,
                                   pattern = "\\\\n"),
         response = str_to_lower(response)) %>% 
  separate(condition, c("scenario", "question", "extra"), "_") %>% 
  rename(participant = workerid) %>% 
  select(participant, scenario, question, response)

# code responses
df.exp2_cause_adults = df.exp2_cause_adults %>%
  mutate(direct = ifelse(str_detect(response,
                                    "^sun$|sun | sun$"), 1, 0),
         direct = ifelse(str_detect(response,
                                    "^water$|water | water$"), 1, direct),
         direct = ifelse(str_detect(response,
                                    "^rain$|rain | rain$"), 1, direct),
         absence = ifelse(str_detect(response,
                                     "^sunscreen$|sunscreen | sunscreen$"), 1, 0),
         absence = ifelse(str_detect(response,
                                     "^window$|window | window$"), 1, absence),
         absence = ifelse(str_detect(response,
                                     "^latch$|latch | latch$"), 1, absence))

## replace simple with lexical
df.exp2_cause_adults = df.exp2_cause_adults %>% 
  mutate(question = str_replace_all(question, "simple", "lexical"))

# code order
df.tmp = df.exp2_cause_adults %>% 
  group_by(participant) %>% 
  filter(row_number() == 1) %>% 
  mutate(scenario_order = str_c(scenario, "_first"),
         question_order = str_c(question, "_first")) %>% 
  select(participant,
         contains("order"))

df.exp2_cause_adults = df.exp2_cause_adults %>% 
  left_join(df.tmp,
            by = "participant") %>% 
  relocate(contains("order"), .after = question) %>% 
  mutate(caused_question_order = case_when(question_order == "lexical_first" ~ "second",
                                          question_order == "cause_first" ~ "first"))


```

#### STATS
##### Direct

```{r}

df.model = df.exp2_cause_adults %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "lexical"),
         caused_question_order = as_factor(caused_question_order),
         caused_question_order = fct_relevel(caused_question_order, "first")) %>% 
   group_by(participant) %>%
   filter(row_number() <= 2) %>%
  ungroup()

# Check contrast values
 contrasts(df.model$question)
 contrasts(df.model$caused_question_order)
 
fit.brm.direct = brm(formula = direct ~ 1 + question*caused_question_order + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_adult_direct_order") 
fit.brm.direct

```

##### Absent
```{r}

fit.brm.absent = brm(formula = absence ~ 1 + question*caused_question_order + (1 | participant),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/cause_adult_absent_order") 

fit.brm.absent

```

### CHILDREN
#### DATA
##### Read in data

```{r message=FALSE, warning=FALSE}

df.exp2_cause_children = read_csv("../../data/experiment2/cause/children/exp2_cause_children.csv")

```

##### Wrangle
```{r message=FALSE, warning=FALSE}

# clean responses
df.exp2_cause_children = df.exp2_cause_children %>% 
  rename(response = full_response,
         question = question_type) %>% 
  mutate(response = str_remove_all(string = response,
                                   pattern = "\""),
         response = str_remove_all(string = response,
                                   pattern = ":"),
         response = str_remove_all(string = response,
                                   pattern = "\\}"),
         response = str_remove_all(string = response,
                                   pattern = "\\."),
         response = str_remove_all(string = response,
                                   pattern = "\\,"),
         response = str_remove_all(string = response,
                                   pattern = "\\\\n"),
         response = str_to_lower(response))


# code responses
df.exp2_cause_children = df.exp2_cause_children %>%
  mutate(direct = ifelse(str_detect(response,
                                    "^sun$|sun | sun$"), 1, 0),
         direct = ifelse(str_detect(response,
                                    "^water$|water | water$"), 1, direct),
         direct = ifelse(str_detect(response,
                                    "^rain$|rain | rain$"), 1, direct),
         absence = ifelse(str_detect(response,
                                     "^sunscreen$|sunscreen | sunscreen$"), 1, 0),
         # note the first response in the data is 'windows' but this doesn't capture that
         absence = ifelse(str_detect(response,
                                     "^window$|window | window$"), 1, absence),
         absence = ifelse(str_detect(response,
                                     "^latch$|latch | latch$"), 1, absence)) 


# compute age and replace simple with lexical
df.exp2_cause_children = df.exp2_cause_children %>%
  mutate(age = round(rounded_age / 365, digits = 2),
         age_whole =as.integer(age),
         question = str_replace_all(question, "simple", "lexical"))

```

#### STATS
##### Direct

```{r}

df.model = df.exp2_cause_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "lexical"),
         caused_question_order = as_factor(cause_question_order),
         caused_question_order = fct_relevel(caused_question_order, "first")) %>% 
   group_by(participant) %>%
   filter(row_number() <= 2) %>%
  ungroup()

# Check contrast values
 contrasts(df.model$question)
 contrasts(df.model$caused_question_order)
 
 fit.brm.direct = brm(formula = direct ~ 1 + question*caused_question_order + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_children_direct_order") 
fit.brm.direct


```

##### Absent

```{r}

fit.brm.absent = brm(formula = absence ~ 1 + question*caused_question_order + (1 | participant),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/cause_children_absent_order") 


fit.brm.absent

```

## MADE V LEXICAL (BURN & FLOOD)
### ADULTS
#### DATA
##### Read in data

```{r message=FALSE, warning=FALSE}

df.exp2_made_adults = read_csv("../../data/experiment2/made/adults/exp2_made_adults.csv")

```

##### Wrangle

```{r message=FALSE, warning=FALSE}

# clean responses
df.exp2_made_adults = df.exp2_made_adults %>% 
  mutate(condition = str_extract(string = responses,
                                 pattern = "sunburn_simple_response|sunburn_made_response|flood_simple_response|flood_made_response"),
         response = str_extract(string = responses, 
                                pattern = ":(.*)"),
         response = str_remove_all(string = response,
                                   pattern = "\""),
         response = str_remove_all(string = response,
                                   pattern = ":"),
         response = str_remove_all(string = response,
                                   pattern = "\\}"),
         response = str_remove_all(string = response,
                                   pattern = "\\."),
         response = str_remove_all(string = response,
                                   pattern = "\\,"),
         response = str_remove_all(string = response,
                                   pattern = "\\\\n"),
         response = str_to_lower(response)) %>% 
  separate(condition, c("scenario", "question", "extra"), "_") %>% 
  rename(participant = workerid) %>% 
  select(participant, scenario, question, response)

# code responses
df.exp2_made_adults = df.exp2_made_adults %>%
  mutate(direct = ifelse(str_detect(response,
                                    "^sun$|sun | sun$"), 1, 0),
         direct = ifelse(str_detect(response,
                                    "^water$|water | water$"), 1, direct),
         direct = ifelse(str_detect(response,
                                    "^rain$|rain | rain$"), 1, direct),
         absence = ifelse(str_detect(response,
                                     "^sunscreen$|sunscreen | sunscreen$"), 1, 0),
         absence = ifelse(str_detect(response,
                                     "^window$|window | window$"), 1, absence),
         absence = ifelse(str_detect(response,
                                     "^latch$|latch | latch$"), 1, absence))


## replace simple with lexical
df.exp2_made_adults = df.exp2_made_adults %>% 
  mutate(question = str_replace_all(question, "simple", "lexical"))

# code order
df.tmp = df.exp2_made_adults %>% 
  group_by(participant) %>% 
  filter(row_number() == 1) %>% 
  mutate(scenario_order = str_c(scenario, "_first"),
         question_order = str_c(question, "_first")) %>% 
  select(participant,
         contains("order"))

df.exp2_made_adults = df.exp2_made_adults %>% 
  left_join(df.tmp,
            by = "participant") %>% 
  relocate(contains("order"), .after = question) %>% 
  mutate(made_question_order = case_when(question_order == "lexical_first" ~ "second",
                                          question_order == "made_first" ~ "first"))

```

#### STATS
##### Direct

```{r}

df.model = df.exp2_made_adults %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "lexical"),
         made_question_order = as_factor(made_question_order),
         made_question_order = fct_relevel(made_question_order, "first")) %>% 
   group_by(participant) %>%
   filter(row_number() <= 2) %>%
  ungroup()

# Check contrast values
 contrasts(df.model$question)
 contrasts(df.model$made_question_order)
 
fit.brm.direct = brm(formula = direct ~ 1 + question*made_question_order + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/made_adult_direct_order") 
fit.brm.direct

```

##### Absent
```{r}

fit.brm.absent = brm(formula = absence ~ 1 + question*made_question_order + (1 | participant),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/made_adult_absent_order") 

fit.brm.absent

```

### CHILDREN
#### DATA
##### Read in data

```{r message=FALSE, warning=FALSE}

df.exp2_made_children = read_csv("../../data/experiment2/made/children/exp2_made_children.csv")

```

##### Wrangle
```{r message=FALSE, warning=FALSE}

# clean responses
df.exp2_made_children = df.exp2_made_children %>% 
  rename(response = full_response,
         question = question_type) %>% 
  mutate(response = str_remove_all(string = response,
                                   pattern = "\""),
         response = str_remove_all(string = response,
                                   pattern = ":"),
         response = str_remove_all(string = response,
                                   pattern = "\\}"),
         response = str_remove_all(string = response,
                                   pattern = "\\."),
         response = str_remove_all(string = response,
                                   pattern = "\\,"),
         response = str_remove_all(string = response,
                                   pattern = "\\\\n"),
         response = str_to_lower(response))

# code responses
df.exp2_made_children = df.exp2_made_children %>%
  mutate(direct = ifelse(str_detect(response,
                                    "^sun$|sun | sun$"), 1, 0),
         direct = ifelse(str_detect(response,
                                    "^water$|water | water$"), 1, direct),
         direct = ifelse(str_detect(response,
                                    "^rain$|rain | rain$"), 1, direct),
         absence = ifelse(str_detect(response,
                                     "^sunscreen$|sunscreen | sunscreen$"), 1, 0),
         absence = ifelse(str_detect(response,
                                     "^window$|window | window$"), 1, absence),
         absence = ifelse(str_detect(response,
                                     "^latch$|latch | latch$"), 1, absence)) 


# compute age and replace simple with lexical, fix typo
df.exp2_made_children = df.exp2_made_children %>%
  mutate(age = round(rounded_age / 365, digits = 2),
         age_whole = as.integer(age),
         question = str_replace_all(question, "simple", "lexical"),
         made_question_order = str_replace_all(made_question_order, "frst", "first"),
         made_question_order = str_replace_all(made_question_order, "scond", "second")) %>% 
  rename(participant = `participant _number`)


```

#### STATS
##### Direct

```{r}

df.model = df.exp2_made_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, "lexical"),
         made_question_order = as_factor(made_question_order),
         made_question_order = fct_relevel(made_question_order, "first")) %>% 
   group_by(participant) %>%
   filter(row_number() <= 2) %>%
  ungroup()

# Check contrast values
 contrasts(df.model$question)
 contrasts(df.model$made_question_order)
 
fit.brm.direct = brm(formula = direct ~ 1 + question*made_question_order + (1 | participant), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/made_children_direct_order") 
fit.brm.direct

```

##### Absent
```{r}

fit.brm.absent = brm(formula = absence ~ 1 + question*made_question_order + (1 | participant),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/made_children_absent_order") 

fit.brm.absent

```
## PLOTS
### Data
#### Different Responses

```{r fig.height=4, fig.width=6, message=FALSE, warning=FALSE}

df.exp2_cause_adults_differnece = df.exp2_cause_adults %>% 
  rename(periphrastic_question_order = caused_question_order) %>% 
  select(question, direct, absence, periphrastic_question_order) %>% 
  mutate(age = rep("adults"))

df.exp2_made_adults_difference = df.exp2_made_adults %>% 
  rename(periphrastic_question_order = made_question_order) %>%
  select(question, direct, absence, periphrastic_question_order) %>% 
  mutate(age = rep("adults"))

df.exp2_cause_children_difference = df.exp2_cause_children %>% 
  rename(periphrastic_question_order = cause_question_order) %>% 
  select(question, direct, absence, periphrastic_question_order) %>% 
  mutate(age = rep("children"))

df.exp2_made_children_difference = df.exp2_made_children %>% 
  rename(periphrastic_question_order = made_question_order) %>% 
  select(question, direct, absence, periphrastic_question_order) %>% 
  mutate(age = rep("children"))

df.plot = df.exp2_cause_adults_differnece %>% 
  bind_rows(df.exp2_made_adults_difference,
            df.exp2_cause_children_difference,
            df.exp2_made_children_difference) %>% 
   mutate(response_pattern = case_when(
    direct == 1 & absence == 1 ~ "both",
    direct == 0 & absence == 0 ~ "neither",
    TRUE ~ "different"
  )) %>% 
  filter(response_pattern == "different") %>% 
  mutate(difference = absence - direct,
        difference = recode(difference, `-1` = 0),
        question = str_replace_all(question, "caused", "cause"))


ggplot(data = df.plot,
       mapping = aes(x = factor(question, levels = c("cause", "made", "lexical")),
                     y = difference,
                     group = interaction(periphrastic_question_order, age),
                     color = periphrastic_question_order,
                     fill = periphrastic_question_order,
                     shape = age)) + 
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  stat_summary(fun.data = "mean_cl_boot",
               position = position_dodge(width = 0.55),
               size = .9,
               color = "black") +  
  scale_fill_brewer(palette = "Set3") +
  scale_color_brewer(palette = "Set3") +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = c("100% \n direct", "75%", "50%", "75%", "100% \n absent"),
                     limits = c(0, 1)) + 
 scale_shape_manual(values = c(21, 23)) +
  guides(fill = guide_legend(order = 1, override.aes = list(shape = 21, color = "black")),
         color = guide_legend(order = 1, override.aes = list(shape = 21, color = "black")),
         shape = guide_legend(order = 2, override.aes = list(color = "black"))) +
  ylab("Probability of selecting \n absence or direct cause") +
  theme(legend.position = "bottom",
        legend.box = "vertical",
        axis.title.x = element_blank(),
        text = element_text(size = 18)) +  
  labs(color = "  periphrastic \n\ question order", 
       fill = "   periphrastic \n\ question order",
       shape = "age")

ggsave("../../figures/experiment2/absent_order_effect.pdf", height = 5, width = 6)


```

